\documentclass[../Liederbuch/LiederbuchGitarristen.tex]{subfiles} 
\begin{document}
\song{American Pie}{Don Mclean}{}{Englisch}{Folk}{
\bridge{
\li{A \G[]long, \D[]long time \Em[]ago - \Am[]I can still re\C[]member how that \Em[]music used to \D[]make me smile.}
\li{And \G[]I knew \D[]if I \Em[]had my chance that \Am[]I could make those \C[]people dance }
\li{and \Em[]maybe they'd by \C[]happy for a \D[]while.}
\li{\Em[]But February \Am[]made me shiver \Em[]with every paper \Am[]I'd deliver.}
\li{\C[]Bad news \G[]on the \Am[]doorstep. I \C[]couldn't take one \D[]more step}
\li{I \G[]can't re\D[]member if \Em[]I cried when I \Am[7]read about his \D[]widowed bride,}
\li{\G[]Something \D[]touched me \Em[]deep inside the \C[]day the \D[7]music \G[]died.\C* \G}
}

\chorus{
\li{So \G[]bye-\C[]bye, Miss \G[]American \D[]Pie. Drove my \G[]Chevy to the \C[]levee but the \G[]levee was \D[]dry,}
\li{them \G[]good ole \C[]boys were drinkin' \G[]whiskey and \D[]Rye,}
\li{singing \Em[]this'll be the day that I \A[7]die, \Em[]this'll be the day that I \D[7]die.}
}

\verse{
\li{\G[]Did you write the \Am[]book of love and do \C[]you have faith in \Am[]God above}
\li{\Em[]If the Bible \D[]tells you so? Now do \G[]you be\D[]lieve in \Em[]rock and roll?}
\li{Can \Am[]music save your \C[]mortal soul? And \Em[]can you teach me \A[7]how to dance \D[7]real slow?}
\li{Well I \Em[]know that you're in \Am[]love with him 'cause I \Em[]saw you dancing \Am[]in the gym,}
\li{You \C[]both kicked \G[]off your \A[7]shoes, Man I \C[]dig those rhythm and \D[7]blues!}
\li{I was a \G[]lonely \D[]teenage \Em[]broncin' buck, with a \Am[]pink carnation and a \C[]pick-up truck.}
\li{But \G[]I knew \D[]I was \Em[]out of luck the \C[]day, the \D[7]music \G[]died.\C* \G[]I started \D[7]singing...}
}

\refrain

\verse{
\li{Now for \G[]ten years, we've been \Am[]on our own and \C[]moss grows fat on a \Am[]rolling stone,}
\li{\Em[]But that's not how it \D[]used to be. When the \G[]jester \D[]sang for the \Em[]King and Queen}
\li{in a \Am[]coat he borrowed \C[]from James Dean and a \Em[]voice that came from \A[7]you and \D[7]me}
\li{Oh and \Em[]while the king was \Am[]looking down the \Em[]jester stole his \Am[]thorny crown}
\li{the \C[]court room \G[]was ad\A[7]journed no \C[]verdict was re\D[7]turned.}
\li{And while \G[]Lennon \D[]read a \Em[]book on Marx, the \Am[]quartet practiced \C[]in the park}
\li{and \G[]we sang \D[]dirges \Em[]in the dark the \C[]day the \D[7]music \G[]died.\C* \G[]I started \D[7]singin'}
}

\refrain

\verse{
\li{\G[]Helter skelter \Am[]in the summer swelter - the \C[]birds flew off with a \Am[]fallout shelter}
\li{\Em[]Eight miles high and falling \D[]fast - it \G[]landed foul \D[]on the \Em[]grass}
\li{The \Am[]players tried for a \C[]forward pass with the \Em[]jester on the sidelines \A[7]in a \D[7]cast}
\li{The \Em[]half time air was \Am[]sweet perfume while the \Em[]seargeants played a \Am[]marching tune}
\li{we \C[]all got \G[]up to \A[7]dance but we \C[]never got the \D[7]chance.}
\li{'Cause the \G[]players \D[]tried to \Em[]take the field, but the \Am[]marching band re\C[]fused to yield}
\li{Do \G[]you re\D[]call what \Em[]was revealed the \C[]day the \D[7]music \G[]died.\C* \G[]We started \D[7]singin'}
}

\refrain

\verse{
\li{And \G[]there we were all \Am[]in one place, a \C[]generation \Am[]lost in space.}
\li{With \Em[]no time left, to \D[]start again. So come on, \G[]Jack be \D[]nimble, \Em[]jack be quick,}
\li{\Am[]Jack flash sat on a \C[]candlestick. 'Cause \Em[]fire is the \A[7]devil's only \D[7]friend.}
\li{And \Em[]as I watched him \Am[]on the stage  my \Em[]hands were clenched in \Am[]fists of rage.}
\li{no \C[]angel \G[]born in \A[7]hell could \C[]break that satan's \D[7]spell}
\li{And as the \G[]flames climbed \D[]high in\Em[]to the night to \Am[]light the sacri\C[]ficial rite}
\li{I saw \G[]Satan \D[]laughing \Em[]with delight, the \C[]day the \D[7]music \G[]died.\C* \G[]He was \D[7]singin' }
}

\refrain

\bridge{
\li{I \G[]met a \D[]girl who \Em[]sang the blues and I \Am[]asked her for some \C[]happy news}
\li{but \Em[]she just smiled and turned \D[]away.}
\li{I \G[]went \D[]down to the \Em[]sacred store where I \Am[]heard the music \C[]years before.}
\li{But the \Em[]man there said the \C[]music wouldn't \D[]play.}
\li{And \Em[]in the streets the \Am[]children screamed, the \Em[]lovers cried and the \Am[]poets dreamed.}
\li{But \C[]not a \G[]word was \Am[]spoken, the \C[]church bells all were \D[]broken.}
\li{And the \G[]three men \D[]I ad\Em[]mire most: the \Am[7]father, son and the \D[]Holy Ghost}
\li{They \G[]caught the \D[]last train \Em[]for the coast the \C[]day, the \D[7]music \G[]died.\C* \G}
\li{And they were singing:}
}

\refrain

\chorus{
\li{\G[]They were \D[7]singing, \G[]bye-\C[]bye, Miss A\G[]merican \D[]Pie. Drove my \G[]Chevy to the \C[]levee but the}
\li{\G[]levee was \D[]dry, them \G[]good ole \C[]boys were drinkin' \G[]whiskey and \D[]Rye,}
\li{singing \C[]this'll be the \D[7]day that I \G[]die.\C* \G}
}
}
\end{document}