\documentclass[../Liederbuch/LiederbuchGitarristen.tex]{subfiles}
\begin{document}
\song{Bohemian Rhapsody}{Queen}{3}{Englisch}{Rock}{

\intro{
\li{\Em[7]Is this the real life - \A[7]Is this just fantasy}
\li{\D[7]Caught in a \Am[7]land\D[7]slide - No \G[]escape from reality}
\li{\Em[]Open your eyes - Look \G[7]up to the skies and \C[]see}
\li{\Am[]I'm just a poor boy, \D[7]I need no sympathy}
\li{Because I'm \Gs[]easy \G[]come, \Fs[]easy \G[]go, \Gs[]little \G[]high, \Fs[]little \G[]low,}
\li{\C[]Any way the \G[/\B]wind blows, \Bb[°7]doesn't really \D[7/\A]matter to \D[7]me, to \G[7]me}
}

\verse{
\li{\G[7]Mama, just \Em[]killed a man, put a \Am[]gun against his head, pulled my \Am[]trigger, now he's \D[]dead,}
\li{\G[7]Mama, life had \Em[]just begun, but \Am[]now I've gone and \Am[/\Gs]thrown it \Am[/\G]all ~\Am[/\Fs]away ~~\Am[/\F]* \Am[/\E]}
\li{\C[]Mama \G[]oo\Am[]oh, didn't \Dm[]mean to make \Dm[/\C]you ~\Dm[/\Bb]cry ~\Dm[/\A]}
\li{If \G[]I'm not back again this time to\C[]morrow}
\li{Carry \G[]on, carry \Am[]on, as if \Fm[]nothing really mat\C[]ters \C* \G[7]}
}

\verse{
\li{\G[7]Too late, my \Em[]time has come,  sends \Am[]shivers down my spine, body's \Am[]aching all the \D[]time,}
\li{\G[]Goodbye everybody, I've \Em[]got to go, gotta \Am[]leave you all be\Am[/\Gs]hind and \Am[/\G]face \Am[/\Fs]the truth\Am[/\F]* \Am[/\E]}
\li{\C[]Mama \G[]oo\Am[]oh (any way the wind blows)}
\li{\Dm[]I don't want \Dm[/\C]to ~~\Dm[/\Bb]die ~~\Dm[/\A]- ~~I \G[]sometimes wish I'd never been born at \C[]all}
}

\bridge{
\chli{(\C[)] \G | \Am | \Dm | \G}
\chli{\C \G | \Am | \Dm | \Bb ~\Bb \A \Gs \G | \Fs}
}

\bridge{
\li{\B[]I \Fs[]see a \F[]little \Fs[]silhou\B[]etto \Fs[]of a \F[]man,}
\li{\Fs[]Scara\B[]mouche, \Fs[]scara\B[]mouche, \Fs[]will you \F[]do the \Fs[]Fan\B[]dan\Fs[]go}
\li{\As[]Thunderbolt and \F[]lightning, \A[]very very \Cs[]frightening \Fs[]me}
\li{\NC Galileo (Galileo) - Galileo (Galileo) - Galileo Figaro - Magnifico (oh)}

\li{\Gs[]I'm \G[]just a \Fs[]poor \G[]boy, \Gs[]no-\G[]body \Fs[]loves \G[]me. - \F[]He's \C[]just a \C[°]poor \C[]boy \F[]from a \C[]poor \C[°]fami\C[]ly.}
\li{\F[]Spare him his \C[/\E]life from this \D[]monstrosi\G[]ty. \F[]* \C[/\E]* \Ds[°]* \Dm[7]}
\li{\Gs[]Easy \G[]come, \Fs[]easy \G[]go, \Gs[]will you \G[]let me \Fs[]go?}
\li{\G[]Bis\C[]mil\G[]lah! \C[]No, we \G[]will not let you go. (let him go)}
\li{\G[]Bis\C[]mil\G[]lah! \G[]We will not let you go. (let him go)}
\li{\G[]Bis\C[]mil\G[]lah! \G[]We will not let you go. (let me go)}
\li{\G[]Will not let you go. (let me go) \G[]Will not let you go. (let me go) Oh\Ds[7]h (oh)}
\li{\Gsm[]No, ~\Fs[]no, \B[]no, \As[]no, \Ds[]no, \G[]no, \C[]no. \NC Oh, mama mia, mama mia}
\li{Mama \C[]mia, let me \G[]go. Be\C[]elze\F[]bub has a \B[]devil put a\Em[]side for \G[]me, for me, for me}
}

\bridge{
\chli{\C | \C | \C | \D}
}

\bridge{
\li{\G* So you think you can stone me and \C[]spit in my \G[]eye \Bb}
\li{\G* So you think you can love me and \C[]leave me to \F[]die}
\li{\Dm[]Oh, \G[]baby - \Dm[]can't do this to me, \G[]baby}
\li{\Dm[]Just gotta get \G[]out - \Dm[]just gotta get \G[]right outta \C[]here}
}

\bridge{
\chli{(\C[)] | \C | \C | \D | \NC}
\chli{\Ab  | \F | \G | \G | \NC}
\chli{\C \G | \Am \E \Am | \E \Am \G \C | \B \Em | \F \C }
}

\outro{
\li{\Am[]Nothing really mat\Em[]ters, \Am[]anyone can \Em[]see,}
\li{\Am[]Nothing really mat\Fm[]ters, \F[/\G]nothing really matters to \C[]me,}
\chli{(\C[)] \F[/\C] | \C \C[°]}
\chli{\G[/\B] \Gm[/\Bb] | \A \Bb[°] | \A \A[7] \D}
\li{\G[]Any\D[/\Fs]way the \D[°/\F]wind ~~\Em[7]blows \D}
}

\ifguitarversion
\footer{
Bb°7 = x1202x, C° = xx2121
}
\fi

}
\end{document}