\documentclass[../Liederbuch/LiederbuchGitarristen.tex]{subfiles}
\begin{document}
\song{Circles}{T:Gwendolyn Lee Zak M:Alan Bell}{}{Englisch}{}{

\verse{
\li{In \G[]days gone \D[]by, when the \C[]world was much \G[]younger,}
\li{men wandered in \D[]spring, born of \C[]winters \D[]cold \G[]knife. }
\li{Wandering of the \D[]games of the \C[]moon and the \G[]sunlight,}
\li{they saw the \D[]Lady and the\C[]Lord of \D[]our \G[]life.}
}

\chorus{
\li{\G[]Round and a\D[]round and a\C[]round turns the \G[]good earth,}
\li{all things must \D[]change as the \C[]seasons \D[]go \G[]by.}
\li{We are the \D[]children of the \C[]Lord and the \G[]Lady}
\li{whose mysteries we \D[]know, but we \C[]never \D[]know \G[]why.}
}

\verse{
\li{In \G[]all lands the \D[]people have \C[]tried to the \G[]good earth}
\li{ploughing and \D[]winging as the \C[]seasons \D[]de\G[]clared.}
\li{Waiting to reep of the \C[]rich golden \G[]harvest,}
\li{knowing their \D[]joy in the \C[]laughs that \D[]they \G[]shared.}
}

\refrain

\verse{
\li{Through \G[]Flandern and \D[]Wales and the \C[]green land of \G[]Ireland}
\li{in the kingdom of \D[]England and \C[]Scotland \D[]and \G[]Spain. }
\li{Circles grow \D[]up all a\C[]long the white \G[]coastline}
\li{and worked for the \D[]land and the \C[]sun and \D[]the \G[]rain.}
}

\refrain

\verse{
\li{\G[]Circles for \D[]healing and \C[]working and \G[]weather,}
\li{circles for \D[]knowing the \C[]moon and \D[]the \G[]sun,}
\li{circles for \D[]thanking the \C[]Lord and the \G[]Lady,}
\li{cirles for \D[]dancing the \C[]dance ne\D[]ver \G[]done.}
}

\refrain

}
\end{document}