\documentclass[../Liederbuch/LiederbuchGitarristen.tex]{subfiles}
\begin{document}
\song{Dear Mr. President}{P!nk}{3}{Englisch}{Pop}{

\intro{
\chli{\G[]\D[]\Em[]\D}
}

\verse{
\li{\G[]Dear Mr President\D[], come take a walk with me \Em* \D}
\li{Lets pretend\G[], we're just two people and, \D[]you're not better than me,}
\li{I'd like to\Em[], ask you some questions if we could\D[], speak honestly.}
\li{\C[]What do \C[/\B]you feel \Am[]when you see the \G[]homeless on the street?\D*}
\li{\C[]Who do \C[/\B]you pr\Am[]ay for at night bef\G[]ore you go to sleep?\D*}
\li{\C[]What do \C[/\B]you feel \Am[]when you look in the \Em[]mirror? \D*}
\li{Are you proud?\C[add9]}
}

\chorus{
\li{How do you \G[]sleep while the \D[]rest of us \Am[]cry? \Am[/\B]* \C}
\li{How do you \G[]dream when a \D[]mother has no \Am[]chance to say good\C[]bye?}
\li{How do you \G[]walk with your \D[]head held \Am[]high? \Am[/\B]* \C}
\li{Can you even \Em[]look me \D[]in the eye?\C[add9]}
\li{And tell me why \G* \D* \Em* \D}
}

\verse{
\li{\G[]Dear Mr president, \D[]were you a lonley boy, \Em[]Were you a lonley boy?\D}
\li{How can you say, \G[]no child is left behind\D[]? We're not dumb, and we're not blind}
\li{\Em[]They're all sitting in your cells \D[]while you pave the road to hell}
\li{\C[]What \C[/\B]kind of \Am[]father might take his own \G[]daughter right away\D[]?}
\li{\C[]And what \C[/\B]kind of \Am[]father might hates his own \G[]daughter if she were ga\D[]y?}
\li{\C[]I can only \C[/\B]imagine \Am[]what the first \Em[]lady has to \D[]say}
\li{you've come a \C[]long way, from whiskey and cocaine\C[add9]}
}

\refrain

\bridge{
\li{Let me tell you 'bot \G[]hard work\D[]: Minimum \Am[]wage with a baby on the \C[]way}
\li{Let me tell you 'bot \G[]hard work\D[]: Re-building your \Am[]house after the bombs took them \C[]away}
\li{Let me tell you 'bout \G[]hard work\D[]: Building a \Am[]bed out of a cardboard box\C[]}
\li{Let me tell you 'bout \G[]hard work, \D[]hard work, \Am[]hard \Am[/\B]work}
\li{\C[]You don't know nothing 'bout \Em[]hard work, \D[]hard work, Hard work!}
}

\outro{
\li{\G[]How do \D[]you sleep \Am[a]t night\C[]?}
\li{\G[]How do \D[]you walk, \Am[]with \Am[/\B]your \C[]head \Cm[]held \G[]high}
\li{\G[]Dear Mr president \D[]you'd never take a walk with me \Em* \D}
\li{ummm, would you?}
}

\footer{Das Lied ist ein offener Brief an George W. Bush (2001 - 2009 Präsident der Vereinigten Staaten). \\
C/H = 01022x | Cadd9 = 01003x | Am/H = 01222x}

}
\end{document}