\documentclass[../Liederbuch/LiederbuchGitarristen.tex]{subfiles} 
\begin{document}
\song{Fairytale of New York}{The Pogues \& Kirsty MacColl}{}{Englisch}{Punk}{
\intro{
\chli{\D \G \G \D}
}

\verse{
\li{Male:}
\li{\A[]It was Christmas \D[]Eve babe, in the \G[]drunktank}
\li{an old man \D[]said to me \dq Won't see a\A[]nother one\dq}
\li{and then he \D[]sang a song, \dq The rare old \G[]mountain dew\dq,}
\li{I turned my \D[]face away \G[]and dreamed \ch{(}a\A[]bout \D[)]you.}
}

\verse{
\li{\A[]Got on a \D[]lucky one, came in eigh\G[]teen to one,}
\li{I've got a \D[]feeling this year's for \A[]me and you,}
\li{so happy \D[]Christmas, I love you \G[]baby,}
\li{I can see a \D[]better time, \G[]when all our\ch{(} \A[]dreams come \D[)]true.\G}
}

\bridge{
\chli{\D \A}
}

\bridge{
\li{Female:}
\li{They've got \D[]cars big as \A[]bars, they've got \Bm[]rivers of \G[]gold,}
\li{but the \D[]wind goes right through you, it's no place for the \A[]old.}
\li{When you \D[]first took my \Bm[]hand on a \D[]cold Christmas \G[]Eve,}
\li{you \D[]promised me Broadway was \A[]waiting for \D[]me.}
}

\verse{
\li{You were \D[]handsome,}
\li{Male:}
\li{you were pretty, queen of New York \A[]City.}
\li{Both:}
\li{When the \D[]band finished \G[]playing they \A[]howled out for \D[]more.}
\li{Sinatra was swinging, all the drunks they were \A[]singing.}
\li{We \D[]kissed on the \G[]corner, then \A[]danced through the \D[]night.}
}

\chorus{
\li{The \G[]boys of the NY\Bm[]PD choir were \D[]singing \dq Galway \Bm[]Bay\dq}
\li{and the \D[]bells were \G[]ringing out \A[]for Christmas \D[]day.}
}

\bridge{
\chli{\G \A \A \D}
}

\verse{
\li{Female:}
\li{You're a \D[]bum, you're a punk,}
\li{Male:}
\li{you're an old slut on \A[]junk,}
\li{lying \D[]there almost \G[]dead on a \A[]drip in that \D[]bed.}
\li{Female:}
\li{You scum bag, you maggot, you cheap lousy \A[]faggot,}
\li{happy \D[]Christmas you \G[]arse, I pray \A[]god it's our \D[]last.}
}

\chorus{
\li{Both:}
\li{The \G[]boys of the NY\Bm[]PD choir still \D[]singing \dq Galway \Bm[]Bay\dq}
\li{and the \D[]bells were \G[]ringing out \A[]for Christmas \D[]day.}
}

\bridge{
\chli{\D \G \G \D}
}

\verse{
\li{Male:}
\li{\A[]I could have \D[]been someone.}
\li{Female:}
\li{Well so could \G[]anyone.}
\li{You took my \D[]dreams from me when I first \A[]found you.}
\li{Male:}
\li{I kept them \D[]with me babe, I put them \G[]with my own,}
\li{can't make it \D[]all alone, I've built my \G[]dreams a\A[]round \D[]you.}
}

\chorus{
\li{Both:}
\li{The \G[]boys of the NY\Bm[]PD choir still \D[]singing \dq Galway \Bm[]Bay\dq}
\li{and the \D[]bells were \G[]ringing out \A[]for Christmas \D[]day.}
}

\outro{
\chli{\A \D \D \G}
\chli{\G \D \D \A}
\chli{\A \D \D \G}
\chli{\G \D \D \G \A \D}
\rep{2}
}
}
\end{document}