\documentclass[../Liederbuch/LiederbuchGitarristen.tex]{subfiles} 
\begin{document}
\song{Fairytale gone bad}{Sunrise Avenue}{1}{Englisch}{Rock}{
\verse{
\li{This is the \Am[]end you \F[maj7]know.}
\li{\C[]Lady, the plans we had went all wrong.}
\li{\G[]We ain't nothing but \D[]fight and shout and \Am[]tears.}
\li{We got to a point I can't \F[maj7]stand.}
\li{I've \C[]had it to the limit, I can't be your man.}
\li{\G[]I ain't more than a \D[]minute away from \Am[]walking.}
}

\bridge{
\li{\F[]We can't \C[]cry the pain \F[]away.}
\li{We can't \C[]find a \G[]need to \F[]stay.}
\li{I slowly \C[]realized there's \F[]nothing on our \G[]side.}
}

\chorus{
\li{\Am[]Out of my life, out of my \F[maj7]mind,}
\li{out of the tears we can't \G[]deny.}
\li{We need to \C[]swallow all our \F[]pride}
\li{and leave this \G[]mess behind.}
\li{\Am[]Out of my head, out of my \F[maj7]bed,}
\li{out of the dreams we had, they're \G[]bad.}
\li{Tell them it's \C[]me who made you \F[]sad.}
\li{Tell them the fairytale \G[]gone \Am[]bad.}
}

\verse{
\li{Another \Am[]night and I \F[maj7]bleed.}
\li{They \C[]all make mistakes and so did we.}
\li{But \G[]we did something we can \D[]never turn back \Am[]right.}
\li{Find a new one to \F[maj7]fool.}
\li{\C[]Leave and don't look back. I won't follow.}
\li{\G[]We have nothing left. \D[]It's the end of \Am[]our time.}
}
\bridge{
\li{\F[]We can't \C[]cry the pain \F[]away.}
\li{We can't \C[]find a \G[]need to \F[]stay.}
\li{There's no more \C[]rabbits \G[]in my \F[]hat to make things \G[]right.}
}

\repref{2}

\outro{
\li{\brep\Am[]Tell them the fairytale gone bad.\erep}
}

\ifguitarversion{
\footer{
Fmaj7 = xx2211
}
}
}
\end{document}