\documentclass[../Liederbuch/LiederbuchGitarristen.tex]{subfiles} 
\begin{document}
\song{Fiddler's Green}{John Conolly}{}{Englisch}{Irisch/Schottisch}{

\verse{
\li{As I \C[]walked by the \F[]dockside one \C[]evening so \Am[]fair}
\li{to \C[]view the salt \F[]water and \C[]take the sea \G[7]air.}
\li{I \F[]heard an old fisherman \C[]singing this song:}
\li{Won't you take me a\F[]way, boys, me \C[]time is not \G[7]long!}
}
                 
\chorus{                 
\li{Wrap me \C[]up in me \G[]oilskin and \C[]jumper,}
\li{no \F[]more on the \C[]docks I'll be \G[]seen.}
\li{Just \F[]tell me old shipmates, I'm \C[]taking a trip, mates}
\li{and \G[7]I'll see you someday in Fiddler's \C[]Green.}
}

\verse{
\li{Now \C[]Fiddler's \F[]Green is a \C[]place I heard \Am[]tell}
\li{where \C[]fishermen \F[]go if they \C[]don't go to \G[7]hell.}
\li{Where the \F[]skies are all clear and the \C[]dolphins do play}
\li{and the cold coast of \F[]Greenland is \C[]far, far a\G[7]way.}
}

\refrain

\verse{
\li{Where the \C[]skies are all \F[]clear and there's \C[]never a \Am[]gale}
\li{and the \C[]fish jump on \F[]board with one \C[]swish on their \G[7]tail.}
\li{Where you \F[]lie at your leisure, there's \C[]no work to do}
\li{and the skipper's be\F[]low making \C[]tea for the \G[7]crew.}
}

\refrain

\verse{
\li{When you \C[]get on the \F[]docks and the \C[]long trip is \Am[]through,}
\li{there's \C[]pubs and there's \F[]clubs and there's \C[]lassies there, \G[7]too.}
\li{Where the \F[]girls are all pretty and the \C[]beer is all free}
\li{and there's bottles of \F[]rum growing \C[]from every \G[7]tree.}
}

\refrain

\verse{
\li{Now I \C[]don't want a \F[]harp nor a \C[]halo, not \Am[]me,}
\li{just \C[]give me a \F[]breeze and a \C[]good rolling \G[7]sea.}
\li{I'll \F[]play me old squeezebox as \C[]we sail along,}
\li{with the wind in the \F[]rigging to \C[]sing me a \G[7]song.}
}

\refrain
}
\end{document}