\documentclass[../Liederbuch/LiederbuchGitarristen.tex]{subfiles} 
\begin{document}
\song{Go West}{Pet Shop Boys}{}{Englisch}{Pop}{
\verse{
\li{To\C[]gether we will \G[]go our way, to\Am[]gether we will \Em[]leave some day,}
\li{to\F[]gether your hand \C[]in my hand, to\Dm[7]gether we will \G[]make our plan.}
}

\verse{
\li{To\C[]gether we will \G[]fly so high, to\Am[]gether tell all our \Em[]friends goodbye,}
\li{to\F[]gether we will \C[]start like new, to\Dm[7]gether this is \G[]what we'll do.}
}

\chorus{
\li{Go \C[]west life is \G[]peaceful there, go \Am[]west in the \Em[]open air,}
\li{go \F[]west where the \C[]skies are blue, go \Dm[7]west this is what we're \G[]gonna do.}
}

\verse{
\li{To\C[]gether we will \G[]love the beach, to\Am[]gether we will \Em[]learn and teach,}
\li{to\F[]gether change our \C[]pace of life, to\Dm[7]gether we will \G[]work and thrive.}
}

\verse{
\li{I \C[]love you I know \G[]you love me, \Am[]I want you how could I \Em[]disagree?}
\li{And \F[]that's why I make \C[]no protest, and \Dm[7]you say you will \G[]do the rest.}
}

\chorus{
\li{Go \C[]west life is \G[]peaceful there, go \Am[]west in the \Em[]open air,}
\li{go \F[]west baby, \C[]you and me, go \Dm[7]west this is our \G[]destiny.}
}

\chorus{
\li{Go \C[]west sun in \G[]winter time, go \Am[]west we will \Em[]do just fine,}
\li{Go \F[]west where the \C[]skies are blue, go \Dm[7]west this is what we're \G[]gonna do.}
}

\bridge{
\li{\E[]There, where the \Am[]air is free, we'll \Em[]be \G[]what we \C[]want to be.}
\li{\E[]Now, if we \Am[]make a stand, we'll \F[]find our \G[]promised land!}
}

\verse{
\li{I \C[]know that there are \G[]many ways, to \Am[]live there in the \Em[]sun or shade,}
\li{to\F[]gether we will \C[]find the place, to \Dm[7]settle where there's \G[]so much space.}
}

\verse{
\li{With\C[]out rush and the \G[]pace back East, the \Am[]hustling rustling \Em[]just to feed}
\li{I \F[]know I'm ready \C[]to leave too, so \Dm[7]that's what we are \G[]gonna do}
}

\bridge{
\li{\G[]What we're gonna do is}
}

\chorus{
{\forceChords
\li{Go \D[]west life is \A[]peaceful there, go \Bm[]west there in the \Fsm[]open air,}
\li{go \G[]west where the \D[]skies are blue, go \Em[7]west this is what we're \A[]gonna do.}
}
}

\chorus{
\li{Go \D[]west life is \A[]peaceful there, go \Bm[]west in the \Fsm[]open air,}
\li{go \G[]west baby, \D[]you and me, go \Em[7]west this is our \A[]destiny.}
}

\chorus{
\li{Go \D[]west sun in \A[]winter time, go \Bm[]west we will \Fsm[]feel just fine,}
\li{Go \G[]west where the \D[]skies are blue, go \Em[7]west this is what we're \A[]gonna do.}
}

\outro{
\li{\A[]C'mon, c'mon, c'mon, c'mon, Go \D[6add9]west}
}
}
\end{document}