\documentclass[../Liederbuch/LiederbuchGitarristen.tex]{subfiles}
\begin{document}
\song{Green Fields of France}{Eric Bogle}{}{Englisch}{}{

\verse{
\li{Oh \D[]how do you do, young \G[]Willy Mc\Em[]Bride?}
\li{Do you \A[]mind if I sit here down \D[]by your grave\A[]side?}
\li{And \D[]rest for a while 'neath the \G[]warm summer \Em[]sun,}
\li{I've been \A[]walking all day and \G[]I'm nearly \D[]done.}
\li{And I \A[]see by you gravestone you were \Em[]only nine\G[]teen}
\li{when you \A[]joined the great falling in \G[]nineteensix\A[]teen.}
\li{Well I hope you died quick and I \Em[]hope you died clean,}
\li{or, young \A[]Willy McBride, was it \G[]slow and ob\D[]scene?}
}

\chorus{
\li{Did they \A[]beat the drums slowly, did they \G[]play the fife \D[]lowly?}
\li{Did they \A[]sound the death march as they \G[]lowered you \A[]down?}
\li{Did the \G[]band play \dq the last post and \D[]chorus\dq?}
\li{Did the \G[]pipes play \dq the flowers of the \A[]fo\D[]rest\dq?}
}

\verse{
\li{And \D[]did you leave a wife or a \G[]sweetheart be\Em[]hind?}
\li{In \A[]some faithful heart is your \D[]memory en\A[]shrined?}
\li{And \D[]though you died back in \G[]ninteensix\Em[]teen,}
\li{to \A[]that loyal heart are you for\G[]ever nine\D[]teen?}
\li{Or \A[]are you a stranger without \Em[]even a \G[]name?}
\li{En\A[]closed down forever behind \D[]some old glass \A[]pane?}
\li{In an old photograph torn and \Em[]tattered, and stained,}
\li{and \A[]fading to yellow in a \G[]brown leather \D[]frame.}
}

\refrain

\verse{
\li{The \D[]sun shining down on these \G[]green fields of \Em[]France,}
\li{the \A[]warm wind blows gently and the \D[]red poppies \A[]dance.}
\li{The \D[]trenches have vanished long \G[]under the \Em[]plow,}
\li{There's no \A[]gas, no barbed wire, no \G[]guns firing \D[]now.}
\li{But \A[]here in this graveyard that's \Em[]still no man's \G[]land}
\li{the \A[]countless white crosses in \D[]mute witness \A[]stand.}
\li{To man's blind indifference to \Em[]his fellow men,}
\li{and a \A[]whole generation were \G[]butchered and \D[]damned.}
}

\refrain

\verse{
\li{And I \D[]can't help but wonder oh \G[]Willy Mc\Em[]Bride,}
\li{Do \A[]all those who lie here \D[]know why they \A[]died?}
\li{Did you \D[]really believe them when they \G[]told you the \Em[]cause?}
\li{Did you \A[]really believe that this \G[]war would end \D[]wars?}
\li{Well the \A[]suffering, the sorrow, the \Em[]glory, the \G[]shame,}
\li{the \A[]killing and dying, it was \D[]all done in \A[]vain.}
\li{Oh young Willy McBride it all \Em[]happened again,}
\li{and a\A[]gain, and again, and a\G[]gain, and a\D[]gain.}
}

\refrain

}
\end{document}