\documentclass[../Liederbuch/LiederbuchGitarristen.tex]{subfiles} 
\begin{document}
\song{Hairline fracture}{Rise Against}{3}{Englisch}{Punk}{
\intro{
\chli{\brep\C \C \A \A\erep{} \G}
\chli{\brep\Em \G \C \D\erep}
}

\verse{
\li{A \Em sinking ship, an \G awkward kiss, a \C chance to set things \D straight.}
\li{The \Em kind of hurt that \G burn and burns, \C like fires we \D can't contain.}
\li{We \Em hole up in a \G shelter made of \C bones and ice and \D there we'll wait.}
\li{To \Em start again, with \G steady hands. \C This time no\D[]thing gets in our \C way.}
\li{But as we \Am peer a little closer, what do we \C see?}
}

\chorus{
\li{\Am A crack in the \Em surface\D,}
\li{a flaw in the \below{(Plans we made together, almost \G buried in the \D sand.)}\C[]plan.}
\li{A cadence im\Em[]perfect\D,}
\li{like a building con\below{(Can we indemnify ourselves if we don't \G face what we're a\Am[]gainst?)}\C[]demned.}
}

\bridge{
\chli{\C \C \Am \D}
}

\verse{
\li{A \Em promise kept, the \G dirt unswept, a \C poorly worn dis\D[]guise.}
\li{A \Em child unloved that \G then grows up, \C to love what \D we despise.}
\li{We're \Em broken, but still \G breathing, we are \C wounded, but we are \D healing.}
\li{We \Em pick up right where \G we left off, \C breathe on the \D ashes that re\C[]main.}
\li{So that these \Am coals may become fire to guide our \C way.}
}

\refrain

\bridge{
\chli{\C}
}

\bridge{
\li{\Em I walk on wounds that seldom \C prove to slow me down,}
\li{\Em I laugh this constant pain a\C[]way. So you can't \D tell.}
\li{But there it lies under the \C smiles, it drains me mile after \D mile.}
\li{But seldom proves to slow me \C down. Here I \Em go.\G* \C* Here I \Em go.\G* \C* Here I \Em go.\G* \C}
\li{So we just \D hold on \C to what re\D[]mains of \C what we \D thought was \C lo-o-ost. \D But it's just}
}

\refrain

\outro{
\li{A crack in the \Em surface\D. A crack in the \C surface\G. \Am* \Am* \D* \Am}
}
}
\end{document}