\documentclass[../Liederbuch/LiederbuchGitarristen.tex]{subfiles} 
\begin{document}
\song{Hero of war}{Rise Against}{}{Englisch}{Punk}{
\verse{
\li{He said \dq\E[]Son, have you seen the \Gsm[]world?}
\li{Well, what would you \A[sus2]say, if I said that you \E[]could?}
\li{Just carry this \A[sus2]gun and you'll even get \E[]paid.\dq}
\li{I said \dq That sounds pretty \B[]good.\dq\B[add11]* \B[]* \B[add11]}
}

\verse{
\li{Black leather \E[]boots, spit-shined so \Gsm[]bright,}
\li{they cut off my \A[sus2]hair, but it looked al\E[]right.}
\li{We marched and we \A[sus2]sang, we all became \E[]friends,}
\li{as we learned how to \B[]fight.\B[add11]* \B[]* \B[add11]}
}

\chorus{
\li{A hero of \Csm[]war, yeah that's what I'll \A[sus2]be}
\li{And when I come \E[]home, they'll be damn proud of \B[]me.}
\li{I'll carry this \Csm[]flag, to the grave if I \A[sus2]must,}
\li{because it's the flag that I \E[]love and a flag that I \B[]trust.}
}

\verse{
\li{I kicked in the \E[]door, I yelled my com\Gsm[]mands,}
\li{the children, they \A[sus2]cried, but I got my \E[]man.}
\li{We took him a\A[sus2]way, a bag over his \E[]face,}
\li{from his family and his \B[]friends.\B[add11]* \B[]* \B[add11]}
}

\verse{
\li{They took off his \E[]clothes, they pissed in his \Gsm[]hands,}
\li{I told them to \A[sus2]stop, but then I joined \E[]in.}
\li{We beat him with \A[sus2]guns and batons not just \E[]once,}
\li{but again and a\B[]gain.\B[add11]* \B[]* \B[add11]}
}

\refrain

\verse{
\li{She \E[]walked through bullets and \Gsm[]haze,}
\li{I asked her to \A[sus2]stop, I begged her to \E[]stay.}
\li{But she pressed \A[sus2]on, so I lifted my \E[]gun}
\li{and I fired a\B[]way.\B[add11]* \B[]* \B[add11]}
}

\verse{
\li{The \E[]shells jumped through the \Gsm[]smoke}
\li{and into the \A[sus2]sand, that the blood now had \E[]soaked.}
\li{She col\A[sus2]lapsed with a flag in her \E[]hand,}
\li{a flag white as \B[]snow.\B[add11]* \B[]* \B[add11]}
}

\chorus{
\li{A hero of \Csm[]war, is that what they \A[sus2]see,}
\li{just medals and \E[]scars, so damn proud of \B[]me.}
\li{And I brought home that \Csm[]flag, now it gathers \A[sus2]dust,}
\li{but it's a flag that I \E[]love, it's the only flag I \B[]trust.}
}

\outro{
\li{He said \dq\E[]Son, have you seen the \Gsm[]world?}
\li{Well, what would you \A[sus2]say, if I said that you \E[]could?}
}
}
\end{document}