\documentclass[../Liederbuch/LiederbuchGitarristen.tex]{subfiles}
\begin{document}
\song{Hey there Delilah}{Plain White T's}{}{Englisch}{Pop}{

\intro{
\chli{\D \Fsm \D \Fsm}
}

\verse{
\li{\D[]Hey there, Delilah what's it \Fsm[]like in New York city?}
\li{I'm a \D[]thousand miles away but, girl, to\Fsm[]night you look so pretty,}
\li{Yes, you \Bm[]do, \G[]Times Square can't \A[]shine as bright as \Bm[]you,}
\li{I swear, it's \A[]true.}
}

\verse{
\li{\D[]Hey there, Delilah don't you \Fsm[]worry about the distance,}
\li{I'm right \D[]there, if you get lonely give this \Fsm[]song another listen,}
\li{close your \Bm[]eyes, \G[]listen to my \A[]voice, it's my dis\Bm[]guise.}
\li{I'm by your \A[]side}
}

\chorus{
\li{\D[]Oh it’s what you do to \Bm[]me, \D[]Oh it’s what you do to \Bm[]me,}
\li{\D[]Oh it’s what you do to \Bm[]me, \D[]Oh it’s what you do to \Bm[]me,}
\li{What you do to \D[]me.}
}

\verse{
\li{\D[]Hey there, Delilah, I know \Fsm[]times are gettin' hard,}
\li{but just \D[]believe me, girl someday I'll pay the \Fsm[]bills with this guitar,}
\li{we'll have it \Bm[]good, \G[]we'll have the \A[]life we knew we \Bm[]would,}
\li{my word is \A[]good.}
}

\verse{
\li{\D[]Hey there, Delilah, I've got \Fsm[]so much left to say,}
\li{if every \D[]simple song I wrote to you would \Fsm[]take your breath away,}
\li{I'd write it \Bm[]all, \G[]even more in \A[]love with me you'd \Bm[]fall,}
\li{we'd have it \A[]all.}
}

\refrain

\bridge{
\li{A \G[]thousand miles seems pretty far but \A[]they've got planes and trains and cars,}
\li{I'd \D[]walk to you if I had no other \Bm[]way.}
\li{Our \G[]friends would all make fun of us and \A[]we'd just laugh along because we'd \D[]know}
\li{that none of them have felt this \Bm[]way.}
\li{\G[]Delilah, I can promise you that \A[]by the time that we get through}
\li{the \Bm[]world will never ever be the same and you're to \A[]blame.}
}

\bridge{
\li{\D[]Hey there, Delilah you be \Fsm[]good, and don't you miss me,}
\li{two more \D[]years and you'll be done with school and \Fsm[]I'll be makin' history like I \Bm[]do}
\li{\G[]You know it's \A[]all because of \Bm[]you, \G[]we can do what\A[]ever we want \Bm[]to.}
\li{\G[]Hey there, De\A[]lilah, here's to \Bm[]you, this one's for \A[]you.}
}

\refrain

\outro{
\li{Oh \Bm* \D* \Bm* \D* \Bm* \D* \Bm* \D*}
}

}
\end{document}