\documentclass[../Liederbuch/LiederbuchGitarristen.tex]{subfiles} 
\begin{document}
\song{Irish soldier laddie}{Paddy McGuigan}{}{Englisch}{Irisch/Schottisch}{
\verse{
\li{\textquotesingle Twas one \C morning in July, I was \F walking to Tippe\C[]rary}
\li{when I heard a battle cry from the \D mountains over\G[7]head}
\li{I \C looked up to the sky, saw an \F Irish soldier \C laddie,}
\li{he looked at me right \G fearlessly and \C said:}
}

\chorus{
\li{Will you \G stand in the band like a \C true Irish man,}
\li{and go to fight the forces of the \G[7]crown?}
\li{Will you \C march with O'Neill to an \F Irish battle field,}
\li{for to\C[]night we're going to \G free old Wexford \C town.}
}

\verse{
\li{Said I \C to that soldier lad: Won't you \F take me to your \C captain.}
\li{It will be my pride and joy for to \D march with you to\G[7]day.}
\li{My young \C brother fell at Cork and my \F son at Ennis\C[]corthy,}
\li{and to the noble \G captain I did \C say:}
}

\chorus{
\li{I will \G stand in the band like a \C true Irish man,}
\li{and go to fight the forces of the \G[7]crown.}
\li{I will \C march with O'Neill to an \F Irish battle field,}
\li{for to\C[]night we're going to \G free old Wexford \C town.}
}

\verse{
\li{As we \C marched back again in the \F shadow of the \C evening,}
\li{with our banners flying low to the \D memory of the \G[7]dead,}
\li{we re\C[]turned to our homes, but with\F[]out our soldier \C laddie.}
\li{But I never will for\G[]get those words he \C said:}
}

\refrain

\chorus{
\li{I will \G stand in the band like a \C true Irish man,}
\li{and go to fight the forces of the \G[7]crown.}
\li{I will \C march with O'Neill to an \F Irish battle field,}
\li{for to\C[]night we're going to \G free old Wexford \C town.}
}

\footer{Das Lied behandelt Ereignisse der irischen Rebellion von 1798.}
}
\end{document}