\documentclass[../Liederbuch/LiederbuchGitarristen.tex]{subfiles}
\begin{document}
\song{Irish Rover}{trad.}{}{Englisch}{Irisch/Schottisch}{

\verse{
\li{On the \C[]fourth of July eighteen \F[]hundred and six,}
\li{we set \C[]sail from the \Am[]sweet cobh of \G[]Cork.}
\li{We were \C[]sailing away with a \F[]cargo of bricks}
\li{for the \C[]grand city \G[]hall in New \C[]York.}
\li{'Twas an \C[]elegant craft, she was \G[]rigged fore and aft,}
\li{and \C[]oh how the wild wind \G[]drove her!}
\li{She stood \C[]several blasts, she had \F[]twentyseven masts}
\li{and they \C[]called her the \G[]Irish \C[]Rover.}
}

\verse{
\li{We had \C[]one million bags of the \F[]best Sligo rags,}
\li{We had \C[]two million \Am[]barrels of \G[]stones.}
\li{We had \C[]three million sides of old \F[]blind horses hides,}
\li{we had \C[]four million \G[]barrels of \C[]bones.}
\li{We had \C[]five million hogs, \G[]six million dogs,}
\li{\C[]seven million barrels of \G[]porter.}
\li{We had \C[]eight million bales of old \F[]nanny goat tails}
\li{in the \C[]hold of the \G[]Irish \C[]Rover.}
}

\verse{
\li{There was \C[]Barney McGee from the \F[]banks of the Lee,}
\li{there was \C[]Hogan from \Am[]County Ty\G[]rone.}
\li{There was \C[]Johnny McGuirk who was \F[]scared stiff of work}
\li{and a \C[]chap from West\G[]meath called Ma\C[]lone.}
\li{There was \C[]Slugger O'Toole who was \G[]drunk as a rule,}
\li{and \C[]fighting Bill Tracy from \G[]Dover,}
\li{and your \C[]man Mick McCann from the \F[]banks of the Bann}
\li{was the \C[]skipper of the \G[]Irish \C[]Rover.}
}

\verse{
\li{We had \C[]sailed seven years when the \F[]measels broke out}
\li{and our \C[]ship lost it's \Am[]way in the \G[]fog.}
\li{Then the \C[]whole of the crew was re\F[]duced down to two,}
\li{just my\C[]self and the \G[]captain's old \C[]dog.}
\li{Then our \C[]ship struck a rock, oh \G[]Lord what a shock!}
\li{The \C[]bulkhead was turned right \G[]over.}
\li{Spun \C[]nine times around and the \F[]poor old dog was drowned,}
\li{I'm the \C[]last of the \G[]Irish \C[]Rover.}
}

}
\end{document}