\documentclass[../Liederbuch/LiederbuchGitarristen.tex]{subfiles} 
\begin{document}
\song{Ironic}{Alanis Morisette}{}{Englisch}{Rock}{
\verse{
\li{An \D[]old \G[]man \D[]turned ninety-\Em[]eight,}
\li{he won the \D[]lotte\G[]ry and \D[]died the next \Em[]day.}
\li{It's a \D[]black \G[]fly in your \D[]Chardon\Em[]nay,}
\li{it's a \D[]death row \G[]pardon two \D[]minutes too \Em[]late.}
\li{Isn't it i\D[]ronic\G[]? \D[]Don't you \Em[]think?}
}

\chorus{
\li{It's like \D[]rain \G[]on your \D[]wedding \Em[]day,}
\li{it's a \D[]free ride \G[]when you've \D[]already \Em[]paid.}
\li{It's the \D[]good ad\G[]vice that you \D[]just didn't \Em[]take.}
\li{And who \F[]would've \C[]thought it \D[]figures?}
}

\verse{
\li{Mr. \D[]Play It \G[]Safe was a\D[]fraid to \Em[]fly,}
\li{he \D[]packed his \G[]suitcase and kissed his \D[]kids good-\Em[]bye.}
\li{He waited his \D[]whole damn \G[]life to \D[]take that \Em[]flight}
\li{and as the \D[]plane crashed \G[]down he thought \dq\D[]Well isn't this \Em[]nice?\dq}
\li{And isn't it i\D[]ronic\G[]? \D[]Don't you \Em[]think?}
}

\refrain

\bridge{
\li{Well \C[maj7]life has a funny way of \D[]sneaking up on you.}
\li{When you think everything's \C[maj7]okay and everything's going \D[]right.}
\li{And \C[maj7]life has a funny way of \D[]helping you out}
\li{when you think everything's gone wrong and \C[maj7]everything blows up in your \D[]face.}
}

\verse{
\li{A \D[]traffic \G[]jam when you're \D[]already \Em[]late,}
\li{a \D[]no-smoking \G[]sign on your \D[]cigarette \Em[]break.}
\li{It's like \D[]ten thousand \G[]spoons when all you \D[]need is a \Em[]knife,}
\li{it's like meeting the \D[]man of my \G[]dreams and then meeting his \D[]beautiful \Em[]wife.}
\li{And isn't it i\D[]ronic\G[]? \D[]Don't you \Em[]think? A little too i\D[]ronic\G[], and yeah I \D[]really do \Em[]think.}
}

\refrain

\outro{
\li{\C[maj7]Life has a funny way of \D[]sneaking up on you.}
\li{\C[maj7]Life has a funny, funny way of \D[]helping you \C[maj7]out - helping you \D[]out.}
}
}
\end{document}