\documentclass[../Liederbuch/LiederbuchGitarristen.tex]{subfiles} 
\begin{document}
\song{Jessie}{Joshua Kadison}{}{Englisch}{Pop}{
\intro{
\chli{\brep\G \D[/\Fs] \Am \C\erep}
}

\verse{
\li{\G[]From a phone booth in \Am[]Vegas, Jessie \C[]calls at five a.\G[]m.}
\li{To tell me that she's \Am[]tired \C[]of all of \G[]them.}
\li{She says \dq Baby I've been \Am[]thinking about a \C[]trailer by the \G[]sea.}
\li{We can go to \Am[]Mexico: \C[]you, the cat, and \D[]me.}
\li{We drink te\Em[]quila \D[]and look for \C[]seashells.}
\li{Now \Em[]doesn't \D[]that sound \C[]sweet?\dq}
\li{\Em[]Jessie, you \D[]always \C[]do this}
\li{Every time I get back on my \D[]feet\C. \D* \C* \D}
}

\chorus{
\li{\G[]Jessie, paint your \C[]pictures, about \G[]how it's gonna \C[]be}
\li{By \G[]now I should know \C[]better, your \D[]dreams are never \Em[]free\D}
\li{But \G[]tell me all a\C[]bout our little \G[]trailer by the \C[]sea}
\li{\G[]Jessie you can \C[]always sell \D[]any dream to \Em[]me \D}
\li{\G[]Jessie you can \C[]always sell \D[]any dream to \G[]me}
}

\bridge{
\chli{\brep\G \D[/\Fs] \Am \C\erep}
}

\verse{
\li{She \G[]asks me how the \Am[]cat's been, I say \dq\C[]Moses, he's just \G[]fine.}
\li{He used to think a\Am[]bout you \C[]all the \G[]time.}
\li{We finally took your \Am[]pictures \C[]down off the \G[]wall.}
\li{Jessie how do you \Am[]always seem to \C[]know just when to \G[]call?\dq}
\li{She says: \dq\Em[]Get your \D[]stuff to\C[]gether.}
\li{Bring \Em[]Mose' and \D[]drive real \C[]fast.\dq}
\li{And \Em[]listening \D[]to her \C[]promise}
\li{I swear to God this time it's gonna \D[]last\C. \D* \C* \D}
}

\refrain

\bridge{
\li{I \Em[]love you \D[]in the \C[]sunshine,}
\li{lay you \Em[]down in the \D[]warm white \C[]sand}
\li{and \Em[]who knows \D[]maybe \C[]this time}
\li{things may turn out just the way you \D[]planned\C. \D* \C* \D}
}

\refrain

\outro{
\chli{\brep\G \D[/\Fs] \Am \C\erep}
}
}
\end{document}