\documentclass[../Liederbuch/LiederbuchGitarristen.tex]{subfiles} 
\begin{document}
\song{Lemon Tree}{Fools Garden}{}{Englisch}{Pop}{
\intro{
\chli{\Am \Em \Am \Em \Dm \Em (\Am \Em[)] \Am}
}

\verse{
\li{I'm \Am[]sitting here in a \Em[]boring room, it's \Am[]just another rainy Sunday \Em[]afternoon.}
\li{I'm \Am[]wasting my time, I got \Em[]nothing to do. I'm \Dm[]hanging around, I'm \Em[]waiting for you,}
\li{but \Dm[]nothing ever happens\Em[] - and I\ch{(} \Am[]wonder.\Em[)]* \Am}
}

\verse{
\li{I'm \Am[]driving around \Em[]in my car, I'm \Am[]driving too fast, I'm \Em[]driving too far.}
\li{I'd \Am[]like to change my \Em[]point of view. I \Dm[]feel so lonely, I'm \Em[]waiting for you,}
\li{but \Dm[]nothing ever happens\Em[] - and I\ch{(} \Am[]wonder.\Em[)]* \Am}
}

\chorus{
\li{I \C[]wonder how, I \G[]wonder why}
\li{\Am[]Yesterday you told me 'bout the \Em[]blue blue sky}
\li{And \F[]all that I can \G[]see is just a yellow \C[]lemon tree.\G[7]}
\li{I'm \C[]turning my head \G[]up and down,}
\li{I'm \Am[]turning turning turning turning \Em[]turning around}
\li{And \F[]all that I can \D[7]see is just another \G[]lemon tree.\G[7]}
}

\bridge{
\chli{\Am \Em \Am \Em \Dm \Em (\Am \Em[)] \Am}
\li{Dam dadoudi....}
}

\verse{
\li{I'm \Am[]sitting here, I \Em[]miss the power. I'd \Am[]like to go out, \Em[]taking a shower,}
\li{but \Am[]there's a heavy cloud in\Em[]side my head. I \Dm[]feel so tired, put my\Em[]self to bed,}
\li{where \Dm[]nothing ever happens \Em[]- and I\ch{(} \Am[]wonder.\Em[)]* \Am}
}

\bridge{
\li{\E[]Isolation - \Am[]Is not good for me, \G[]Isolation - \C[]I don't want to \E[]sit on a lemon tree.}
\li{I'm \Am[]stepping around in a \Em[]desert of joy, \Am[]Baby anyhow I'll get a\Em[]nother toy}
\li{and \Dm[7]everything will happen \Em[]- and you'll\ch{(} \Am[]wonder.\Em[)]* \Am}
}

\refrain

\outro{
\li{And I \G[]wonder - I wonder - I \C[]wonder how, I \G[]wonder why}
\li{\Am[]Yesterday you told me 'bout the \Em[]blue blue sky}
\li{And \F[]all that I can \G[]see, And \F[]all that I can \G[]see,}
\li{And \F[]all that I can \G[]see is just a yellow \C[]lemon tree.}
}
}
\end{document}