\documentclass[../Liederbuch/LiederbuchGitarristen.tex]{subfiles} 
\begin{document}
\song{Living next door to Alice}{Smokie}{}{Englisch}{Rock}{
\verse{
\li{\G[]Sally called when she got the word.}
\li{\C[]She said: \dq I suppose you've \D[]heard about \G[]Alice.\dq\D[7]}
\li{Well, I \G[]rushed to the window and I looked outside,}
\li{\C[]I could hardly believe my eyes,}
\li{as a \D[]big limousine rolled up into \G[]Alice's \D[7drive.]}
}

\chorus{
\li{I \G[]don't know why she's leaving or where she's gonna go}
\li{I \C[]guess she's got her reasons but I just don't want to know.}
\li{'Cause for \D[7]twenty-four years I've been living next door to \G[]Alice.\D[7]}
\li{\G[]Twenty-four years just waiting for the chance}
\li{to \C[]tell her how I feel and maybe get a second glance,}
\li{now I've \D[]got to get used to not \C[]living next \D[]door to \G[]Alice.\D[7]}
}

\verse{
\li{\G[]Grew up together, two kids in the park.}
\li{\C[]Carved our initials deep in the \D[]bark, \G[]me and \D[7]Alice.}
\li{Now she \G[]walks through the door with her head held high,}
\li{\C[]just for a moment I caught her eyes.}
\li{As a \D[]big limousine pulled slowly out of \G[]Alice's \D[7]drive.}
}

\refrain

\verse{
\li{\G[]Sally called back, and asked how I felt,}
\li{\C[]she said \dq I know how to \D[]help ...  \G[]get over Alice.\dq\D[7]}
\li{She said \dq Now \G[]Alice is gone, but I'm still here}
\li{- \C[]you know I've been waiting twenty-four years.\dq}
\li{And the \D[]big limousine disappeared.}
}

\chorus{
\li{I \G[]don't know why she's leaving or where she's gonna go}
\li{I \C[]guess she's got her reasons but I just don't want to know.}
\li{'Cause for \D[7]twenty-four years I've been living next door to \G[]Alice.\D[7]}
\li{\G[]Twenty-four years just waiting for the chance}
\li{to \C[]tell her how I feel and maybe get a second glance.}
\li{But I'll \D[]never get used to not \C[]living next \D[]door to \G[]Alice.\D[7]}
}

\outro{
\li{(slow down)}
\li{No, I'll \D[]never get used to not \C[]living next \D[]door to \G[]Alice.}
}
}
\end{document}