\documentclass[../Liederbuch/LiederbuchGitarristen.tex]{subfiles} 
\begin{document}
\song{Long forgotten sons}{Rise Against}{}{Englisch}{Punk}{
\intro{
\chli{\brep\Csm \A \Fs \Csm\erep}
\chli{\brep\Csm \A \B \B\erep}
}

\verse{
\li{\Csm Far from home, on a road unknown, where the \Fs vultures circle on winds that blow}
\li{from \B norther skies that \A haunt these \E waking \Csm moments.}
\li{On shadows cast by the mountain range, on \Fs calloused soles we find our way}
\li{through \B desperate eyes, we \A long for \E the ho\Csm[]rizon.}
\li{While the sun is \B rising, yeah.}
}

\chorus{
\li{We are the \Csm long \A forgotten \B sons}
\li{and \Csm daughters that \A don't belong to \B anyone.}
\li{We are a\Csm[]lone \A under this \B sun.}
\li{And we \Csm work to fix the \A work that you've un\B[]done.}
}

\bridge{
\chli{\Csm}
}

\verse{
\li{When \Csm cries for help go unanswered and \Fs signal fires just burn and burn}
\li{we \B wonder if we're \A waiting \E here for \Csm nothing.}
\li{'Cause our lips are sewn, our ears are filled, with the \Fs constant drone of the unfufilled.}
\li{But we'll \B never fall \A if we \E stand for \Csm something,}
\li{we stand for \B something, yeah.}
}

\refrain

\bridge{
\li{\A Don't fall, I see lights in the \B distance, they're not far a\A[]way.}
\li{Stand up, because the sky is turning \B gra-ay.}
\li{\A There's hope in these footsteps of per\B[]sistence, so don't go a\A[]stray.}
\li{These lights get closer every \B da-ay.}
}

\bridge{
\li{We are the \Csm long \A forgotten \Fs sons,}
\li{yeah we are the \Csm long \A forgotten \B sons.}
}

\refrain

\outro{
\li{What you've un\Csm[]done.}
}

\footer{
Calloused - engl. schwielig
}
}
\end{document}