\documentclass[../Liederbuch/LiederbuchGitarristen.tex]{subfiles} 
\begin{document}
\song{Lord of the dance}{Sydney Carter}{}{Englisch}{}{
\verse{
\li{I \G[]danced in the morning when the \Em[]world was be\G[]gun,}
\li{I \C[]danced in the \D[7]moon and the stars and the sun.}
\li{I \G[]came down from heaven and I \D[]danced on the \Em[]earth,}
\li{at \D[]Bethlehem I \C[]had my \G[]birth.}
}

\chorus{
\li{\G[]Dance, then, wher\Em[]ever you may \G[]be, \Em[]I am the lord of the \D[]dance, said he}
\li{And I'll \G[]lead you all, wher\Em[]ever you may \G[]be,}
\li{and I'll \D[]lead you all in the \G[]dance, said he}
}

\verse{
\li{I \G[]danced for the scribes and the \Em[]Phari\G[]see,}
\li{but \C[]they would not \D[7]dance and they wouldn't follow me.}
\li{I \G[]danced for the fishermen, \D[]James and \Em[]John,}
\li{they \D[]came with me and the \C[]dance went \G[]on.}
}

\refrain

\verse{
\li{I \G[]danced on the Sabbath and I \Em[]cured the \G[]lame,}
\li{the \C[]holy \D[7]people said it was a shame.}
\li{They \G[]cut and they stripped and they \D[]hung me \Em[]high}
\li{and they \D[]left me there on a \C[]cross to \G[]die.}
}

\refrain

\verse{
\li{I \G[]danced on a Friday when the \Em[]sky turned \G[]black,}
\li{it's \C[]hard to \D[7]dance with the devil on your back.}
\li{They \G[]buried my body and they \D[]thought I'd \Em[]gone,}
\li{but \D[]I am the dance and I \C[]still go \G[]on.}
}

\refrain

\verse{
\li{They \G[]cut me down, but I \Em[]leapt up \G[]high,}
\li{\C[]I am the \D[7]light that will never, never die.}
\li{I'll \G[]live in you if you \D[]live in \Em[]me,}
\li{\D[]I am the lord of the \C[]dance, said \G[]he.}
}

\refrain
\footer{Carter wurde zu dem Lied inspiriert von einer Statue des Gottes Shiva als tanzender Nataraja (König des Tanzes) auf seinem Schreibtisch.}
}
\end{document}