\documentclass[../Liederbuch/LiederbuchGitarristen.tex]{subfiles} 
\begin{document}
\song{Moonlight shadow}{Mike Oldfield}{}{Englisch}{Pop}{
\verse{
\li{The \Csm[]last that ever she \A[]saw him, \B[]carried away by a \E[]moonlight \B[]shadow.}
\li{He \Csm[]passed on worried and \A[]warning, \B[]carried away by a \E[]moonlight \B[]shadow.}
\li{\E[]Lost in a riddle last \B[]Saturday night,}
\li{\Csm[]far a\A[]way on the \B[]other side.}
\li{He was \E[]caught in the middle of a \B[]desperate fight}
\li{and she \Csm[]couldn't find \A[]how to push \B[]through.}
}

\verse{
\li{The \Csm[]trees that whisper in the \A[]evening, \B[]carried away by a \E[]moonlight \B[]shadow.}
\li{Sing a \Csm[]song of sorrow and \A[]grieving, \B[]carried away by a \E[]moonlight \B[]shadow.}
\li{\E[]All she saw was a silhou\B[]ette of a gun,}
\li{\Csm[]far a\A[]way on the \B[]other side.}
\li{He was \E[]shot six times by a \B[]man on the run}
\li{and she \Csm[]couldn't find \A[]how to push \B[]through.}
}

\chorus{
\li{\E[]I \B[]stay, \E[]I \B[]pray - I see \E[]you in \A[]heaven \B[]far away}
\li{\E[]I \B[]stay, \E[]I \B[]pray - I see \E[]you in \A[]heaven - \B[]one day}
}

\verse{
\li{\Csm[]Four a.m.\ in the \A[]morning, \B[]carried away by a \E[]moonlight \B[]shadow.}
\li{I \Csm[]watched your vision \A[]forming, \B[]carried away by a \E[]moonlight \B[]shadow.}
\li{\E[]Star was light in a \B[]silvery night,}
\li{\Csm[]far a\A[]way on the \B[]other side}
\li{Will you \E[]come to talk to \B[]me this night?}
\li{But she \Csm[]couldn't find \A[]how to push \B[]through.}
}

\refrain

\verse{
\li{\Csm[]Far a\A[]way on the \B[]other side.}
}

\verse{
\li{\E[]Caught in the middle of a \B[]hundred and five\Csm. { }{ } \A* \B}
\li{The \E[]night was heavy but the \B[]air was alive.}
\li{But she \Csm[]couldn't find \A[]how to push \B[]through\Csm. { }{ } \A}
}

\verse{
\li{\B[]Carried away by a \E[]moonlight \B[]shadow\Csm. { }{ } \A}
\li{\B[]Carried away by a \E[]moonlight \B[]shadow\E. \B}
\li{\Csm[]Far a\A[]way on the \B[]other side.}
}
}
\end{document}