\documentclass[../Liederbuch/LiederbuchGitarristen.tex]{subfiles}
\begin{document}
\song{Mr. Blue Sky}{Electric Light Orchestra}{}{Englisch}{Pop}{

\intro{
\li{\F[](Morning! Today's forecast calls for blue skies)}
}

\verse{
\li{\F[]Sun is shining in the sky, there ain't a \Em[7]cloud \A[]in \Dm[]sight,}
\li{it stopped \G[]raining every\Em[]body's in a \A[]play,}
\li{and don't you \Bb[]know, it's a \Bb[/\C]beautiful new \F[]day, he he \Bb[/\C]hey}
}

\verse{
\li{\F[]Running down the avenue, see how the \Em[7]sun \A[]shines \Dm[]brightly,}
\li{in the \G[]city on the \Em[]streets where once was \A[]pity }
\li{Mr. \Bb[]blue sky is \Bb[/\C]living here to\F[]day, he he \Bb[/\C]hey}
}

\chorus{
\li{\brep{}\Dm[]Mr. blue \Dm[/\C]sky please tell us \Bb[maj7]why}
\li{you had to \F[]hide away for \Gm[]so long (\F[]so long), where did \Eb[]we go wrong\Bb[]\erep \Bb[/\C]}
}

\bridge{
\chli{\F \Em[7] \A \Dm \G \Em \A[] \Bb \Bb[/\C] \F \Bb[/\C]}
}

\verse{
\li{\F[]And you with the pretty face, welcome to the \Em[7]hu-m\A[]an \Dm[]race,}
\li{A cele\G[]bration Mr. \Em[]blue sky's up there \A[]waiting }
\li{And to\Bb[]day is the \Bb[/\C]day we've waited \F[]for, ah ah \Bb[/\C]ahh}
}

\chorus{
\li{\Dm[]Mr. blue \Dm[/\C]sky please tell us \Bb[maj7]why}
\li{you had to \F[]hide away for \Gm[]so long (\F[]so long), where did \Eb[]we go wrong\Bb[]}
\li{\brep\Dm[]Hey there \Dm[/\C]Mr. blue, \Bb[maj7]we're so pleased to \F[]be with you}
\li{\Gm[]look around see \F[]what you do, \Eb[]everybody \Bb[]smiles at you\erep \Bb[/\C]}
}

\bridge{
\li{\F[]Mr. blue sky, \Em[7]Mis-\A[]ter \Dm[]blue \G[]sky,\Em[7]* \A[7]Mis-\A[]ter \Bb[]blue \Bb[/\C]sky \F[]guy \Bb[/\C]}
}

\verse{
\li{\F[]Mr. blue you did it right, but soon comes \Em[7]mis-\A[]ter \Dm[]night}
\li{creeping \G[]over now his \Em[]hand is on your \A[]shoulder}
\li{Never \Bb[]mind, I'll re\Bb[/\C]member you this, \Cs[]I'll re\Eb[]member you this \Dm[]way}
}

\chorus{
\li{\Dm[]Mr. blue \Dm[/\C]sky please tell us \Bb[maj7]why}
\li{you had to \F[]hide away for \Gm[]so long (\F[]so long), where did \Eb[]we go wrong\Bb[]}
\li{\Dm[]Hey there \Dm[/\C]Mr. blue (sky), \Bb[maj7]we're so pleased to \F[]be with you (sky)}
\li{\Gm[]look around see \F[]what you do, \Eb[]everybody \Bb[]smiles at you\Bb[/\C]}
}

\outro{
\chli{\brep\Dm \Dm[/\C] \Bb[maj7] \F[] \Gm[] \F[] \Eb[] \Bb[]\erep\ \F}
}

\ifguitarversion{
\footer{
B/C = x3x331, Bmaj7 = x13231
}
}
}
\end{document}