\documentclass[../Liederbuch/LiederbuchGitarristen.tex]{subfiles}
\begin{document}
\song{Nothing Suits Me Like a Suit}{How I Met Your Mother}{}{Englisch}{Film/Serie}{

\intro{
\chli{\Bm}
}

\verse{
\li{\E[]I know what you're thinking: \Fsm[]What's Barney been drinking, \A[]that girl was smoking \D[]hot?}
\li{\E[]Yes I could have nailed her, but \Fsm[]no it's not a failure 'cos there's \A[]one thing she is \D[]not}
\li{To \Csm[]score a 10 would be just fine - But I'd \Gs[]rather be dressed to the nines}
\li{\E[]It's a truth you can't re\A[]fu- \E[]u -\Fsm[]\ u - \Fs[]u - \B[]use: Nothing suits me like a \E[]suit}
}

\verse{
\li{\E[]Picture a world where \Fsm[]all the boys and girls are im\A[]peccably well \D[]dressed}
\li{That \E[]delivery guy in a \Fsm[]jacket and tie, that \A[]puppy in a double \D[]reast}
\li{That \Csm[]80's dude with mutton chop, that \Gs[]baby with a lollipop}
\li{\E[]That lady cop who's kinda \A[]cu - \E[]u -\Fsm[]\ u - \Fs[]u - \B[]ute. Nothing suits 'em like a \A[]suit}
}

\chorus{
\li{\A[](Suits) Wingman I can wear}
\li{\Csm[](Suits) They're oh so debonair}
\li{\Fsm[](Suits) The perfect way to snare a \E[]girl with daddy \Fs[]iss\A[]ue\B[]s \C}
\li{\C[](Suits) In navy, blue or black,}
\li{\Csm[]Check out this \B[]perfect rack}
\li{\A[]I want to \E[]give them a \Fsm[]squeeze (Oh really?)}
\li{Then \D[]answer these \Csm[]questions if you \B[]please}
}

\bridge{
\li{\Csm[]What would you do if you had to chose between your suits and a pot of gold? (Suits)}
\li{\A[]What would you say if you gave your suits away and in return you'd never grow old? (Suits)}
\li{\Fsm[]What would you pick? One million chicks or a single three piece suit. (It's moot.)}
\li{\B[]What if world peace were within your reach? (Alalalala!)}
\li{\NC I'm gonna stop you right there. It's suits. C'mon Lily. Get your head outta your ass.}
\li{\NC Two! Three! Four! \Fsm* \As* \B* \Cs}
}

\outro{
\li{\E[]Girls will go and \Fsm[]girls will come but there's \A[]only one abso\D[]lute.}
\li{Every \E[]bro on the go needs to \Fsm[]know that there's no ac\A[]cepted substi\D[]tute.}
\li{I'm \Csm[]sorry suits, let's make amends? My \Gs[]Sunday best are my best friends.}
\li{\E* Send Casual \A[]Friday down the \E[]laun\Fs[]dry \B[]chute. - \Cs[]}
\li{'cos \A[]nothing suits the \Fs[]undisputed \E[]oft-saluted \Gs[]suitor of re\Csm[]pute \E[]}
\li{\A[]Like \B[]a - \NC Wait for it -}
\li{Su - \E[]u -\Fsm[]\ u - \below{(nothing suits him \Am[]like \D[]a \E[]suit)}\A[]uit!}
}

}
\end{document}