\documentclass[../Liederbuch/LiederbuchGitarristen.tex]{subfiles} 
\begin{document}
\song{Prayer of the refugee}{Rise Against}{-1}{Englisch}{Punk}{
\intro{
\chli{\brep\Em \C \Em \C\erep}
}

\verse{
\li{\Em Warm yourself by the \C fire, son, and the \D morning will come \Am soon.}
\li{\Em I'll tell you stories of a \C better time, in a \G place that we once \Em knew.}
\li{\Em Before we packed our bags and \C left all this be\D[]hind us in the \Am dust,}
\li{\Em We had a place that we could \C call home, and a \G life no one could \Em touch.}
}

\chorus{
\li{\brep Don't hold me \Em up now, I can stand my \G own ground,}
\li{I don't need your \D help now, you will let me \C down, down, down!\erep}
}

\bridge{
\li{\C Down\Em!}
}

\verse{
\li{\Em We are the angry and the \C desperate, the \D hungry, and the \Am cold.}
\li{\Em We are the ones who kept \C quiet, and always \G did what we were \Em told.}
\li{\Em But we've been sweating while you \C slept so calm, in the \D safety of your \Am home.}
\li{\Em We've been pulling out the \C nails that hold up \G everything you've \Em known.}
}

\refrain

\bridge{
\li{\Am So open your \G eyes child, let's be on our \Am way.}
\li{Broken windows and \G ashes are guiding the \Am way.}
\li{Keep quiet no \G longer, we'll sing through the \F day,}
\li{Of the lives that we've \Em lost, and the lives we've re\C[]claimed. \Em Go!}
}

\bridge{
\chli{\brep\G \D \C \Em\erep}
\chli{\brep\Em \C \Em \C\erep}
}

\refrain

\outro{ 
\li{\below{(I don't need your \G help, I'll stand my ground)}Don't hold me \Em up...}
\li{\below{(I don't need your help)}Don't hold me \D up... \C No! No! No!}
\li{\below{(I don't need your \G help, I'll stand my ground)}Don't hold me \Em up!}
\li{\below{(I don't need your help, I'll stand my ground)}Don't hold me \D up!}
\li{Don't let me \C down, down, down, down, \Em down!}
}
}
\end{document}