\documentclass[../Liederbuch/LiederbuchGitarristen.tex]{subfiles}
\begin{document}
\song{Roadie}{Tenacious D}{}{Englisch}{Rock}{

\intro{
\chli{\brep \E[5] \E[sus4] \Em\erep ~ \D \E}
}

\verse{
\li{Well it's \E[5]3pm time to \E[sus4]lug the \Em[]gear, got to \E[5]get it on the stage,}
\li{my muscles \D[]flex, my fucking sweat will save the \E[]day. \E[sus4]* \E}
\li{When I \E[5]check the mic, I fucka \E[sus4]check the \Em[]mic, I fucka \E[5]checka checka 1 2 3}
\li{I plug it \D[]in, I make it sound as good as it \E[]can be.}
\li{'cause the \E[5]rock is rock, and the \E[sus4]road is \Em[]road,}
\li{got'a \E[5]take the mic, he got \E[5]take \E[sus4]contr\Em[]ol,}
\li{got'a \D[]get that shit up on that fucking \E[]stage.\E[sus4]* \E}
\li{Cuz the \E[5]roadie knows what the \E[sus4]roadie \Em[]knows}
\li{And the \E[5]roadie knows that he \E[5]wears \E[sus4]black \Em[]clothes}
\li{And he \D[]hides off in the shadows of the \E[]stage \E[sus4]* \E}
}

\chorus{
\li{Because the \C[]roadie \A[sus2]looks a 1000 miles with \E[]his eyes}
\li{And when the \C[]crowd roars, \A[sus2]Brings a teardrop to the roadies \E[]eyes, Tears of pride}
\li{Because he \C[]brought you the show, But \A[sus2]you will never know}
\li{\C[]He's changing the strings, While \A[sus2]hiding in the wings}
\li{No \C[]matter how hard, \A[sus2]the show must \E[]go on}
}

\verse{
\li{\E[5]Then a beautiful girl come to me she says, \dq hey can i suckka your dick\dq}
\li{I say \D[]yes, I am in \E[]love}
\li{\E[5]Then she quickly said, \dq I sucked your dick, now gimme that backstage pass\dq}
\li{I do not \D[]want you roadie, I want K.G's \E[]chode}
}

\chorus{
\li{I'm \C[]standing at the threshold of your \A[sus2]dreams}
\li{With\C[]out me there'd be no sound from those \A[sus2]amps}
\li{With\C[]out me there'd be no lights on the \A[sus2]stage}
\li{But you don't applaud for \E[]me}
}

\outro{
\li{I am the \C[]roadie: \A[sus2]lonesome warrior searching for a \E[]soul (no!)}
\li{I am the \C[]roadie: \A[sus2]I make the rock \E[]go!}
\li{\C[]Roa\A[sus2]die, \C[]Roa\A[sus2]die, \C[]Ro-\A[sus2]a-d-i\E[]-e}
}

\footer{
Ein Roadie ist ein mitreisender Veranstaltungstechniker bei Konzerten von Musikern. Roadies sind für den Auf- und Abbau von Musikinstrumenten und Verstärkern sowie von PA- und Lichtanlagen zuständig. Der Begriff Roadie ist vom englischen Wort Road (Straße) abgeleitet. Er verdeutlicht, dass Roadies einen Großteil ihres Berufslebens auf Reisen verbringen. Sie reisen häufig den Künstlern voraus, um vor den Veranstaltungen rechtzeitig den Aufbau erledigen zu können.

\g{\ \\ E5 = 022400}
}

}
\end{document}