\documentclass[../Liederbuch/LiederbuchGitarristen.tex]{subfiles} 

\begin{document}
\song{The Boxer}{Simon \& Garfunkel}{2}{Englisch}{Folk}{

\verse{
\li{\A[]I am just a poor boy, though my story is seldom \Fsm[]told.}
\li{I have squandered my \E[]resistance,}
\li{For a \E[7]pocketful of \E[]mumbles, such are \A[]promises.}
\li{All lies and \Fsm[]jests, still a \E[]man hears what he \D[]wants to hear}
\li{and disregards the \A[]rest.}
\li{\E[]Hmm… \D* \E* \E[7]* \E* \A*}
}

\verse{
\li{When I \A[]left my home and my family I was no more than a \Fsm[]boy,}
\li{In the \E[]company of strangers,}
\li{In the \E[7]quiet of the \E[]railway station, \A[]runnin' scared.}
\li{Laying \Fsm[]low, seeking \E[]out the poorer \D[]quarters,}
\li{Where the ragged people \A[]go.}
\li{Lookin' \E[]for the places, \D[]only \E[]they \E[7]would \A[]know.}
}

\chorus{
\li{Lei-la-\Fsm[]lei - Lei-la-\Csm[]lei la lei-la-lie}
\li{Lei-la-\Fsm[]lei - Lei-la-\E[]lei la la la lei la la la la \A[]lei}
}

\verse{
\li{Asking \A[]only workman's wages I come lookin' for a \Fsm[]job,}
\li{But I get no \E[]offers,}
\li{Just a \E[7]come-on from the \E[]whores on Seventh \A[]Avenue.}
\li{I do de\Fsm[]clare there were \E[]times when I was so \D[]lonesome,}
\li{I took some comfort \A[]there.}
\li{\E[]La la la… \D* \E* \E[7]* \E* \A*}
}

\refrain

\verse{
\li{Then I'm \A[]laying out my winter clothes, and wishing I was \Fsm[]gone, goin' \E[]home}
\li{Where the \E[7]New York City \E[]winters aren't \A[]bleedin me, \Csm[]leadin' me \Fsm[] goin' \E[]home.}
}

\bridge{
\li{In the \A[]clearing stands a boxer, and a fighter by his \Fsm[]trade,}
\li{And he \E[]carries the reminders}
\li{of \E[7]every glove that \E[]laid him down or \A[]cut him 'til he cried out}
\li{In his anger and his \Fsm[]shame, \dq I am \E[]leaving, I am \D[]leaving.\dq}
\li{But the fighter still re\A[]mains}
\li{\E[]Hmm… \D* \E* \E[7]* \E* \A*}
}

\repref{5}

}
\end{document}