\documentclass[../Liederbuch/LiederbuchGitarristen.tex]{subfiles}
\begin{document}
\song{The Mermaid}{trad.}{}{Englisch}{}{

\verse{
\li{It was \G[]Friday morn' when \D[]we set \G[]sail}
\li{and we \C[]were not \D[]far from the \G[]land}
\li{when our captain, he spied a \D[]mermaid so \G[]fair}
\li{with a \C[]comb and a \D[]glass in her \G[]hand.}
}

\chorus{
\li{And the ocean waves do roll}
\li{and the stormy winds do \D[]blow.}
\li{And \G[] we poor sailors, we're \C[]skippin' at the \G[]top}
\li{while the \C[]landlubbers \D[]lie down be\G[]low, below, below,}
\li{while the \C[]landlubbers \D[]lie down be\G[]low.}
}

\verse{
\li{Then up spoke the captain \D[]of our gallant \G[]ship}
\li{and a \C[]fine old \D[]man was \G[]he.}
\li{\dq This fishy mermaid has \D[]warned me of our \G[]doom:}
\li{we shall \C[]sink to the \D[]bottom of the \G[]sea.\dq}
}

\refrain

\verse{
\li{Then up spoke the mate \D[]of our gallant \G[]ship}
\li{and a \C[]fine spoken \D[]man was \G[]he.}
\li{He said \dq I have a wife in \D[]Brooklyn by the \G[]sea }
\li{and to\C[]night a \D[]widow she will \G[]be.\dq}
}

\refrain

\verse{
\li{Then up spoke the cabin-boy \D[]of our gallant \G[]ship}
\li{and a \C[]brave young \D[]lad was \G[]he.}
\li{\dq Oh I have a sweetheart in \D[]Salem by the \G[]sea }
\li{and to\C[]night she'll be \D[]weepin' for \G[]me.\dq}
}

\refrain

\verse{
\li{Then up spoke the cook \D[]of our gallant \G[]ship}
\li{and a \C[]crazy old \D[]butcher was \G[]he.}
\li{He said \dq I care much more for my \D[]pots and my \G[]pans}
\li{than I  \C[]do for the \D[]bottom of the \G[]sea.\dq}
}

\refrain

\verse{
\li{Then three times 'round \D[]spun our gallant \G[]ship}
\li{and \C[]three times \D[]'round spun \G[]she.}
\li{Three times 'round \D[]spun our gallant \G[]ship}
\li{and she \C[]sank to the \D[]bottom of the \G[]sea.}
}

\refrain

}
\end{document}