\documentclass[../Liederbuch/LiederbuchGitarristen.tex]{subfiles} 
\begin{document}
\song{This is letting go}{Rise Against}{1}{Englisch}{Punk}{
\intro{
\chli{\brep\Em \Em \G \D\erep}
\chli{\Em \C \D \D}
}

\verse{
\li{\Em Once upon a \C time I could take \G anything, \D anything.}
\li{\Em Always stepped in \C time, re\D[]gardless of the beat.}
\li{I moved my \Em feet, I carried \C weight, what I \G could not do I \D faked.}
\li{And \Em I dug seeking \C treasure, \D just to wake up in an early \C grave.}
\li{So I \D stopped right there and said:}
}

\chorus{
\li{Go on a\G[]lone, 'cause I won't \D follow, this isn't \Em giving up, no this is letting \C go.}

\li{Out with the \G old dreams I've \D borrowed the path I \Em carve from here on out will be my \C own.}
\li{The path will be my own.\Em* \C* \G* \D* \Em* \C* \D* \D*}
}

\verse{
\li{\Em This is the part where the \C needle skips and the \G chorus plays like a \D sink that drips.}
\li{A \Em syllable re\C[]peating, like a \D warning we aren't heeding.}
\li{Until \Em all of a sudden we \C notice it, when the \G wheels brace and the \D tires grip.}
\li{A \Em map we've been mis\C[]reading, a de\D[]feat we're not conceding until \C now.}
\li{There must be \D some other way out.}
}

\chorus{
\li{Go on a\G[]lone, 'cause I won't \D follow, this isn't \Em giving up, no this is letting \C go.}

\li{Out with the \G old dreams I've \D borrowed the path I \Em carve from here on out will be my \C own.}
\li{A path to take me home.\forceChords{\G* \C* \G* \C}}
}

\bridge{
\li{\Em The wind died, \C the whole world ceased to \G move.}
\li{Now so quiet, \Am her beating heart became a \Em boom.}
\li{We locked eyes, \C for just a moment or \G two.}
\li{She asked \dq Why?\dq, I said \dq\Am I don't know why. I just \Em know:\dq}
\li{The wind \C died, \G the whole \Am world ceased to \Em move.}
\li{Now so \C quiet, \G her beating heart be\Am[]came a \Em boom.}
\li{We locked \C eyes, \G for just a \Am moment or \Em two.}
\li{She asked \dq \C Why?\dq, I said \dq\G I don't know \Am why. I just \C know, \D I just know:\dq}
}

\chorus{
\li{Go on a\G[]lone, 'cause I won't \D follow, this isn't \Em giving up, no this is letting \C go.}
\li{I'll make the \G most of all this \D sorrow, I tried to \Em brave this discontent but now I'm \C through.}
\li{I'm letting go of \G you-oh-oho. \D Wo-oh-oho. This is letting \Em go-o-oh.}
\li{\C This is letting \G go-oh-oho. Wo-oh. This is letting \Em go-o-\C[]oh.}
\li{Once upon a time I could take \G anything, \Am anything.}
}
}
\end{document}