\documentclass[../Liederbuch/LiederbuchGitarristen.tex]{subfiles} 
\begin{document}
\multicolsong{When I'm sixty-four}{The Beatles}{}{Englisch}{Pop}{
\verse{
\li{\C[]When I get older losing my hair,}
\li{Many years from \G[]now,}
\li{\ch{}Will you still be sending me a valentine}
\li{\sch{(}\G[]Birth\A[)]day\ch{(} \Bb[]gree\B[)]tings \C[]bottle of wine?}
}

\chorus{
\li{\C[]If I'd been out till quarter to three}
\li{\C[7]Would you lock the \F[]door,}
\li{Will you still \Fm[]need me,}
\li{\C[/\G]will you still \A[]feed me,}
\li{\D]When I'm \G[7]sixty-\C[]four?}
}

\bridge{
\li{\Am[]You'll be older \E[]too,}
\li{(\Am[]ah ah \below{And if you \Dm[]say the word,}ah ah ah)}
\li{\F[]I could \G[]stay with \C[]you.\G}
}

\verse{
\li{\C[]I could be handy mending a fuse}
\li{When your lights have \G[]gone.}
\li{\ch{}You can knit a sweater by the fireside}
\li{\sch{(}\G[]Sun\A[)]day\ch{(} \Bb[]mor\B[)]nings \C[]go for a ride.}
}

\chorus{
\li{\C[]Doing the garden, digging the weeds,}
\li{\C[7]Who could ask for \F[]more?}
\li{Will you still \Fm[]need me,}
\li{\C[/\G]will you still \A[]feed me,}
\li{\D[]When I'm \G[7]sixty-\C[]four?}
}

\bridge{
\li{\Am[]Every summer we can rent a cottage}
\li{in the Isle of \G[]Wight,}
\li{If it's not too \Am[]dear.}
\li{We shall scrimp and \E[]save}
\li{(\Am[]ah ah \below{Grandchildren \Dm[]on your knee}ah ah ah)}
\li{\F[]Vera, \G[]Chuck, and \C[]Dave\G* \sch{(}\G* \B[)] \sch{(}\D* \F[)]}
}

\verse{
\li{\C[]Send me a postcard, drop me a line,}
\li{Stating point of \G[]view.}
\li{\ch{}Indicate precisely what you mean to say}
\li{\sch{(}\G[]Yours \A[)]si\ch{(}n\Bb[]cere\B[)]ly, \C[]wasting Away.}
}

\chorus{
\li{\C[]Give me your answer, fill in a form}
\li{\C[7]Mine for ever\F[]more}
\li{Will you still \Fm[]need me,}
\li{\C[/\G]will you still \A[]feed me,}
\li{\D[]When I'm \G[7]sixty-\C[]four?}
}
}
\end{document}