\documentclass[../Liederbuch/LiederbuchGitarristen.tex]{subfiles} 
\begin{document}
\song{Whiskey in the jar}{trad. irisch}{}{Englisch}{Irisch/Schottisch}{
\verse{
\li{As \G[]I was going over, the \Em[]far famed Kerry mountains.}
\li{I \C[]met with captain Farrell and his \G[]money he was \Em[]counting.}
\li{I \G[]first produced me pistol, and \Em[]then produced me rapier:}
\li{I said '\C[]Stand and deliver' for he \G[]was a bold de\Em[]ceiver.}
}

\chorus{
\li{Mush a \D[]ring dum a doo dum a dah, \G[]whack fol the daddy o,}
\li{\C[]whack fol the daddy o, there's \G[]whiskey \D[]in the \G[]jar.}
}

\verse{
\li{I \G[]counted out his money, it \Em[]made a pretty penny.}
\li{I \C[]put it in me pocket and I \G[]took it home to \Em[]Jenny.}
\li{She \G[]sighed and she swore that she \Em[]never would deceive me.}
\li{But the \C[]devil take those women, for they \G[]never can be \Em[]easy.}
}

\refrain

\verse{
\li{I \G[]went up to my chamber, all \Em[]for to take a slumber.}
\li{I \C[]dreamt of gold and jewels, and for \G[]sure it was no \Em[]wonder.}
\li{That \G[]Jenny drew me charges and she \Em[]filled them up with water,}
\li{and \C[]sent for Captain Farrell to be \G[]ready for the \Em[]slaughter.}
}

\refrain

\verse{
\li{It was \G[]early in the morning be\Em[]fore I rose to travel.}
\li{Up \C[]came a band of footmen and \G[]likewise captain \Em[]Farrell.}
\li{I \G[]first produced me pistol, for she \Em[]stole away me rapier.}
\li{But I \C[]couldn't shoot the water, so as \G[]prisoner I was \Em[]taken.}
}

\refrain

\verse{
\li{Now \G[]some take delight in the \Em[]carriages a-rollin'}
\li{And \C[]some take delight in the \G[]hurling and the \Em[]howlin'}
\li{But \G[]I take delight in the \Em[]juice of the barley}
\li{And \C[]courtin' pretty fair maids in the \G[]morning bright and \Em[]early.}
}

\refrain

\verse{
\li{If \G[]anyone can aid me, it's me \Em[]brother in the army.}
\li{If \C[]I can find his station, in \G[]Cork or in Kil\Em[]larney.}
\li{And \G[]if he'll come and join me, we'll go \Em[]rovin' near Kilkenny.}
\li{And I'm \C[]sure he'll treat me better than me \G[]own a-sporting \Em[]Jenny.}
}

\refrain
\footer{Das Lied handelt in der Ichform von einem Raubritter, der in den Bergen bei Cork und Kerry einen Captain namens Farrel 체berf채llt und dabei Gold erbeutet, jedoch von Jenny, zu der er eine Liebesbeziehung aufrecht erh채lt, verraten wird. Das Lied stammt vermutlich urspr체nglich aus dem 17. oder 18. Jahrhundert. Jar = engl. Krug, Glas.}
}
\end{document}