\documentclass[../Liederbuch/LiederbuchGitarristen.tex]{subfiles} 
\begin{document}
\song{Ye Jacobites by name}{trad. schottisch/Robert Burns}{}{Englisch}{Irisch/Schottisch}{
\chorus{
\li{Ye \Am[]Jacobites by name lend an \C[]ear, lend an \G[]ear}
\li{Ye \Am[]Jacobites by name lend an ear}
\li{Ye \C[]Jacobites by name your \G[]faults I will proclaim}
\li{Your \Am[]doctrines I might blame, you shall \C[]hear, you shall \G[]hear.}
\li{Your \Am[]doctrines I might blame, you shall hear.}
}

\verse{
\li{What is \Am[]right, and what is wrong, by the \C[]law, by the \G[]law?}
\li{What is \Am[]right, and what is wrong, by the law?}
\li{What is \C[]right, and what is wrong? A \G[]short sword and a long,}
\li{A \Am[]weak arm and a strong, for to \C[]draw, for to \G[]draw!}
\li{A \Am[]weak arm and a strong, for to draw!}
}

\refrain

\verse{
\li{What \Am[]makes heroic strife, famed a\C[]far, famed a\G[]far?}
\li{What \Am[]makes heroic strife famed afar?}
\li{What \C[]makes heroic strife? To \G[]whet th' assassin's knife,}
\li{Or \Am[]hunt a parent's life, wi bloody \C[]war, wi bloody \G[]war!}
\li{Or \Am[]hunt a parent's life, wi bloody war!}
}

\refrain

\verse{
\li{Then \Am[]let your schemes alone, in the \C[]state, in the \G[]state!}
\li{Then \Am[]let your schemes alone, in the state!}
\li{Then \C[]let your schemes alone, a\G[]dore the rising sun,}
\li{And \Am[]leave a man alone, to his \C[]fate, to his \G[]fate!}
\li{And \Am[]leave a man alone, to his fate!}
}

\repref{2}
\footer{Ein traditionelles schottisches Volkslied, das auf die Jakobitenaufstände 1688-1745 zurück geht. Der hier gedruckte Text stammt von Robert Burns.}
}
\end{document}