\documentclass[../Liederbuch/LiederbuchGitarristen.tex]{subfiles}
\begin{document}
\multicolsong{21 Guns}{Green Day}{}{Englisch}{Pop}{

\verse{
\li{\Dm[]Do you \Bb[]know what's worth \F[]fighting \C[]for,}
\li{\Dm[]When it's \Bb[]not worth \F[]dying \C[]for?}
\li{\Dm[]Does it \Bb[]take your \F[]breath a\C[]way}
\li{And you \Bb[]feel yourself suffo\C[]cating?}
\li{\Dm[]Does the \Bb[]pain weigh \F[]out the \C[]pride?}
\li{\Dm[]And you \Bb[]look for a \F[]place to \C[]hide?}
\li{\Dm[]Did some\Bb[]one break your \F[]heart in\C[]side?}
\li{You're in \Bb[]ruins\C[5]}
}

\chorus{
\li{\F[5]One, \C[]21 \Dm[]guns}
\li{\C[5]Lay down your \Bb[5]arms}
\li{\F[5]Give up the \C[5]fight}
\li{\F[5]One, \C[]21 \Dm[]guns}
\li{\C[5]Throw up your \Bb[5]arms \F[5]into the \C[5]sky,}
\li{You and \Bb[5]I~ \F[5]* \C[5]}
}

\verse{
\li{\Dm[]When you're \Bb[]at the \F[]end of the \C[]road}
\li{\Dm[]And you \Bb[]lost all \F[]sense of con\C[]trol}
\li{\Dm[]And your \Bb[]thoughts have \F[]taken their \C[]toll}
\li{When your \Bb[]mind breaks the spirit of your \C[]soul}
\li{\Dm[]Your \Bb[]faith walks on \F[]broken \C[]glass}
\li{\Dm[]And the \Bb[]hangover \F[]doesn't \C[]pass}
\li{\Dm[]Nothing's \Bb[]ever \F[]built to \C[]last}
\li{You're in \Bb[]ruins. \C[5]}
}

\refrain

\bridge{
\li{\Dm[]Did you \Bb[5]try to \F[5]live on your \C[5]own}
\li{\Dm[]When you \Bb[5]burned down the \F[5]house and \A[5]home?}
\li{\Dm[]Did you \Bb[5]stand too \F[5]close to the \A[5]fire?}
\li{Like a \Bb[5]liar looking for}
\li{for\C[5]giveness from a \F[5]stone}
}

\verse{
\li{\Dm[]When it's \Bb[]time to \F[]live and let \C[]die}
\li{\Dm[]And you \Bb[]can't get \F[]another \C[]try}
\li{\Dm[]Something \Bb[]inside this \F[]heart has \C[]died}
\li{You're in \Bb[]ruins.\C[5]}
}

\chorus{
\li{\brep\F[5]One, \C[]21 \Dm[]guns}
\li{\C[5]Lay down your \Bb[5]arms}
\li{\F[5]Give up the \C[5]fight}
\li{\F[5]One, \C[]21 \Dm[]guns}
\li{\C[5]Throw up your \Bb[5]arms \F[5]into the \C[5]sky\erep}
\li{You and \Bb[5]I~ \F[5]* \C[5]}
}

}
\end{document}