\documentclass[../Liederbuch/LiederbuchGitarristen.tex]{subfiles}
\begin{document}
\song{4 Chords}{Axis of Awesome}{1}{Englisch}{Rock}{

\verse{
\li{\C* \G* \Am* \F* You recognize this? (Yeah, that's Don't Stop Believing from Journey)}
}

\verse{
\li{\C[]My life is brilliant, \G[]my love is pure}
\li{\Am[]I saw an angel, \F[]of that I'm sure}
}

\verse{
\li{\C[]People killing people \G[]dying, children hurtin', you hear them crying}
\li{\Am[]Can you practice what you preach, \F[]would you turn the other cheek?}
}

\verse{
\li{\C[]Forever \G[]young. I want to \Am[]be forever \F[]young}
}

\verse{
\li{\C[]I won't hesi\G[]tate no more, no \Am[]more, it cannot \F[]wait, I'm yours}
}

\verse{
\li{\C[]Your lipstick stains \G[]on the front lobe of my \Am[]left side brains}
\li{\F[]I knew I wouldn't forget you}
}

\verse{
\li{\C[]If I could, \G[]then I would, \Am[]I'll go wher\F[]ever you will go}
}

\verse{
\li{And \C[]can you \G[]feel the \Am[]love to\F[]night}
}

\verse{
\li{\C[]Nobody want's to \G[]see us together, \Am[]but it don't matter \F[]no ('cause I got you)}
}

\verse{
\li{Country \C[]roads, take me \G[]home to the \Am[]place, I be\F[]long}
}

\verse{
\li{\C[]I'm your biggest fan \G[]I'll follow you until you \Am[]love me, Papa-\F[]Paparazzi}
}

\verse{
\li{I can't \C[]live\G* with or with\Am[]out \F[]you}
}

\verse{
\li{Pictures of \C[]you, pictures of \G[]me}
\li{Hung upon your \Am[]wall for the world to \F[]see}
}

\verse{
\li{(And she \C[]will be \G[]loved. Yeah, she \Am[]will be \F[]lov-)}
}

\verse{
\li{When I \C[]find myself in \G[]times of trouble \Am[]Mother Mary \F[]comes to me}
}

\verse{
\li{\C[]No, \G[]woman, \Am[]no cry}
}

\verse{
\li{Yeah, Mama this \F[]surely is a \C[]dream}
}

\verse{
\li{I come from a \G[]land down under\Am* \F*}
}

\verse{
\li{\C[]Red, white and \G[]blue \Am[]funny things you \F[]do. Ameri\C[]ca, Ameri\G[]ca, this is \Am[]you\F*}
}

\verse{
\li{They say \C[]Taylor was a good girl, \G[]never one to be late}
\li{\Am[]complain express \F[]ideas in her \C[]brain}
}

\verse{
\li{I need some love like I \G[]never needed love be\Am[]fore}
\li{Wanna make love \F[]to ya baby}
}

\verse{
\li{\C[]Take \G[]on \Am[]me (\F[]When I come around)}
\li{\C[]Take \G[]me \Am[]on (\F[]When I come around)}
\li{\C[]I'll \G[]be \Am[]gone, \F[]when I'm \C[]on \G[]take\Am* \F* \C}
}

\verse{
\li{\G[]Save to\Am[]night (Its gonna take a lot \F[]to drag me away from you)}
\li{and \C[]fight the break of \G[]dawn come}
\li{\Am[]tomorrow (There's nothing that a \F[]hundred men or)}
\li{\C\below{(more could ever do)}Tomorrow I'll be \G[]gone (If I were a boy)}
}

\verse{
\li{Here I \Am[]am, once \F[]again I'm \C[]torn (I think I could understand) into \G[]pieces}
\li{Can't \Am[]deny it, can't pre\F[]tend, just \C[]thought you were the \G[]one}
}

\verse{
\li{In my \Am[]head, I \F[]see \C[]you all over \G[]me.}
\li{In my \Am[]head, \F[]you ful\C[]fill my fantasy.\G* }
\li{In my head (\Am[]Despite all my \F[]rage I am \C[]still just a \G[]rat in a cage)}
}

\verse{
\li{What if \Am[]God was \F[]one of us\C* \G*}
}

\verse{
\li{(Tell me: \Am[]Why'd you have to go and make \F[]things so compli\C[]cated?}
\li{I \G[]see the way you're \Am[]acting like you're somebody)}
}

\verse{
\li{I \F[]know she's \C[]playin' with \G[]me, \Am[]but that's \F[]ok 'cause I got \C[]no self \G[]esteem}
}

\verse{
\li{With a \Am[]1,000 eyes and a \F[]good disguise}
\li{Hit 'em \C[]right between the eyes, hit them \G[]right between the eyes}
}

\verse{
\li{'cause you're so \Am[]beauti\F[]ful something \C[]beauti\G[]ful}
}

\verse{
\li{\Am[]Too late to apolog\F[]ize, \C[]too late\G*}
}

\verse{
\li{Just gonna \Am[]stand there and watch me \F[]burn,}
\li{but that's al\C[]right, because I like the way it \G[]hurts}
}

\verse{
\li{It's my \Am[]life, it's \F[]now or never\C[], I ain't gonna \G[]live forever}
}

\verse{
\li{\Am[]Can't read my, can't read my, \F[]no he can't read my \C[]poker face}
}

\verse{
\li{(\G[]Come on Barbie, let's go party!)}
}

\verse{
\li{\Am[]How long how \F[]long will I \C[]slide \G[]separate my}
}

\verse{
\li{\Am[]Double rainbow all the way \F[]'cross the sky, \C[]yeah, yeah, \G[]so intense}
}

\verse{
\li{\Am[]Enjoy yourself \F[]take only what you \C[]need from it\G*}
\li{\Am[]A family of \F[]trees wanting}
}

\verse{
\li{\C[]Time to \G[]say good\Am[]bye veduto \F[]e vissuto con te}
}

\verse{
\li{Should \C[]auld acquaintance \G[]be forgot and \Am[]never brought to \F[]mind?}
}

\verse{
\li{I'm more than a \C[]bird, I'm more than a \G[]plane,}
\li{I'm a \Am[]birdplane\F[], I'm a \C[]birdplane\G[], a mother fuckin' \Am[]birdplane\F[]}
}

\verse{
\li{And doesn't that sound fami\C[]liar? Doesn't that hit too \G[]close to home?}
\li{Doesn't that make you \Am[]shiver? The way things could have \F[]gone.}
\li{And doesn't it feel \C[]peculiar, when everyone wants a \G[]little more?}
\li{So that I do \Am[]remember to never go this \F[]far}
\li{That's all it takes to be a \C[]star!}
}

\footer{Journey - Don't stop believing; James Blunt - You're beautiful; The Black Eyed Peas - Where is the love; Alphaville - Forever young; Jason Mraz - I'm yours; Train - Hey, Soul Sister; The Calling - Wherever you will go; Elton John - Can you feel the love tonight; Akon - Don't matter; John Denver - Country Roads; Lady Gaga - Paparazzi; U2 - With or without you; The Last Goodnight - Pictures of you; Maroon 5 - She will be loved; The Beatles - Let it be; Bob Marley - No woman, no cry; Marcy Playground - Sex and candy; Men at Work - Down Under; Jill Colucci - The funny things you do; Jack Johnson - Taylor; Spice Girls - 2 become 1;a-ha - Take on me; Green Day - When I come around; Eagle Eye Cherry - Save tonight; Toto - Africa; Beyoncé - If I were a boy; Kelly Clarkson - Behind these hazel eyes; Jason Derulo - In my head; The Smashing Pumpkins - Bullet with buttefly wings; Joan Osborne - One of us; Avril Lavigne - Complicated; The Offspring - Self Esteem; The Offspring - You're gonna go far, kid; Akon - Beautiful; OneRepublic - Apologize; Eminem ft. Rihanna - Love the way you lie; Bon Jovi - It's my life; Lady Gaga - Poker Face; Aqua - Barbie girl; Red Hot Chili Peppers - Otherside; The Gregory Brothers - Double Rainbow Song; MGMT - Kids; Andrea Bocelli - Time to say goodbye; Robert Burns - Auld lang syne; Five for Fighting - Superman / The Axis of Awesome - Birdplane; Missy Higgins - Scar / The Axis of Awesome - Star}
}
\end{document}