\documentclass[../Liederbuch/LiederbuchGitarristen.tex]{subfiles}
\begin{document}
\song{50 ways to leave your lover}{Paul Simon}{}{Englisch}{Folk}{

\intro{
\chli{\Em \D \C[maj7] \B[7] | \Em[7] \D \C[maj7] \Ds[dim7] | \Em[7] \D \C[maj7] \B[7] | \Em[] \Am[7] \Em[]}
}

\verse{
\li{\Em[]\dq{}The problem is \D[]all inside your \C[maj7]head\dq{}, she said to \B[7]me,}
\li{\Em[7]The answer is \D[]easy if you \C[maj7]take it logical\Ds[dim7]ly.}
\li{\Em[7]I'd like to \D[]help you in your \C[maj7]struggle to be \B[7]free.}
\li{There must be \Em[]- fifty \Am[7]ways to leave your \Em[]lover.\dq}
}

\verse{
\li{\Em[]She said: \dq{}It's \D[]really not my \C[maj7]habit to intru\B[7]de,}
\li{Further\Em[]more I hope my \D[]meaning won't be \C[maj7]lost or miss-constru\Ds[dim7]ed,}
\li{But I'll \Em[]repeat my\D[]self, at the \C[maj7]risk of being \B[7]crude.}
\li{There must be \Em[]- fifty \Am[7]ways to leave your \Em[]lover. \Em[]Fifty \Am[7]ways to leave your \Em[]lover.\dq}
}

\chorus{
\li{Just slip out the \G[]back Jack, make a new \Bb[]plan Stan,}
\li{You don't need to be \C[7]coy Roy, just get yourself \G[]free}
\li{Hop on the \G[]bus Gus, you don't need to dis\Bb[]cuss much,}
\li{Just drop off the \C[7]key Lee, and get yourself \G[]free.}
\li{Slip out the \G[]back Jack, make a new \Bb[]plan Stan,}
\li{You don't need to be \C[7]coy Roy, you just listen to \G[]me.}
\li{Hop on the \G[]bus Gus, you don't need to dis\Bb[]cuss much,}
\li{Just drop off the \C[7]key Lee, and get your-self \G[]free.}
}

\verse{
\li{\Em[]She said: \dq{}It \D[]grieves me so to \C[maj7]see you in such \B[7]pain.}
\li{I wish there \Em[]was something I could \D[]do to make \C[maj7]you smile \Ds[dim7]again.\dq}
\li{I said: \dq{}I ap\Em[]preciate that \D[]and would you \C[maj7]please ex\B[7]plain}
\li{About the \Em[]- fifty \Am[7]ways.\dq\Em[]}
}

\verse{
\li{\Em[]She said: \dq{}Why \D[]don't we both just \C[maj7]sleep on it to\B[7]night,}
\li{And I be\Em[]lieve that in the \D[]morning you'll \C[maj7]begin to see the \Ds[dim7]light.\dq}
\li{Then she \Em[]kissed me and I \D[]realised, she \C[maj7]probably was \B[7]right,}
\li{There must be \Em[]fifty \Am[7]ways to leave your \Em[]lover, \Em[]fifty \Am[7]ways to leave your \Em[]lover.}
}

\refrain

\footer{
\ifguitarversion{
D\#dim7 = xx1212 \\
}
Paul Simon hat diesen Song 1975 nach der Scheidung von seiner Frau Peggy Harper geschrieben. \\ Es wurde der Größe und einziger Nummer 1 Hit seiner Solo-Karriere.

}

}
\end{document}