\documentclass[../Liederbuch/LiederbuchGitarristen.tex]{subfiles} 
\begin{document}
\song{Architects}{Rise Against}{1}{Englisch}{Punk}{
\verse{
\li{\Am Are there no fighters left here any \C more?}
\li{\Am Are we the generation we've been waiting \C for?}
\li{Or are we \F patiently burning, \C waiting \G to be \Am saved\G[]?}
\li{\Am Our heroes, our icons have mellowed with \C age,}
\li{\Am following rules that they once diso\C[]beyed.}
\li{They're \F now being led when they \C used to \G lead the \Am way\G[].}
}

\chorus{
\li{Do you \F still believe in \C all the things that \G you stood by be\Am[]fore?}
\li{Are you \F out on the \C front lines, or \G at home keeping \Am score?}
\li{Do you \F care to be the \C layer of the \G bricks that seal your \Am fate}
\li{or would you \F rather be the architect of \G what we might create?}
}

\verse{
\li{They \Am laid out the blueprints, they poured down a \C base.}
\li{\Am Concrete solutions to slow our de\C[]cay.}
\li{But \F when they are gone who the \C fuck's gonna \G take their \Am place\G[]?}
\li{Yeah, will \Am it be the cynic, the critics ga\C[]lore?}
\li{The cli\Am[]ché apathetic, passed out on the \C floor.}
\li{The \F trusting complicit who col\C[]lective\G[]ly ig\Am[]nore\G[].}
}

\refrain

\bridge{
\li{\Am Don't you remember when you were young - and you wanted to set the world on \F fire?}
\li{Somewhere deep \G down, I know you \Am do.}
\li{\Am And don't you remember when we were young - and we wanted to set the world on \F fire?}
\li{'Cause I still \G am and I still \Am do.}
\li{Make no mis\F[]take, we are \C not a\G[]fraid to \Am bear the \F burden of re\C[]peating}
\li{what they're \G thinking any\Am[]way.}
\li{Let's raise the \F stakes - \C on the bet we \G made. \Am Let's de\F[]cide to be \C architects,}
\li{the \G master of our \Am fate.}
}

\outro{
\li{Yeah, we \F still believe in \C all the things that \G we stood by be\Am[]fore.}
\li{And \F after every\C[]thing we've seen, there \G may be even \Am more.}
\li{And I \F know we're not the \C only ones and \G we were not the \Am first.}
\li{and \F unapologetically we stand behind each \G word\Am.}
}
}
\end{document}