\documentclass[../Liederbuch/LiederbuchGitarristen.tex]{subfiles} 
\begin{document}
\song{Back home in Derry}{Bobby Sands}{}{Englisch}{Irisch/Schottisch}{
\verse{
\li{In \Am[]1803 we \C[]sailed out to sea, \G[]out from the \D[]sweet town of \Am[]Derry}
\li{For \Am[]Australia bound if we \Em[]didn't all drown}
\li{and the \G[]marks of our \D[]fetters we \Am[]carried.}
\li{In the \Am[]rusty iron chains we \C[]sighed for our wains}
\li{As our \Am[]good wives we left in \C[]sorrow.}
\li{As the \Am[]mainsails unfurled our \C[]curses we hurled}
\li{On the \G[]English and \D[]thoughts of to\Am[]morrow.}
}

\chorus{
\li{\brep\C[]Oh Oh \G[]Oh Oh I \Am[]wish I was \G[]back home in \Am[]Derry.\erep}
}

\verse{
\li{By the \Am[]mouth of the Foyle, bid fare\C[]well to the soil}
\li{As \G[]down below \D[]decks we were \Am[]lying}
\li{O'\Am[]Doherty screamed, woken \Em[]up from a dream}
\li{by a \G[]vision of \D[]bold Robert \Am[]dying}
\li{The \Am[]sun burned cruel as we \C[]dished out the gruel}
\li{Dan O'\Am[]Connor was down with a \C[]fever.}
\li{Sixty \Am[]rebels today bound \C[]for Botany Bay,}
\li{how \G[]many will \D[]meet their de\Am[]ceiver?}
}

\refrain

\verse{
\li{I \Am[]cursed them to hell as our \C[]bow fought the swell.}
\li{Our \G[]ship danced like a \D[]moth in the \Am[]firelight.}
\li{White \Am[]horses rode high as the \Em[]devil passed by}
\li{Taking \G[]souls to \D[]Hades by \Am[]twilight.}
\li{Five \Am[]weeks out to sea we were \C[]now forty-three}
\li{Our \Am[]comrades we buried each \C[]morning.}
\li{In \Am[]our own slime we were \C[]lost in a time.}
\li{\G[]Endless \D[]night without \Am[]dawning.}
}

\refrain

\verse{
\li{Van \Am[]Diemen's land is a \C[]hell for a man}
\li{To \G[]end out his \D[]whole life in \Am[]slavery.}
\li{When the \Am[]climate is raw and the \Em[]gun makes the law.}
\li{Neither \G[]wind nor \D[]rain cares for \Am[]bravery.}
\li{Twenty \Am[]years have gone by and I've \C[]ended me bond}
\li{And \Am[]comrades' ghosts are be\C[]hind me.}
\li{A \Am[]rebel I came and \C[]I'll die the same.}
\li{On the \G[]cold winds of \D[]night you will \Am[]find me.}
}

\refrain
\footer{Van Diemen's Land war ein Name für die Insel Tasmanien, einem Teil von Australien.}
}
\end{document}