\documentclass[../Liederbuch/LiederbuchGitarristen.tex]{subfiles} 
\begin{document}
\song{Cat's in the cradle}{Harry Chapin}{}{Englisch}{Folk}{
\verse{
\li{My \E[]child arrived just the \G[]other day, he \A[]came to the world in the \E[]usual way.}
\li{But there were \E[]planes to catch, and \G[]bills to pay, \A[]he learned to walk while \E[]I was away.}
\li{And he was \D[]talking 'fore I knew it and as he grew, he'd say:}
\li{\dq\G[]I'm gonna be like \E[]you, dad, you \G[]know I'm gonna be like \E[]you.\dq}
}

\chorus{
\li{\E[]And the cat's in the cradle and \D[]the silver spoon,}
\li{\G[]little boy blue and the \A[]man on the moon.}
\li{\E[]When you comin' home dad? I \G[]don't know when.}
\li{\D[]We'll get together \E[]then, son, \G[]you know we'll have a good time \E[]then.}
}

\verse{
\li{My \E[]son turned ten just the \G[]other day he said \dq\A[]Thanks for the ball dad come \E[]on let's play}
\li{Can you \E[]teach me to throw?\dq{} I said \dq\G[]Not today, I got a \A[]lot to do\dq{} He said \dq\E[]That's ok\dq}
\li{\D[]And he walked away but his smile never dimmed, and said:}
\li{\dq\G[]I'm gonna be like \E[]him, yeah, you \G[]know I'm gonna be like \E[]him.\dq}
}

\refrain

\verse{
\li{Well he \E[]came from college just the \G[]other day, so \A[]much like a man I just \E[]had to say:}
\li{\dq I'm \E[]proud of you, can you \G[]sit for a while?\dq{} He \A[]shook his head and he \E[]said with a smile:}
\li{\dq\D[]What I'd really like, dad, is to borrow the car keys.}
\li{\G[]See you later, can I \E[]have them please?\dq}
}

\chorus{
\li{\E[]And the cat's in the cradle and \D[]the silver spoon,}
\li{\G[]little boy blue and the \A[]man on the moon.}
\li{\E[]When you comin' home son? I \G[]don't know when.}
\li{\D[]We'll get together \E[]then, dad, \G[]you know we'll have a good time \E[]then.}
}

\verse{
\li{I've \E[]long since retired, my \G[]son's moved away. \A[]I called him up just the \E[]other day, said:}
\li{\dq I'd \E[]like to see you if \G[]you don't mind\dq{} He said \dq I'd \A[]love to dad if I \E[]can find the time}
\li{\D[]You see, my new job's a hassle and the kids have the flu,}
\li{\G[]but it's sure nice talking to \E[]you dad, it's been \G[]sure nice talking to \E[]you.\dq}
}

\bridge{
\li{And as he \D[]hung up the phone it occurred to me.}
\li{\G[]He'd grown up just like \E[]me, my \G[]boy was just like \E[]me!}
}

\refrain

}
\end{document}