\documentclass[../Liederbuch/LiederbuchGitarristen.tex]{subfiles}
\begin{document}
\song{Community Property}{Steel Panther}{-1}{Englisch}{Rock}{

\verse{
\li{I would \E[5/A] give you the stars in the \E[5/C\#] sky}
\li{But they're too far a\B[5]way.}
\li{If \E[5/A] you were a hooker, you'd \E[5/C\#] know}
\li{I'd be happy to \B[5] pay.}
\li{If \E[5/A] suddenly you were a \E[5/C\#] guy}
\li{I'd be suddenly \B[5] gay.}
}

\chorus{
\li{'Cause my \E[5] heart be\A[5]longs to \B[5] you,}
\li{my \E[5] love is \A[5] pure and \B[5] true,}
\li{my \E[5] heart be\A[5]longs to \B[5] you,}
\li{but my \A[5] cock is community property.}
}

\verse{
\li{You're the \E[5/A] only girl that I like to \E[5/C\#] screw}
\li{When I'm not on the \B[5] road.}
\li{When I come \E[5/A] home, my dinner's \E[5/C\#] made}
\li{And the front lawn is \B[5] mowed.}
\li{I'll kiss your \E[5/A] mouth even \E[5/C\#] after you }
\li{swallow my \B[5] load.}
}

\chorus{
\li{'Cause my \E[5] heart be\A[5]longs to \B[5] you,}
\li{There ain't \E[5] nothing that \A[5] I wouldn't \B[5] do (for you)}
\li{my \E[5] heart be\A[5]longs to \B[5] you,}
\li{but my \A[5] cock is community property.}
}

\bridge{
\li{\B[5] I wanna \C[\#5] make it \A[5] clear so you retain it}
\li{\B[5] my dick's a \C[\#5] free spi\A[5]rit and you can't restrain it,}
\li{no, you just can't chain it down!}
\li{\E[sus4] I love you so much it \E[]hurts from my head to my \B[sus4] feet.}
\li{\E[sus4]I think of you and I \E[]can't help but fondle my \B[sus4] meat.}
\li{\E[sus4] I see your face every \E[]time that I go out and \B[sus4] cheat.}
}

\chorus{
\li{'Cause my \E[5] heart be\A[5]longs to \B[5] you,}
\li{There ain't \E[5] nothing that \A[5] I wouldn't \B[5] do}
\li{my \E[5] heart be\A[5]longs to \B[5] you,}
\li{but my \A[5] dong is community property.}
\li{Yeah, yeah, yeah.}
}

}
\end{document}