\documentclass[../Liederbuch/LiederbuchGitarristen.tex]{subfiles}
\begin{document}
\song{Cousin Jack}{Port Issac's Fisherman's Friends}{}{Englisch}{Irisch/Schottisch}{

\verse{
\li{\Em This land is barren and \C  broken,}
\li{\D scarred like the face of the \G moon.}
\li{\Em Our tongue is no longer \Bm spoken,}
\li{\C towns all around face \D ruin.}
\li{\Em Will there be work in New \C Brunswick?}
\li{\D Will I find gold in the \G Cape?}
\li{If I \Em  tunnel way down to \Bm Australia,}
\li{\C oh will I ever es\D[]cape?}
}

\chorus{
\li{\G Where there's a mine or a \D hole in the ground,}
\li{\Em that's where I'm heading for, \C that's where I'm bound,}
\li{\D look for me under the \G lode and inside the \C vain. \D}
\li{Where the \G copper the clay, where the \D arsenic and tin}
\li{\Em run in your blood, then get \C under your skin,}
\li{I'm \D leaving the county be\G[]hind, and I'm not coming \C back,}
\li{so \D follow me \C down cousin \Em Jack.}
}

\verse{
\li{The \Em soil was to poor to make \C Eden,}
\li{\D granite and sea left no \G choice.}
\li{Though \Em visions of heaven sus\Bm[]tained us,}
\li{when \C John Wesley gave us a \D voice.}
\li{Did \Em Joseph once come to St. \C Michaels Mount?}
\li{Two \D thousand years pass in a \G dream.}
\li{When you're \Em working your way in the \Bm darkness,}
\li{\C deep in the heart of the \D seam.}
}

\refrain

\verse{
\li{I \Em dream of a bridge on the \C Tamar,}
\li{it \D opens us up to the \G east.}
\li{And the \Em English they live in our \Bm houses}
\li{and the \C Spanish they fish in our \D seas.}
}

\refrain

}
\end{document}