\documentclass[../Liederbuch/LiederbuchGitarristen.tex]{subfiles} 
\begin{document}
\song{Finnegan's Wake}{trad. irisch}{}{Englisch}{Irisch/Schottisch}{
\verse{
\li{Tim \C[]Finnegan lived in \Am[]Walker Street a \F[]gentle Irish man \G[]mighty odd.}
\li{He'd a \C[]beautiful brogue so \Am[]rich and sweet and to \F[]rise in the world he \G[]carried a \C[]hod.}
\li{Now you \C[]see he'd a sort of a \Am[]tipplin' way with a \F[]love of liquor \G[]Tim was born}
\li{And to \C[]help him on with his \Am[]way each day he'd a \dq\F[]drop of the creature\dq {} \G[]every \C[]morn.}
}

\chorus{
\li{\C[]Whack for the hurrah, \Am[]take your partner \F[]round the floor ye \G[]trotters shake;}
\li{\C[]Wasn't it the \Am[]truth I told you \F[]lots of fun at \G[]Finnegan's \C[]wake!}
}

\verse{
\li{One \C[]morning Tim was \Am[]rather full, his \F[]head felt heavy which \G[]made him shake}
\li{He \C[]fell off the ladder and \Am[]broke his skull, so they \F[]carried him home his \G[]corpse to \C[]wake.}
\li{They \C[]rolled him up in a \Am[]nice clean sheet and \F[]laid him out u\G[]pon the bed,}
\li{With \C[]plenty of candles a\Am[]round his feet, and a \F[]couple of dozen a\G[]round his \C[]head.}
}

\refrain

\verse{
\li{His \C[]friends assembled \Am[]at the wake, and \F[]Mrs. Finnegan \G[]called for lunch,}
\li{\C[]First they laid out \Am[]tea and cakes, then \F[]pipes, tobacco and \G[]whiskey \C[]punch.}
\li{Then \C[]Biddy O'Brien be\Am[]gan to cry; Such a \F[]lovely corpse, did you \G[]ever see}
\li{O \C[]Tim, avourneen, \Am[]why did you die? Ah! \F[]None of your gab said \G[]Biddy Ma\C[]gee.}
}

\refrain

\verse{
\li{Then \C[]Peggy O'Connor took \Am[]up the job; Ah! \F[]Biddy says she, \dq You're \G[]wrong, I'm sure\dq}
\li{But \C[]Biddy gave her a \Am[]belt on the gob and \F[]left her sprawling \G[]on the \C[]floor.}
\li{Each \C[]side in war did \Am[]soon engage, 'twas \F[]woman to woman and \G[]man to man,}
\li{\C[]Shillelagh-law was \Am[]all the rage and a \F[]row and a ruction \G[]soon be\C[]gan.}
}

\refrain

\verse{
\li{Then \C[]Mickey Maloney \Am[]raised his head when a \F[]gallon of whiskey \G[]flew at him,}
\li{It \C[]missed, and landed \Am[]on the bed, the \F[]whiskey scattered \G[]over \C[]Tim!}
\li{Be\C[]dad he revives! \Am[]See how he rises! Tim \F[]Finnegan jumping \G[]from the bed,}
\li{\C[]Crying while he ran a\Am[]round like blazes: \F[]Thundering blazes ye \G[]think I'm \C[]dead.}
}

\refrain
}
\end{document}