\documentclass[../Liederbuch/LiederbuchGitarristen.tex]{subfiles} 
\begin{document}
\song{Ghost Riders in the Sky}{Stan Jones}{1}{Englisch}{Country}{
\verse{
\li{An \Am[]old cowboy went ridin' out one \C[]dark and windy day,}
\li{u\Am[]pon a ridge he rested as he \C[]went along his way}
\li{when \Am[]all at once a mighty herd of red eyed cows he saw}
\li{\F[]driving through the ragged sk-ies  and \Am[]up a cloudy draw.}
}

\verse{
\li{Their \Am[]brands were still on fire and their \C[]hooves were made of steel}
\li{their \Am[]horns were black and shiny and their \C[]hot breath he could feel}
\li{a \Am[]bolt of fear cut through him as they thundered through the sky}
\li{For he \F[]saw the riders coming hard- and he \Am[]heard their mournful cry}
}

\chorus{
\li{\Am[]Yipie i \C[]ay - Yipie i \Am[]oh - \F[]Ghost riders in the \Am[]sky.}
}

\verse{
\li{Their \Am[]face was drawn there eyes were blurred their \C[]shirts all soaked with sweat}
\li{He's \Am[]ridin' hard to catch that herd but \C[]he 'aint caught 'em yet}
\li{'cause \Am[]they've all to ride forever on that range up in the sky}
\li{oh the \F[]horses start to shi-re as they \Am[]ride on through they cry.}
}

\verse{
\li{As the \Am[]riders loped on by him he \C[]heard one call his name}
\li{\Am[]if you want to save your soul from hell a \C[]riding on our range}
\li{\Am[]cow-boy change your ways today or with us you will ride.}
\li{\F[]Driving with the devils herd-  a\Am[]cross this moonlit sky. - \refrain*}
}
\footer{Stan Jones arbeitete 1948 als Park Ranger im Death Valley National Park in Kalifornien. Abgestellt als Kontaktperson für Filmteams, die vor Ort Außenaufnahmen durchführten, fand er für seine Geschichten und Lieder bald ein breiteres Publikum. Bereits 1949 wurde es als \dq Geisterreiter\dq gecovert.}
}
\end{document}