\documentclass[../Liederbuch/LiederbuchGitarristen.tex]{subfiles} 
\begin{document}
\song{Hallelujah}{Jeff Buckley}{}{Englisch}{Folk}{
\verse{
\li{\G[]I've heard there was a \Em[]secret chord \G[]that David played and it \Em[]pleased the Lord,}
\li{But \C[]you don't really \D[]care for music \G[]do you\D[]. \G[]It goes like this: The \C[]fourth the \D[]fifth,}
\li{the \Em[]minor fall, the \C[]major lift, the \D[]baffled king com\Bm[]posing halle\Em[]lujah.}
\li{Halle\C[]lujah, Halle\Em[]lujah, Halle\C[]lujah, Halle\G[]lu-\D[]u-\G[]jah}
}

\verse{
\li{Your \G[]faith was strong but you \Em[]needed proof.}
\li{You \G[]saw her bathing \Em[]on the roof.}
\li{Her \C[]beauty and the \D[]moonlight over\G[]threw you.\D}
\li{She \G[]tied you to a \C[]kitchen \D[]chair,}
\li{she \Em[]broke your throne, and she \C[]cut your hair}
\li{and \D[]from your lips she \Bm[]drew the Halle\Em[]lujah.}
\li{Halle\C[]lujah, Halle\Em[]lujah, Halle\C[]lujah, Halle\G[]lu-\D[]u-\G[]jah}
}

\verse{
\li{You \G[]say I took the \Em[]name in vain,}
\li{I \G[]don't even \Em[]know the name.}
\li{But \C[]if I did, well \D[]really, what's it \G[]to you?\D}
\li{There's a \G[]blaze of light in \C[]every \D[]word,}
\li{it \Em[]doesn't matter \C[]which you heard:}
\li{The \D[]holy or the \Bm[]broken Halle\Em[]lujah.}
\li{Halle\C[]lujah, Halle\Em[]lujah, Halle\C[]lujah, Halle\G[]lu-\D[]u-\G[]jah}
}

\verse{
\li{\G[]Baby I've been \Em[]here before.}
\li{I \G[]know this room I've \Em[]walked this floor.}
\li{I \C[]used to live a\D[]lone before I \G[]knew you.\D}
\li{I've \G[]seen your flag on the \C[]marble \D[]arch,}
\li{but \Em[]love is not a \C[]victory march}
\li{It's a \D[]cold and it's a \Bm[]broken Halle\Em[]lujah.}
\li{Halle\C[]lujah, Halle\Em[]lujah, Halle\C[]lujah, Halle\G[]lu-\D[]u-\G[]jah}
}

\verse{
\li{There \G[]was a time you \Em[]let me know,}
\li{what's \G[]really going \Em[]on below.}
\li{But \C[]now you never \D[]show it to me \G[]do you?\D}
\li{I re\G[]member when I \C[]moved in \D[]you}
\li{and the \Em[]holy dove was \C[]moving, too,}
\li{and \D[]every breath we \Bm[]drew was Halle\Em[]lujah.}
\li{Halle\C[]lujah, Halle\Em[]lujah, Halle\C[]lujah, Halle\G[]lu-\D[]u-\G[]jah}
}

\verse{
\li{Now \G[]maybe there's a \Em[]god above,}
\li{but \G[]all I ever \Em[]learned from love}
\li{is \C[]how to shoot at \D[]someone who out\G[]drew you.\D}
\li{And it's \G[]not a cry you can \C[]hear at \D[]night,}
\li{and it's \Em[]not somebody who's \C[]seen the light,}
\li{it's a \D[]cold and it's a \Bm[]broken Halle\Em[]lujah.}
\li{Halle\C[]lujah, Halle\Em[]lujah, Halle\C[]lujah, Halle\Em[]lujah}
}

\outro{
\li{Halle\C[]lujah, Halle\Em[]lujah, Halle\C[]lujah, Halle\G[]lu-\D[]u-\G[]jah}
}

\footer{Original von Leonard Cohen. Von Buckley bezeichnet als \dq a hallelujah to the orgasm\dq.}
}
\end{document}
