\documentclass[../Liederbuch/LiederbuchGitarristen.tex]{subfiles} 
\begin{document}
\song{Hey Jude}{The Beatles}{}{Englisch}{Pop}{
\verse{
\li{Hey, \G[]Jude, don't make it \D[]bad,}
\li{Take a \D[7]sad song and make it \G[]better.}
\li{Re\C[]member to let her into your \G[]heart,}
\li{Then you can \D[]start to \D[7]make it \G[]better.}
}

\verse{
\li{Hey, \G[]Jude, don't be a\D[]fraid, you were \D[7]made to go out and \G[]get her.}
\li{The \C[]minute you let her under your \G[]skin, then you'll be\D[]gin to \D[7]make it \G[]better.}
}

\chorus{
\li{\G[7]And any time you feel the \C[]pain,}
\li{Hey Jude, re\Am[7]frain, don't carry the \D[7]world upon your \G[]shoulders.\G[7]}
\li{\G[7]For well you know that it's a \C[]fool,}
\li{Who plays it \Am[7]cool, by making his \D[7]world a little \G[]colder.}
\li{Na, na, \G[7]na, na - \D[]na, na, na, \D[7]na}
}

\verse{
\li{Hey, \G[]Jude, don't let me \D[]down, you have \D[7]found her now go and \G[]get her.}
\li{Re\C[]member, to let her into your \G[]heart, then you can \D[]start to \D[7]make it \G[]better.}
}

\chorus{
\li{\G[7]So let it out and let it \C[]in,}
\li{Hey, Jude, be\Am[7]gin, you're waiting for \D[7]someone to per\G[]form with.\G[7]}
\li{\G[7]And don't know that it's just \C[]you,}
\li{Hey Jude, you'll \Am[7]do, the movement you \D[7]need is on your \G[]shoulders.}
\li{Na, na, \G[7]na, na - \D[]na, na, na, \D[7]na - yeah.}
}

\verse{
\li{Hey, \G[]Jude, don't make it \D[]bad, take a \D[7]sad song and make it \G[]better.}
\li{Re\C[]member to let her under your \G[]skin, then you be\D[]gin to \D[7]make it \G[]better,}
\li{Better, better, \G[7]better, better, better, \D[7]aaaaah}
}

\outro{
\li{\G[7]Na, na, na, na - \F[]na, na, na, na - \C[]na, na, na, na - Hey, \G[]Jude. \rep{15}}
}
}
\end{document}