\documentclass[../Liederbuch/LiederbuchGitarristen.tex]{subfiles} 
\begin{document}
\song{In the summertime}{Mungo Jerry}{}{Englisch}{}{
\intro{
\chli{\E \E \A \E (\B \A[)] \E}
}

\verse{
\li{In the \E[]summertime when the weather is high,}
\li{you can \E[]stretch right up and touch the sky,}
\li{when the \A[]weather is fine, you got women, you got women on your \E[]mind.}
\li{Have a \B[]drink, have a drive,}
\li{go \A[]out and see what you can \E[]find.}
}

\verse{
\li{If her \E[]daddy's rich, take her out for a meal,}
\li{if her \E[]daddy's poor, just do as you feel.}
\li{Speed a\A[]long the lane, do a ton or a ton and twenty-\E[]five.}
\li{When the \B[]sun goes down,}
\li{you can \A[]make it, make it good in a lay-\E[]by.}
}

\verse{
\li{We're \E[]not gray people, we're not dirty, we're not mean,}
\li{we love \E[]everybody but we do as we please.}
\li{When the \A[]weather is fine, we go fishing or go swimming in the \E[]sea.}
\li{We're always \B[]happy,}
\li{life's for \A[]living, yeah, that's our philoso\E[]phy.}
}

\verse{
\li{Sing a\E[]long with us, da da di di di}
\li{Da da \E[]da da yeah we're happy}
\li{Da da \A[]da da, di di di di di da da \E[]da}
\li{Da da \B[]da da da,}
\li{da da \A[]da da da da da da da da da \E[]da}
}

\verse{
\li{When the \E[]winter's here, yeah, it's party-time,}
\li{bring a \E[]bottle, wear your bright clothes, it'll soon be summertime.}
\li{And we'll \A[]sing again, we'll go driving or maybe we'll settle \E[]down.}
\li{If she's \B[]rich if she's nice,}
\li{bring your \A[]friend and we will all go into \E[]town.}
}
}
\end{document}