\documentclass[../Liederbuch/LiederbuchGitarristen.tex]{subfiles} 
\begin{document}
\song{Johnny I hardly knew ye}{trad. irisch}{}{Englisch}{Irisch/Schottisch}{
\verse{
\li{While \Em[]on the road to sweet Athy, ha-\D[]roo, ha-roo,}
\li{while \Em[]on the road to sweet Athy, ha-\G[]roo, ha-\B[7]roo,}
\li{while \Em[]on the road to \D[]sweet Athy, a \C[]stick in the hand, a \B[7]drop in the eye,}
\li{a \Em[]doleful \D[]damsel \C[]I heard \B[7]cry. \Em[]Johnny, I \D[]hardly \Em[]knew ya.}
}

\chorus{
\li{With your \Em[]drums and guns and guns and drums, ha-\D[]roo, ha-roo}
\li{With your \Em[]drums and guns and guns and drums, ha-\G[]roo, ha-\B[7]roo}
\li{With your \Em[]drums and guns and \D[]guns and drums the \C[]enemy nearly \B[7]slew ye}
\li{Me \Em[]darling \D[]dear, you \C[]look so \B[7]queer. \Em[]Johnny, I \D[]hardly \Em[]knew ye.}
}

\verse{
\li{Where \Em[]are the eyes that looked so mild, ha-\D[]roo, ha-roo}
\li{Where \Em[]are the eyes that looked so mild, ha-\G[]roo, ha-\B[7]roo}
\li{Where \Em[]are the eyes that \D[]looked so mild when \C[]my poor heart you \B[7]first beguiled}
\li{Why \Em[]did you run \D[]from me \C[]and the \B[7]child, \Em[]Johnny I \D[]hardly \Em[]knew ye. - \refrain*}
}

\verse{
\li{Where \Em[]are the legs with which you ran, ha-\D[]roo, ha-roo,}
\li{Where \Em[]are the legs with which you ran, ha-\G[]roo, ha-\B[7]roo,}
\li{Where \Em[]are the legs with \D[]which you ran when \C[]first you went to \B[7]carry a gun?}
\li{In\Em[]deed your \D[]dancing \C[]days are \B[7]done. \Em[]Johnny, I \D[]hardly \Em[]knew ye. - \refrain*}
}

\verse{
\li{It \Em[]grieved my heart to see you sail, ha-\D[]roo, ha-roo}
\li{It \Em[]grieved my heart to see you sail, ha-\G[]roo, ha-\B[7]roo}
\li{It \Em[]grieved my heart to \D[]see you sail though \C[]from my heart you \B[7]took leg-bail}
\li{Like a \Em[]cod you're \D[]doubled up \C[]head and \B[7]tail, \Em[]Johnny I \D[]hardly \Em[]knew ye. - \refrain*}
}

\verse{
\li{Ye \Em[]haven't an arm, you haven't a leg, ha-\D[]roo, ha-roo,}
\li{Ye \Em[]haven't an arm, you haven't a leg, ha-\G[]roo, ha-\B[7]roo,}
\li{Ye \Em[]haven't an arm, you \D[]haven't a leg, you're an \C[]eyeless, noseless, \B[7]chickenless egg,}
\li{You'll \Em[]have to be \D[]put with a \C[]bowl to \B[7]beg. \Em[]Johnny, I \D[]hardly \Em[]knew ye. - \refrain*}
}

\verse{
\li{I'm \Em[]happy for to see you home, ha-\D[]roo, ha-roo}
\li{I'm \Em[]happy for to see you home, ha-\G[]roo, ha-\B[7]roo}
\li{I'm \Em[]happy for to \D[]see you home \C[]from the island \B[7]of Ceylon}
\li{So \Em[]low in the \D[]flesh so \C[]high in the \B[7]bone, \Em[]Johnny I \D[]hardly \Em[]knew ye. - \refrain*}
}

\verse{
\li{How \Em[]sad it is to see you so, ha-\D[]roo, ha-roo,}
\li{How \Em[]sad it is to see you so, ha-\G[]roo, ha-\B[7]roo,}
\li{How \Em[]sad it is to \D[]see you so, and I \C[]think of you now as an \B[7]object of woe,}
\li{But your \Em[]Peggy'll still \D[]keep you on \C[]as her \B[7]beau. \Em[]Johnny, I \D[]hardly \Em[]knew ye. - \refrain*}
}

\verse{
\li{They're \Em[]rolling out the guns again, ha-\D[]roo, ha-roo,}
\li{They're \Em[]rolling out the guns again, ha-\G[]roo, ha-\B[7]roo,}
\li{They're \Em[]rolling out the \D[]guns again but they \C[]never will take our \B[7]sons again}
\li{No they \Em[]never will \D[]take our \C[]sons a\B[7]gain, \Em[]Johnny I'm \D[]swearing \Em[]to ye. - \refrain*}
}
}
\end{document}