\documentclass[../Liederbuch/LiederbuchGitarristen.tex]{subfiles}
\begin{document}
\song{Kilkelly, Ireland}{Peter Jones}{}{Englisch}{Irisch/Schottisch}{

\verse{
\li{\Am[]Kilkelly, Ireland, \F[]eighteen and sixty, my \G[]dear and loving son \Am[]John,}
\li{your good friend the schoolmaster \F[]Pat McNamara's so \G[]good as to write these words \Am[]down.}
\li{Your \C[]brothers have all gone to \G[]find work in England, the \F[]house is so empty and \Em[]sad.}
\li{The \Am[]crop of potatoes is \F[]sorely infected, a \G[]third to a half of them \Am[]bad.}
\li{And \C[]your sister Brigid and \G[]Patrick O'Donnell are \F[]going to be married in \Em[]June.}
\li{Your \Am[]mother says not to \F[]work on the railroad and be \G[]sure to come on home \Am[]soon.}
}

\verse{
\li{\Am[]Kilkelly, Ireland, \F[]eighteen and seventy, \G[]dear and loving son \Am[]John,}
\li{hello to your missus and \F[]to your four children, may \G[]they grow healthy and \Am[]strong.}
\li{\C[]Michael has got in a \G[]wee bit of trouble, I \F[]suppose he never will \Em[]learn.}
\li{Be\Am[]cause of the dampness, there's \F[]no turf to speak of, and \G[]now there's nothing to \Am[]burn.}
\li{And \C[]Brigid is happy you \G[]named a child for her, you \F[]know she has six of her \Em[]own.}
\li{You \Am[]said you found work, but you \F[]don't say what kind, or when \G[]you will be coming \Am[]home.}
}

\verse{
\li{\Am[]Kilkelly, Ireland, \F[]eighteen and eighty, dear \G[]Michael and John, my \Am[]sons,}
\li{I'm sorry to give you the \F[]very sad news your \G[]dear old mother has \Am[]gone.}
\li{We \C[]buried her down at the \G[]church in Kilkelly, your \F[]brothers and Brigid were \Em[]there.}
\li{You \Am[]don't have to worry, she \F[]died very quickly, re\G[]member her in your \Am[]prayers.}
\li{And it's \C[]so good to hear that \G[]Michael's returning, with \F[]money he's sure to buy \Em[]land.}
\li{For the \Am[]crop has been poor and the \F[]people are selling - at \G[]any price that they \Am[]can.}
}

\verse{
\li{\Am[]Kilkelly, Ireland, \F[]eighteen and ninety, my \G[]dear and loving son \Am[]John,}
\li{I guess that I must be \F[]close on to eighty, it's \G[]thirty years since you've \Am[]gone.}
\li{Be\C[]cause of all of the \G[]money you send me, I'm \F[]still living out on my \Em[]own.}
\li{\Am[]Michael has built him\F[]self a fine house, \G[]Brigid's daughters are \Am[]grown.}
\li{\C[]Thank you for sending your \G[]family picture, they're \F[]lovely young women and \Em[]men.}
\li{You \Am[]say that you might even \F[]come for a visit, what \G[]joy to see you a\Am[]gain.}
}

\verse{
\li{\Am[]Kilkelly, Ireland, \F[]eighteen and ninety\G[]two, my dear brother \Am[]John,}
\li{I'm sorry that I didn't write \F[]sooner to tell you \G[]that father passed \Am[]on.}
\li{He was \C[]living with Brigid, she \G[]says he was cheerful and \F[]healthy right down to the \Em[]end.}
\li{Oh, \Am[]you should have seen him playing \F[]with the grandchildren of \G[]Pat McNamara, your \Am[]friend.}
\li{And we \C[]buried him a\G[]longside of mother, down \F[]at the Kilkelly church\Em[]yard.}
\li{He \Am[]was a strong and a \F[]feisty old man, con\G[]sidering his life was so \Am[]hard.}
\li{It's \C[]funny the way he kept \G[]talking about you, he \F[]called for you at the \Em[]end.}
\li{Oh, \Am[]why don't you think about \F[]coming to visit, we'd \G[]all love to see you a\Am[]gain.}
}

}
\end{document}