\documentclass[../Liederbuch/LiederbuchGitarristen.tex]{subfiles} 
\begin{document}
\song{Lady In Black}{Uriah Heep}{}{Englisch}{Rock}{
\verse{
\li{She \Em[]came to me one morning, one lonely Sunday morning,}
\li{her \D[]long hair flowing in the \Em[]mid-winter wind.}
\li{I \Em[]know not how she found me, for in darkness I was walking,}
\li{and de\D[]struction lay around me from a \Em[]fight I could not win.}
}

\chorus{
\li{\Em[]Ahahaaa\D[]haa\Em[]hah, \G[]ahahaaa\D[]haha\Em[]ha.}
}

\verse{
\li{She \Em[]asked me name my foe then. I said the need within some men}
\li{to \D[]fight and kill their brothers without \Em[]thought of love or god.}
\li{And I \Em[]begged her give me horses to trample down my enemies,}
\li{so \D[]eager was my passion to de\Em[]vour this waste of life.}
}

\refrain

\verse{
\li{But she \Em[]would not think of battle that reduces men to animals,}
\li{so \D[]easy to begin and yet im\Em[]possible to end.}
\li{For \Em[]she the mother of all men had counseled me so wisely that}
\li{I \D[]feared to walk alone again and \Em[]asked if she would stay.}
}

\refrain

\verse{
\li{\dq Oh \Em[]lady lend your hand\dq, I cried, \dq Oh let me rest here at your side.\dq}
\li{\dq Have \D[]faith and trust in me\dq, she said and \Em[]filled my heart with life.}
\li{There \Em[]is no strength in numbers, have no such misconceptions.}
\li{But \D[]when you need me be assured I \Em[]won't be far away.}
}

\refrain

\verse{
\li{Thus \Em[]having spoke she turned away and though I found no words to say}
\li{I \D[]stood and watched until I saw her \Em[]black cloak disappear.}
\li{My \Em[]labor is no easier, but now I know I'm not alone.}
\li{I \D[]find new heart each time I think u\Em[]pon that windy day.}
\li{And \Em[]if one day she comes to you drink deeply from her words so wise.}
\li{Take \D[]courage from her as your prize and \Em[]say hello for me.}
}

\repref{10}
\footer{Der pazifistische Text handelt von der Begegnung eines Mannes mit einer mysteriösen 'Lady in Black'. Er bittet sie um Hilfe nach einem, nicht näher beschriebenen, schweren Kampf mit einem furchtbaren Gegner. Die Frau weigert sich ihm behilflich zu sein, macht ihm stattdessen mit Frieden und Liebe vertraut. Seine Bitte bei ihm zu bleiben lehnt sie ab und verschwindet genauso unvermutet wie sie erschienen ist.}
}
\end{document}