\documentclass[../Liederbuch/LiederbuchGitarristen.tex]{subfiles} 
\begin{document}
\song{Lanigan's ball}{James Farrell}{}{Englisch}{Irisch/Schottisch}{
\verse{
\li{In the \Am town of Athy one Jeremy Lanigan}
\li{\G battered away till he hadn't a pound.}
\li{And his \Am father he died and made him a man again,}
\li{left him a \Dm farm and ten \Am acres of ground.}
\li{He \Am gave a grand party to friends and relations}
\li{who \G did not forget him when come to the wall.}
\li{\Am If you'd only listen, I'll make your eyes glisten}
\li{at the rows and \Dm ructions of \Am Lanigan's ball.}
}

\verse{
\li{My\Am[]self to be sure got free invitations}
\li{for \G all the nice girls and boys I might ask.}
\li{In \Am less than a minute both friends and relations}
\li{were dancing as \Dm merry as \Am bees round a cask.}
\li{\Am Lashing of punch and wine for the ladies,}
\li{po\G[]tatoes and cakes, there was bacon and tea.}
\li{\Am There were the Nolans, Dolans, O'Grady's,}
\li{courting the \Dm girls and \Am dancing away.}
}

\chorus{ 
\li{Six long months I \G spent in Dublin \Am six long months doing \Em nothing at all.}
\li{\Am Six long months I \G spent in Dublin, \Am learning to \Em dance for \Am Lanigan's ball.}
}

\verse{
\li{They were \Am doing all kinds of nonsensical polkas}
\li{\G round the room in a whirlygig.}
\li{But \Am Julia and I soon banished their nonsense}
\li{and tipped them a \Dm twist of a \Am real Irish jig.}
\li{Oh, \Am how the girl she really got mad at me}
\li{\G danced till you'd think that the ceiling would fall.}
\li{For I \Am spent three weeks at Brook's Academy,}
\li{learning to \Dm dance for \Am Lanigan's ball.}
}

\refrain

\bridge{
\li{\brep And \Am I stepped out and I stepped in again, and \G I stepped out and I stepped in again,} 
\li{and \Am I stepped out and I stepped in again, learning to \Dm dance for \Am Lanigan's ball.\erep}
}

\verse{
\li{The \Am boys were as merry, the girls all hearty,}
\li{\G dancing around in couples and groups.}
\li{Till an \Am accident happened: Young Terence McCarthy,}
\li{he put his right \Dm leg through Miss \Am Finerty's hoops.}
\li{The \Am creature she fainted and cried \dq Meelia, murther\dq,}
\li{and \G called for her brothers and gathered them all.}
\li{\Am Carmody swore that he'd go no further}
\li{till he'd satis\Dm[]faction at \Am Lanigan's ball.}
}

\repref{2}

\verse{
\li{\Am Boys, oh boys, 'tis then there was ructions,}
\li{my\G[]self got a kick from big Phelim McHugh.}
\li{And \Am soon I replied to his kind introduction}
\li{and kicked up a \Dm terrible \Am hullabaloo.}
\li{Ould \Am Casey, the piper, was near being strangled,}
\li{they \G squeezed up his pipes, bellows, chanters and all.}
\li{The \Am girls in their ribbons they all got entangled}
\li{and that put an \Dm end to \Am Lanigan's ball.}
}

\repref{2}

\bridge{
\li{\brep And \Am I stepped out and I stepped in again, and \G I stepped out and I stepped in again,} 
\li{and \Am I stepped out and I stepped in again, learning to \Dm dance for \Am Lanigan's ball.\erep}
}

}
\end{document}