\documentclass[../Liederbuch/LiederbuchGitarristen.tex]{subfiles} 

\begin{document}
\song{Memories}{Maroon 5}{4}{Englisch}{Pop}{

\intro{
\chli{\G \D \Em \Bm \C \G \C \D}
}

\chorus{
\li{\G Here's to the ones that we \D got,}
\li{\Em cheers to the wish you were \Bm here but you're not.}
\li{'Cause the \C drinks bring back all the \G memories}
\li{of \C everything we've been \D through.}
\li{\G Toast to the ones here to\D[]day,}
\li{\Em toast to the ones that we \Bm lost on the way.}
\li{'Cause the \C drinks bring back all the \G memories,}
\li{and the \C memories bring back \D memories bring back \G you.}
}

\verse{
\li{There's a time that I re\D[]member, when I \Em did not know no \Bm pain.}
\li{When I \C believed in for\G[]ever, and every\C[]thing would stay the \D same.}
\li{Now my \G heart feel like De\D[]cember when some\Em[]body say your \Bm name.}
\li{'Cause I \C can't reach out to \G call you, but I \C know I will one \D day - hey.}
}

\bridge{
\li{\G Everybody \D hurts sometimes, \Em everybody hurts some\Bm[]day - eh eh.}
\li{\C Everything will \G be alright, \C go on raise a glass and \D say - eh:}
}

\refrain

\bridge{
\li{Doo-doo, \D Doo-doo-doo, \Em Doo-doo-doo-doo \Bm doo-doo-doo-doo}
\li{\C Doo-doo-doo-doo \G doo-doo-doo-doo, \C memories bring back \D memories bring back \G you.}
}

\verse{
\li{There's a time that I re\D[]member, when I \Em never felt so \Bm lost.}
\li{When I \C felt that all the \G hatred was too \C powerful to \D stop (uh-yeah).}
\li{Now my \G heart feel like an \D ember, and it's \Em ligthing up the \Bm dark.}
\li{I'll \C carry these torches \G for ya, that you \C know I'll never \D drop - yeah.}
}

\bridge{
\li{\G Everybody \D hurts sometimes, \Em everybody hurts some\Bm[]day - eh eh.}
\li{\C Everything will \G be alright, \C go on raise a glass and \D say - eh:}
}

\refrain

\bridge{
\li{\brep Doo-doo-doo-\D doo, \Em Doo-doo-doo-doo \Bm doo-doo-doo-doo}
\li{\C Doo-doo-doo-doo \G doo, \C memories bring back \D memories bring back \G you.\erep}
}

\outro{
\li{\D Yeah-yeah-\Em[]yeah, yeah-yeah-\C[]yeah-\G[]doh-doh,}
\li{\C memories bring back \D memories bring back \G you.}
}

}
\end{document}