\documentclass[../Liederbuch/LiederbuchGitarristen.tex]{subfiles} 
\begin{document}
\song{Mrs. Robinson}{Simon \& Garfunkel}{}{Englisch}{Folk}{
\intro{
\li{\E[7]De de \A[]de de \D[]de de \G[]de de \C[]de de \Am[]de de \E[7]de \D}
}

\chorus{
\li{\D[]And here's to \G[]you Mrs. \Em[]Robinson}
\li{\G[]Jesus loves you \Em[]more than you will \C[]know, wo wo \Am[]wo}
\li{\D[]God bless you \G[]please Mrs. \Em[]Robinson}
\li{\G[]Heaven holds a \Em[]place for those who \C[]pray, hey hey \Am[]hey}
}

\verse{
\li{\E[7]We'd like to know a little bit about you for our files}
\li{\A[]We'd like to help you learn to help yourself}
\li{\D[]Look around you \G[]all you see are \C[]sympathetic \Am[]eyes}
\li{\E[7]Stroll around the grounds un\D[]til you feel at home}
}

\refrain

\verse{
\li{\E[7]Hide it in a hiding place where no one ever goes,}
\li{\A[]put it in your pantry with your cupcakes}
\li{\D[]It's a little \G[]secret just the \C[]Robinsons' af\Am[]fair}
\li{\E[7]Most of all you've got to \D[]hide it from the kids}
}

\chorus{
\li{\D[]Koo koo ka \G[]choo Mrs. \Em[]Robinson}
\li{\G[]Jesus loves you \Em[]more than you will \C[]know, wo wo \Am[]wo}
\li{\D[]God bless you \G[]please Mrs. \Em[]Robinson}
\li{\G[]Heaven holds a \Em[]place for those who \C[]pray, hey hey \Am[]hey}
}

\verse{
\li{\E[7]Sitting on a sofa on a Sunday afternoon,}
\li{\A[]going to the candidates debate}
\li{\D[]Laugh about it \G[]shout about it \C[]when you've got to \Am[]choose}
\li{\E[7]Any way you look at it you \D[]lose}
}

\chorus{
\li{\D[]Where have you \G[]gone Joe Di\Em[]Maggio,}
\li{a \G[]nation turns its \Em[]lonely eyes to \C[]you, woo woo \Am[]woo}
\li{\D[]What's that you \G[]say Mrs. \Em[]Robinson,}
\li{\G[]Joltin' Joe has \Em[]left and gone a\C[]way, hey hey \Am[]hey}
}
\footer{Mrs. Robinson ist der Titelsong des Films 'The Graduate', dt. 'Die Reifeprüfung', mit Dustin Hoffman in der Hauptrolle. Er schildert die Beziehung einer verheirateten Frau zu einem jüngeren Liebhaber.}
}
\end{document}