\documentclass[../Liederbuch/LiederbuchGitarristen.tex]{subfiles}
\begin{document}
\song{Off To Sea}{The Longest Johns}{3}{englisch}{Irisch/Schottisch}{

\verse{
\li{When \Am first I landed in \G Liverpool, I \F went u\G[]pon the \Am spree,}
\li{with money at last, I \C[/G]spent it fast, I got \Am drunk as drunk could \G be,}
\li{but \C[/G] when my money \G was all gone, it was \Am then that I wanted \G more,}
\li{but a \Am man must be blind to \G make up his mind to \F go to \G sea once \Am more.}
}

\chorus{
\li{Once \C more, once \G more, \Am go to sea once \G more,}
\li{but a \Am man must be blind to \G make up his mind to \F go to \G sea once \Am more.}
}

\verse{
\li{And as I walked down \G London Road I \F met with a \G Rapper \Am Brown,}
\li{I asked him if he'd \C[/G] take me in and he \Am looked at me with a \G frown,}
\li{He \C[/G] said: Last time you \G was paid off, to \Am me you chalked no \G score,}
\li{But I'll \Am give you a chance and I'll \G take your advance, and I'll \F send you to \G sea once \Am more.}
}

\chorus{
\li{Once \C more, once \G more, \Am send you to sea once \G more,}
\li{But I'll \Am give you a chance and I'll \G take your advance, and I'll \F send you to \G sea once \Am more.}
}

\verse{
\li{I shipped on board of a \G whaling barque, we were \F bound for the \G Greenland \Am seas}
\li{where cold winds blow through \C[/G] frost and snow, why \Am Jamaica rum would \G freeze}
\li{and \C[/G] worst to bear, I'd no \G hard weather gear, as I'd \Am spent all my money a\G[]shore}
\li{it was \Am then that I wished that \G I was dead and could \F go to \G sea no \Am more.}
}

\chorus{
\li{No \C more, no \G more, \Am go to sea no \G more,}
\li{it was \Am then that I wished that \G I was dead and could \F go to \G sea no \Am more.}
}

\verse{
\li{Some times we're catching \G whales, my lads, some \F times we're \G catching \Am none}
\li{with a twenty-foot oar stuck \C[/G] in your paw, from \Am four o'clock in the \G morn}
\li{and \C[/G] as the shades of \G night roll on and you \Am rest on your weary \G oar,}
\li{it was \Am then that I wished that \G I was dead and could \F go to \G sea no \Am more.}
}

\chorus{
\li{Ref. wie nach Strophe 3}
}

\verse{
\li{So come all you hard weather \G sailing lads, who \F listen \G to my \Am song}
\li{when you get back from \C[/G] those long trips, I'd \Am have you not go \G wrong}
\li{take \C[/G] my advice, drink \G no strong drink, don't you \Am knock on that brothel \G door}
\li{but get \Am married instead and spend \G all night in bed, and \F go to \G sea no \Am more.}
}

\chorus{
\li{\brep No \C more, no \G more, \Am go to sea no \G more,}
\li{but get \Am married instead and spend \G all night in bed, and \F go to \G sea no \Am more. \erep}
}

}
\end{document}