\documentclass[../Liederbuch/LiederbuchGitarristen.tex]{subfiles} 
\begin{document}
\song{Puff, the magic dragon}{Peter, Paul and Mary}{}{Englisch}{Folk}{
\verse{
\li{\C Puff, the magic \Em dragon \F lived by the \C sea}
\li{and \F frolicked in the \C autumn \Am mist in a \D[7]land called Honah\G[7]lee.}
\li{\C Little Jackie \Em Paper \F loved that rascal \C Puff}
\li{and \F brought him strings and \C sealing \Am wax and \D[7]other \G[7]fancy \C stuff. \G[7]Oh!}
}

\chorus{
\li{\C Puff, the magic \Em dragon \F lived by the \C sea}
\li{and \F frolicked in the \C autumn \Am mist in a \D[7]land called Honah\G[7]lee.}
\li{\C Puff, the magic \Em dragon \F lived by the \C sea}
\li{and \F frolicked in the \C autumn \Am mist in a \D[7]land called \G[7]Honah\C[]lee.}
}

\verse{
\li{To\C[]gether they would \Em travel on a \F boat with billowed \C sail,}
\li{\F Jackie kept a \C lookout \Am perched on \D[7]Puff's gigantic \G[7]tail.}
\li{\C Noble kings and \Em princes would \F bow whenever they \C came,}
\li{\F pirate ships would \C lower their \Am flag when \D[7]Puff roared \G[7]out his \C name. \G[7]Oh!}
}

\refrain

\verse{
\li{A \C dragon lives for\Em[]ever, but \F not so little \C boys.}
\li{\F Painted wings and \C giant's \Am rings make \D[7]way for other \G[7]toys.}
\li{\C One grey night it \Em happened, Jackie \F Paper came no \C more.}
\li{And \F Puff that mighty \C dra\Am[]gon, he \D[7]ceased his \G[7]fearless \C roar.}
}

\verse{
\li{His \C head was bent in \Em sorrow, \F green scale fell like \C rain.}
\li{\F Puff no longer \C went to \Am play a\D[7]long the cherry \G[7]lane.}
\li{With\C[]out his life-long \Em friend, \F Puff could not be \C brave.}
\li{So \F Puff that mighty \C dragon \Am sadly \D[7]slipped in\G[7]to his \C cave. \G[7]Oh!}
}

\refrain
}
\end{document}