\documentclass[../Liederbuch/LiederbuchGitarristen.tex]{subfiles} 
\begin{document}
\song{Savior}{Rise Against}{1}{Englisch}{Punk}{
\verse{
\li{It \Em kills me not to know this, but I've \G all but just forgotten}
\li{what the \C color of her eyes were and her \G scars or how she \D got them.}
\li{As the \Em telling signs of age rain down a \G single tear is dropping}
\li{through the \C valleys of an aging face that \G this world has for\D[]gotten.}
}

\bridge{
\chli{\brep\Em \G \C \G \D\erep}
}

\verse{
\li{There is no \Em reconciliation that will \G put me in my place}
\li{and there is \C no time like the present to \G drink these draining \D seconds.}
\li{But \Em seldom do these words ring true when \G I'm constantly failing you,}
\li{like \C walls that we just can't break through un\G[]til we disap\D[]pear.}
}

\chorus{
\li{So tell me \C now: If this ain't \G love then how do \D we get \C out? 'Cause I don't \D know.}
\li{That's when she said I don't \Em hate you, boy,}
\li{I just want to \G save you while there's still something \C left to save\G.}
\li{That's when I \D told her I \Em love you, girl,}
\li{but I'm not the \G answer for the questions that \C you still have.}
}

\bridge{
\li{\G Wo-o-o-\D[]oh, wo-o-o-\Em[]oh.\G* \C* \G* \D}
}

\verse{
\li{But the \Em day pressed on like crushing weighths, for \G no man does it ever wait.}
\li{Like \C memories of dying days that \G deafen us like \D hurricanes.}
\li{\Em Bathed in flames we held the brand, un\G[]curled the fingers in your hand,}
\li{\C pressed into the flesh like sand, now \G do you under\D[]stand?}
}

\refrain

\bridge{
\li{\G Wo-o-o-\D[]oh, wo-o-o-\C[]oh.\Em* \D}
}

\verse{
\li{\Em One thousand miles a\D[]way, there's nothing left to \Am say, but so much left that \C I don't \D know.}
\li{\Em We never had a \D choice, this world has too much \Am noise.}
\li{It takes me \C under, it takes me \D under once a\Em[]gain.}
}

\bridge{
\li{\D I don't \Em hate you, I don't \G hate you \D no.}
}

\refrain

\outro{
\li{\D I don't \Em hate you. \G I don't \C hate you.}
\li{\D I don't \Em hate you. \G I don't \C hate you, \G no. Wo-o-o-\D[]oh, wo-o-o-\Em[]oh.}
}
}
\end{document}