\documentclass[../Liederbuch/LiederbuchGitarristen.tex]{subfiles}
\begin{document}
\song{Self esteem}{The Offspring}{}{Englisch}{Punk}{

\intro{
\li{\NC lala lalala lala lalala}
\chli{\brep \A \F \C \G\erep ~ \F \C \G \C \G\ \brep \A \F \C \G\erep}
}

\verse{
\li{\A[]I wrote her \F[]off for the \C[]tenth time \G[]today. \A[]And practiced all \F[]the \C[]things I would \G[]say}
\li{\A[]But she came \F[]over \C[]I lost my \G[]nerve. \A[]I took her back \F[]and \C[]made her dessert\G}
\li{\A[]Oh I \F[]know \C[]I'm being used\G[]. \A[]That's okay man  cause \F[]I \C[]like the abuse\G}
\li{\A[]Oh I know \F[]she's \C[]playing with me\G[]. \A[]That's okay \F[]cause I've got \C[]no self esteem\G}
}

\bridge{
\li{\A[]Oh wey \F[]oohh... \C[]yeah! \G[]yeah! \A[]oo\F[]hh \C[]yeah, \G[]yeah!}
\li{\A[]oo\F[]hh \C[]yeah, \G[]yeah! \A[]oo\F[]hh \C[]yeah, \G[]yeah!}
}

\verse{
\li{\A[]We make plans \F[]to \C[]go out at night\G[]. \A[]I wait till \F[]two \C[]then I turn out the ligh\G}
\li{\A[]This rejections \F[]got \C[]me so \G[]low. \A[]If she keeps it \F[]up \C[]I just might tell her so\G}
}

\chorus{
\li{\A[]Oh wey \F[]oohh... \C[]yeah! \G[]yeah! \A[]oo\F[]hh \C[]yeah, \G[]yeah!}
\li{\A[]oo\F[]hh \C[]yeah, \G[]yeah! \A[]oo\F[]hh \C[]yeah, \G[]yeah!}
\li{\D[]When she's \Bb[]saying, \F[]oh, that she w\C[]ants only \D[]me}
\li{Then I \Bb[]wonder why she \F[]sleeps with my \C[]friends}
\li{\D[]When she's \Bb[]saying, \F[]oh, that I'm \C[]like a di\D[]sease}
\li{Then I \Bb[]wonder how much \F[]more I can \C[]spend}
\li{\D[]Well I \Bb[]guess \F[]I should stick \C[]up for \D[]myself}
\li{But I \Bb[]really think it's \F[]better this \C[]way}
\li{\D[]The more you \Bb[]suffer. \C[]The more it \G[]shows you really \F[]care}
\li{Right? \G[]Yeah-eh\C[]-eh\G}
\chli{\brep \A \F \C \G\erep}
}

\verse{
\li{\A[]Now I'll re\F[]late \C[]this little \G[]bit, \A[]that happens \F[]more \C[]than I'd like to admit\G}
\li{\A[]Late at \F[]night \C[]she knocks on my \G[]door, \A[]she's drunk \F[]again \C[]and looking to score\G}
\li{\A[]Oh I \F[]know \C[]I should say no \G[]but \A[]it's kind of \F[]hard \C[]when she's ready to go\G}
\li{\A[]I may be \F[]dumb\C[], but I'm not a \G[]dweeb \A[]I'm just a su\F[]cker \C[]with no self esteem\G}
}

\refrain

}
\end{document}