\documentclass[../Liederbuch/LiederbuchGitarristen.tex]{subfiles} 
\begin{document}
\song{SHA-2 will soon retire}{T:Michael Naehrig/Christiane Peters/Peter Schwabe M:Billy Joel}{}{Englisch}{}{
\intro{
\chli{\brep\G \D \Em \C\erep}
}

\verse{
\li{\G Cheetah and Dynamic-SHA, \D CHI, Lux, Luffa, Lesamnta, \Em BLAKE, LANE, Hamsi, Skein, \C NKS2D.}
\li{\G All repeat SHAvite-3, \D Mikhail Maslennikov \Em is the man behind \C MCSSHA-3.}
}

\bridge{
\chli{\G \D \Em \C}
}

\verse{
\li{\G ECHO, ECOH, EDON-R, \D Spectral Hash and Aurora, \Em MD6 and ARIRANG \C do not rhyme with anythang.}
\li{\G SWIFFTX, VORTEX, FSB, \D Sgàil, Fugue and TIB-3.}
\li{\Em No one knows their fate, \C Shabal plays at number eight.}
}

\chorus{
\li{\G SHA-2 will soon re\D[]tire, because \Am NIST is learning and SHA-\C[]1 is burning.}
\li{\G SHA-2 will soon re\D[]tire, no we \Am didn't light it, but we \C tried to fight it.}
}

\verse{
\li{\G JH and Blue Midnight Wish, \D Grøstl is a breakfast dish.}
\li{\Em CRUNCH and SIMD, \C SANDstorm... we will see.}
\li{\G Twister, Blender and Keccak, \D Sarmal, do they rock?}
\li{\Em CubeHash really sucks, \C Dan do you agree?}
}

\verse{
\li{\G Martin, Knudsen, Misarsky, \D Indesteege, Jason Lee,}
\li{\Em Hirotaka Yoshida, \C Küçük, Lim, Vidyasagar,}
\li{\G Finiasz, Fay, the Keccak Team, \D Jutla and Jacques Patarin,}
\li{\Em Bernstein, Biham, \C trouble with the benchmarks. - \refrain*}
}

\bridge{
\li{\C Abacus, Waterfall, \Am StreamHash, Tangle, WAMM and Boole, \Em Ponic, Shamata, \D DCH and Maraca,}
\li{\C MeshHash, HASH 2X, \Am didn't really meet the specs.}
\li{\Em ZK-Crypt, Khichidi-1, \D they're all already gone.}
}

\verse{
\li{\G NaSHA, ESSENCE, Kara, \D Neil Sholer, Sean O'Neil,}
\li{\Em Gligoroski, Varici, \C Schroeppel and Watanabe,}
\li{\G Khovratovich, Hatterley, \D Leurent, Koç and Markovski.}
\li{\Em Eurocrypt, now you know, \C where the competition goes. - \refrain*}
}

\verse{
{\forceChords
\li{\G 26a 52d \D 798f1c \Em 8a 9b \C d84823 \G 84d 422d \D 6892 abc \Em 15 323 \C 9259 a6d}
}
\li{\G Who will break this hash, \D we can say it's not just trash.}
\li{\Em EnRUPT blown away, \C what else do I have to say? - \refrain*}
}

\outro{
\chli{\brep\G \D \Em \C\erep}
}
}
\end{document}