\documentclass[../Liederbuch/LiederbuchGitarristen.tex]{subfiles} 
\begin{document}
\song{Soon may the Wellerman come}{unbek./Nathan Evans}{3}{English}{Shanty}{
\verse{
\li{There \Am once was a ship that put to sea, the \Dm name of the ship was the \Am Billy of tea.}
\li{The winds blew up, her bow dipped down, o \E blow, my bully boys, \Am blow - huh.}
}

\chorus{
\li{\F Soon may the \C Wellerman come to \Dm bring us sugar and \Am tea and rum.}
\li{\F One day, when the \C tonguin' is done, we'll \E take our leave and \Am go.}
}

\verse{
\li{\Am She'd not been two weeks from shore, when \Dm down on her a \Am right whale bore.}
\li{The captain called all hands and swore he'd \E take that whale in \Am tow - huh.}
}

\refrain

\bridge{
\li{\F Da da da \C da da da, da \Dm da da da da \Am da da da.}
\li{\F Da da da \C da da da, da \E da da da da \Am da.}
}

\verse{
\li{Be\Am[]fore the boat had hit the water, the \Dm whale's tail came \Am up and caught her.}
\li{All hands to the side harpooned and fought her \E when she dived down \Am low - huh.}
}

\refrain

\verse{
\li{No \Am line was cut, no whale was freed, the \Dm captain's mind was \Am not of greed.}
\li{And he belonged to the whaleman's creed, she \E took that ship in \Am tow - huh.}
}

\refrain

\bridge{
\li{\F Da da da \C da da da, da \Dm da da da da \Am da da da.}
\li{\F Da da da \C da da da, da \E da da da da \Am da.}
}

\verse{
\li{For \Am forty days or even more, the \Dm line went slack, then \Am tight once more.}
\li{All boats were lost, there were only four, but \E still that whale did \Am go - huh.}
}

\refrain

\verse{
\li{As \Am far as I've heard, the fight's still on, the \Dm line's not cut and the \Am whale's not gone.}
\li{The Wellerman makes his regular call, to en\Dm[]courage the the captain, \Am crew and all - huh.}
}

\repref{2}

\footer{Wellermen waren Schiffe der Gebr체der Weller, die neuseel채ndische Walf채nger versorgten.\\Billy of tea - Einfacher Topf zum Teekochen auf offenem Feuer; tonguing - abflensen, d.h. das streifenweise abschneiden des Blubbers (Walspeck); right whale - S체dkaper}
}
\end{document}