\documentclass[../Liederbuch/LiederbuchGitarristen.tex]{subfiles} 
\begin{document}
\song{Sound of Silence}{Simon \& Garfunkel}{}{Englisch}{Folk}{
\verse{
\li{\Em[]Hello darkness, my old \D[]friend,}
\li{I've come to talk with you a\Em[]gain,}
\li{Because a \G[]vision soft\C[]ly creep\G[]ing,}
\li{Left its seeds while I \C[]was sleep\G[]ing,}
\li{And the \C[]vision that was \C[/\G]planted in my \G[]brain}
\li{Still re\Em[]mains \G[]within the \D[]sound of \Em[]silence.}
}

\verse{
\li{\Em[]In restless dreams I walked a\D[]lone. Narrow streets of cobble\Em[]stone,}
\li{'Neath the \G[]halo of \C[]a street \G[]lamp, I turned my collar to the \C[]cold and \G[]damp}                                                      
\li{When my \C[]eyes were stabbed by the \C[/\G]flash of a neon \G[]light}
\li{That split the \Em[]night. \G[]And touched the \D[]sound of \Em[]silence.}
}

\verse{
\li{\Em[]And in the naked light I \D[]saw ten thousand people, maybe \Em[]more.}
\li{People \G[]talking with\C[]out spea\G[]king, people hearing with\C[]out liste\G[]ning,}
\li{People writing \C[]songs that \C[/\G]voices never \G[]share}
\li{And no one \Em[]dares, \G[]disturb the \D[]sound of \Em[]silence.}
}

\verse{
\li{\Em[]Fools said I, you do not \D[]know silence like a cancer \Em[]grows.}
\li{Hear my \G[]words that I \C[]might teach \G[]you, take my arms that I \C[]might reach \G[]you.}
\li{But my \C[]words like \C[/\G]silent raindrops \G[]fell,\Em}
\li{And \G[]echoed in the \D[]wells of \Em[]silence}
}

\verse{
\li{\Em[]And the people bowed and \D[]prayed to the neon god they \Em[]made.}
\li{And the \G[]sign flashed out \C[]its warn\G[]ing, in the words that it \C[]was form\G[]ing.}
\li{And the sign said, the \C[]words of the prophets are \C[/\G]written on the subway \G[]walls}
\li{and tenement \Em[]halls \G[]and whispered in the \D[]sounds of \Em[]silence.}
}
}
\end{document}