\documentclass[../Liederbuch/LiederbuchGitarristen.tex]{subfiles} 
\begin{document}
\song{Star of the County Down}{T:Cathal Mac Garvey M:trad. irisch}{}{Englisch}{Irisch/Schottisch}{
\verse{
\li{Near\ch{(} \Em[]Banbridge \C[)]town in the\ch{(} \G[]County \D[)]Down one \Em[]mornin' last Ju\D[]ly,}
\li{Down a\ch{(} \Em[]boring \C[)]green came a\ch{(} \G[]sweet col\D[)]leen and she\ch{(} \Em[]smiled as she \C[)]passed\ch{(} \D[]me \Em[)]by.}
\li{She \G[]looked so sweet from her \D[]two bare feet to the\ch{(} \Em[]sheen of her \C[)]nut-brown \D[]hair.}
\li{Such a\ch{(} \Em[]coaxin' \C[)]elf, sure I\ch{(} \G[]shook my\D[)]self for to\ch{(} \Em[]see if I was \C[)]rea\ch{(}l\D[]ly \Em[)]there.}
}

\chorus{
\li{From \G[]Bantry Bay up to \D[]Derry Quay and from\ch{(} \Em[]Galway to \C[)]Dublin \D[]town,}
\li{no\ch{(} \Em[]maid I've \C[)]seen like the\ch{(} \G[]sweet col\D[)]leen, that I\ch{(} \Em[]met in the \C[)]Cou\ch{(}n\D[]ty \Em[)]Down.}
}

\verse{
\li{As she\ch{(} \Em[]onward \C[)]sped, sure I\ch{(} \G[]scratched my \D[)]head}
\li{And I \Em[]looked with a feelin' \D[]rare.}
\li{And I\ch{(} \Em[]says, says \C[)]I, to a\ch{(} \G[]passer-\D[)]by}
\li{\dq Who's the\ch{(} \Em[]maid with the \C[)]nut\ch{(} \D[]brown \Em[)]hair?\dq}
\li{He \G[]smiled at me and \D[]then, says he,}
\li{\dq That's the\ch{(} \Em[]gem of the \C[)]Ireland's \D[]crown,}
\li{Young\ch{(} \Em[]Rosie Mc\C[)]Cann from the\ch{(} \G[]banks of the \D[)]Bann.}
\li{She's the\ch{(} \Em[]Star of the \C[)]Cou\ch{(}n\D[]ty \Em[)]Down.\dq {} - \refrain*}
}

\verse{
\li{She'd a\ch{(} \Em[]soft brown \C[)]eye and a\ch{(} \G[]look so \D[)]shy}
\li{And a \Em[]smile like the rose in \D[]June.}
\li{And you\ch{(} \Em[]hung on each \C[)]note from her\ch{(} \G[]lily-white \D[)]throat}
\li{As she\ch{(} \Em[]lilted an \C[)]I \ch{(}\g{-}\D[]rish \Em[)]tune.}
\li{At the \G[]pattern dance, you were \D[]held in a trance}
\li{As she\ch{(} \Em[]tripped through a \C[)]reel or a \D[]jig.}
\li{And when her\ch{(} \Em[]eyes she'd \C[)]roll, she'd coax \ch{(}u\G[]pon my \D[)]soul}
\li{A\ch{(} \Em[]spud from a \C[)]hun\ch{(}g\D[]ry \Em[)]pig - \refrain*}
}

\verse{
\li{I've\ch{(} \Em[]travelled a \C[)]bit, but\ch{(} \G[]never was \D[)]hit}
\li{Since my \Em[]roving career be\D[]gan.}
\li{But\ch{(} \Em[]fair and \C[)]square I s\ch{(}u\G[]rrendered \D[)]there}
\li{To the\ch{(} \Em[]charm of young \C[)]Rosie\ch{(} \D[]Mc\Em[)]Cann.}
\li{With a \G[]heart to let and no \D[]tenant yet}
\li{Did I\ch{(} \Em[]meet within \C[)]shawl or \D[]gown,}
\li{But\ch{(} \Em[]in she \C[)]went and I\ch{(} \G[]asked no \D[)]rent}
\li{From the\ch{(} \Em[]Star of the \C[)]Cou\ch{(}n\D[]ty \Em[)]Down - \refrain*}
}

\verse{
\li{At the\ch{(} \Em[]Harvest \C[)]Faire she'll be\ch{(} \G[]surely \D[)]there,}
\li{So I'll \Em[]dress in my Sunday \D[]clothes.}
\li{With my\ch{(} \Em[]shoes shone \C[)]bright and my\ch{(} \G[]hat cocked \D[)]right,}
\li{For a\ch{(} \Em[]smile from my \C[)]nut\ch{(}-\D[]brown \Em[)]rose.}
\li{No \G[]pipe I'll smoke; no \D[]horse I'll yoke}
\li{'Til my\ch{(} \Em[]plough is a \C[)]rust-coloured \D[]brown,}
\li{'Til my\ch{(} \Em[]smilin' \C[)]bride by my\ch{(} \G[]own fire\D[)]side}
\li{Sits the\ch{(} \Em[]Star of the \C[)]Cou\ch{(}n\D[]ty \Em[)]Down - \refrain*}
}
}
\end{document}