\documentclass[../Liederbuch/LiederbuchGitarristen.tex]{subfiles}
\begin{document}
\song{Sunny Afternoon}{The Kinks}{5}{Englisch}{Pop}{

\intro{
\chli{\Am \E[7] \Am \E[7]}
}

\verse{
\li{The \Am[]tax man's taken \G[]all my dough}
\li{and \C[]left me in my \G[]stately home,}
\li{\E[7]lazing on a sunny after\Am[]noon.}
\li{And I can't \G[]sail my yacht,}
\li{he's \C[]taken every\G[]thing I've got,}
\li{\E[7]all I've got's this sunny after\Am[]noon.}
}

\chorus{
\li{\A[7]Save me, save me, save me from this \D[7]squeeze,}
\li{I got a \G[]big fat mama trying to break \C[]me\E[7].}
\li{And I \Am[]love to live so \D[7]pleasantly,}
\li{\Am[]live this life of \D[7]luxu\G[]ry,}
\li{\C[]lazing on a \E[7]sunny after\Am[]noon,}
\li{in the \E[7]summertime, in the \Am[]summertime, in the \E[7]summertime.}
}

\verse{
\li{My \Am[]girlfriend's run off \G[]with my car}
\li{and \C[]gone back to her \G[]ma and pa,}
\li{\E[7]telling tales of drunkenness and \Am[]cruelty.}
\li{Now I'm \G[]sitting here,}
\li{\C[]sipping at my \G[]ice cold beer,}
\li{\E[7]lazing on a sunny after\Am[]noon.}
}

\chorus{
\li{\A[7]Help me, help me, help me sail a\D[7]way,}
\li{Well, give me \G[]two good reasons why I oughta \C[]stay\E[7].}
\li{'Cause \Am[]I love to live so \D[7]pleasantly}
\li{\Am[]Live this life of \D[7]luxu\G[]ry,}
\li{\C[]lazing on a \E[7]sunny after\Am[]noon,}
\li{in the \E[7]summertime, in the \Am[]summertime, in the \E[7]summertime. Ah,}
}

\refrain

\outro{
\li{In the \Am[]summertime, in the \E[7]summertime.}
}

\footer{
Ray Davies schrieb das Lied, als er krank zuhause saß. Er dachte dabei, an einen verstaubten gefallen Aristokraten von altem Reichtum, der sein Dasein als Schuft fristet und nach seinen nächtlichen Gelagen mit seiner Freundin streitet.
}
}
\end{document}