\documentclass[../Liederbuch/LiederbuchGitarristen.tex]{subfiles} 
\begin{document}
\song{Survive}{Rise Against}{1}{Englisch}{Punk}{
\intro{
\chli{\Bm \G \A \Em \G \A}
}

\verse{
\li{\Bm Somewhere between \G happy, and total fucking \A wreck,}
\li{\Em feet sometimes on \G solid ground, \A sometimes at the edge.}
\li{To \Bm spend your waking \G moments, simply killing \A time}
\li{is to \Em give up on your \G hopes and dreams, to \A give up on your...}
}

\chorus{
\li{\Bm Life for you, has been \A less than kind,}
\li{so \G take a number, \A stand in line.}
\li{We've \Bm all been sorry, we've \A all been hurt,}
\li{but \G how we survive, \A is what makes us who we \G are\A. \G* \A}
}

\verse{
\li{\Bm An obvious dis\G[]interest, a barely managed \A smile,}
\li{a \Em deep nod in a\G[]greement, a \A status quo exile.}
\li{I \Bm shirk my obli\G[]gations, I miss all your dead\A[]lines.}
\li{I ex\Em[]cel at quitting \G early, and \A fucking up my life.}
}

\refrain

\bridge{
\li{All \C smiles and sunshine, \Bm a perfect world on a perfect \D day,}
\li{\C everything always works out, \Bm I have never felt so fucking \D great.}
\li{All \C smiles and sunshine, \Bm a perfect world on a perfect \D day,}
\li{\C everything always works out, \Bm I have never felt so great.}
}

\bridge{
\li{\brep\Bm Life isn't \G like this, \A life isn't \Em like this.\erep {} \rep{3}}
\li{\Bm Are we \G verging on an \A answer, or fucking up our...}
}

\outro{
\li{\Bm Life for you, has been \A less than kind,}
\li{so \G take a number, \A stand in line.}
\li{We've \Bm all been sorry, we've \A all been hurt,}
\li{but \G how we survive, \A is what makes us who we \Bm are. (Who we are)}
\li{It's what \Em makes us who we \G are. (Who we \A are)}
\li{Makes us who we \Bm are. (Who we \A are)}
\li{It's what makes us who we \G are. (Who we \A are\Bm)}
}
}
\end{document}