\documentclass[../Liederbuch/LiederbuchGitarristen.tex]{subfiles} 
\begin{document}
\song{Teenage Dirtbag}{Wheatus}{}{Englisch}{Pop}{
\intro{
\chli{\brep\E \B \E \A\erep}
}

\verse{
\li{Her \E[]name is No\B[]elle, \E[]I have a \A[]dream about her.}
\li{\E[]She rings my \B[]bell, I got \E[]gym class in \A[]half an hour.}
\li{\E[]Oh, how she \B[]rocks, in \E[]Keds and tube \A[]socks,}
\li{but \Csm[]she doesn't \A[]know who I \B[]am}
\li{and \Csm[]she doesn't \A[]give a \B[]damn about me.}
}

\chorus{
\li{Cause \E[]I'm just a \A[]teenage \B[]dirtbag, \Csm[]baby.}
\li{Yeah, \E[]I'm just a \A[]teenage \B[]dirtbag, \Csm[]baby.}
\li{\E[]Listen to \A[]Iron \B[]Maiden, \Csm[]baby, with \E[]me. \A[]Ooooh\B* \Csm* \sch{\brep}\E* \B* \E* \A*\sch{\erep}}
}

\verse{
\li{Her \E[]boyfriend's a \B[]dick, and \E[]he brings a \A[]gun to school,}
\li{and \E[]he'd simply \B[]kick my \E[]ass if he'd \A[]knew the truth.}
\li{He \E[]lives on my \B[]block and he \E[]drives an I\A[]ROC,}
\li{but \Csm[]he doesn't \A[]know who I \B[]am}
\li{and \Csm[]he doesn't \A[]give a \B[]damn about me.}
}

\refrain

\bridge{
\li{\E* \A[]Oh yeah\E[], \A[]dirtbag\E[]. \A[]No, \Csm[]she doesn't know, \A[]what she's \B[]missing.}
\li{\E* \A[]Oh yeah\E[], \A[]dirtbag\E[]. \A[]No, \Csm[]she doesn't know, \A[]what she's \B[]mis\E[]sing.}
}

\verse{
\li{Man, \E[]I feel like \B[]mold, it's \E[]prom night and \A[]I am lonely.}
\li{\E[]Low and be\B[]hold, \E[]she's walking \A[]over to me,}
\li{\E[]this must be \B[]fake, my \E[]lip starts to \A[]shake.}
\li{\Csm[]How does she \A[]know who I \B[]am?}
\li{And \Csm[]why does she \A[]give a \B[]damn about me?}
}

\chorus{
\li{I've got two \E[]tickets to \A[]Iron \B[]Maiden, \Csm[]baby.}
\li{\E[]Come with me \A[]Friday, \B[]don't say \Csm[]maybe.}
\li{\E[]I'm just a \A[]teenage \B[]dirtbag, \Csm[]baby, like \E[]you. \A[]Ooooh\B* \Csm* \A* \B*}
}

\bridge{
\li{\E* \A[]Oh yeah\E[], \A[]dirtbag\E[]. \A[]No, \Csm[]she doesn't know, \A[]what she's \B[]missing.}
\li{\E* \A[]Oh yeah\E[], \A[]dirtbag\E[]. \A[]No, \Csm[]she doesn't know, \A[]what she's \B[]mis\E[]sing...\B[]* \E[]* \A[]*}
}

\outro{
\chli{\E \B \E \A \Gs \Fs \Gs \Fs \E}
}

}
\end{document}