\documentclass[../Liederbuch/LiederbuchGitarristen.tex]{subfiles} 
\begin{document}
\song{The Sound of Quantum}{T:Michael Naehrig M:Paul Simon}{}{Englisch}{}{
\verse{
\li{\Em[]Hello cryptographers, my old \D[]friends,}
\li{I've come to talk with you a\Em[]gain,}
\li{Because a \G[]threat is slow\C[]ly creep\G[]ing,}
\li{Left its seeds while we were \C[]all sleep\G[]ing,}
\li{And the \C[]vision that came \C[/\G]out of Feynman's \G[]brain}
\li{Still re\Em[]mains \G[]within the \D[]sound of \Em[]quantum.}
}

\verse{
\li{\Em[]In restless dreams I worked a\D[]lone. All elliptic curves were \Em[]gone.}
\li{'Neath the \G[]halo of \C[]a desk \G[]lamp, I turned my touch screen which was \C[]cold and \G[]damp.}                                                      
\li{When my \C[]eyes were stabbed by the \C[/\G]flash of a D-Wave \G[]sign.}
\li{That split the \Em[]night. \G[]And touched the \D[]sound of \Em[]quantum.}
}

\verse{
\li{\Em[]And in the naked light I \D[]saw ten thousand RSA keys, maybe \Em[]more.}
\li{Some say \G[]they can only \C[]factor fif\G[]teen, researchers are making schemes with\C[]out liste\G[]ning,}
\li{People writing \C[]papers that \C[/\G]eprint should never \G[]share.}
\li{And no one \Em[]dare, \G[]disturb the \D[]sound of \Em[]quantum.}
}

\verse{
\li{\Em[]Fools said I, you do not \D[]know those qubits like a cancer \Em[]grow.}
\li{Read Shor's \G[]works that they \C[]might teach \G[]you, they'll be able to factor \C[]seventeen \G[]soon.}
\li{But my \C[]words like \C[/\G]single photons \G[]fell,\Em}
\li{And \G[]echoed in the \D[]waves of \Em[]quantum.}
}

\verse{
\li{\Em[]And the people will be \D[]late to replace the crypto that they \Em[]made.}
\li{And the \G[]NIST will flash out \C[]its warn\G[]ing, in the standards that it \C[]is form\G[]ing.}
\li{Just keep in mind that the \C[]words of the physicists are \C[/\G]written on the arxiv \G[]walls}
\li{and experiment \Em[]halls and \G[]whispered in the \D[]sounds of \Em[]quantum.}
}
}
\end{document}