\documentclass[../Liederbuch/LiederbuchGitarristen.tex]{subfiles}
\begin{document}
\song{The Raven}{T:Edgar Allan Poe M:Omnia}{5}{Englisch}{}{

\intro{
\li{Once upon a midnight dreary, while I pondered, weak and weary, }
\li{over many a quaint and curious volume of forgotten lore.}
\li{While I nodded, nearly napping, suddenly there came a tapping, }
\li{as of some one gently rapping, tapping at my chamber door.}
\li{\dq 'Tis some visitor,\dq{} I muttered, \dq tapping at my chamber door -}
\li{only this, and nothing more.\dq }
}

\intro{
\li{Ah, distinctly I remember it was in the bleak December,}
\li{and each separate dying ember wrought its ghost upon the floor.}
\li{Eagerly I wished the morrow; - vainly I had sought to borrow}
\li{from my books surcease of sorrow - sorrow for the lost Lenore -}
\li{for the rare and radiant maiden whom the angels name Lenore -}
\li{nameless here for evermore.}
}

\verse{
\li{\Am* And the silken sad uncertain rustling \G[]of each purple curtain}
\li{\F[]thrilled me - filled me with fantastic terrors \G[]never felt before.}
\li{Present\Am[]ly, to still the beating of my \C[]heart, I stood repeating,}
\li{\dq 'Tis some visi\F[]tor entreating entrance \G[]at my chamber door –}
\li{some \Em[]late visitor entreating entrance \F[]at my chamber door; -}
\li{merely \G[]this, and nothing \Am[]more.\dq}
}

\bridge{
\li{\G* \F* \G* \Am* \C* \F* \G*}
}

\verse{
\li{\Am* Back into the chamber turning, all my \G[]soul within me burning,}
\li{soon a\F[]gain I heard a tapping somewhat \G[]louder than before.}
\li{\dq Surely,\dq{}  \Am[]said I, \dq surely that is someone \C[]at my window lattice:}
\li{let me \F[]see, then, what thereat is, and this \G[]mystery explore –}
\li{let my \Em[]heart be still a moment and this \F[]mystery explore; -}
\li{'tis the \G[]wind and nothing \Am[]more.\dq}
}

\verse{
\li{Open wide I flung the shutter, when, with \G[]many a flirt and flutter,}
\li{in there \F[]stepped a stately raven of the \G[]saintly days of yore;}
\li{not the \Am[]least obeisance made he; not a \C[]minute stopped or stayed he;}
\li{but, with \F[]mien of lord or lady, perched a\G[]bove my chamber door –}
\li{perched u\Em[]pon a bust of Ares just a\F[]bove my chamber door –}
\li{perched, and \G[]sat, and nothing \Am[]more.}
}

\bridge{
\li{\G* \F* \G* \Am* \C* \F* \G*}
}

\verse{
\li{\Am* Soon that ebony bird beguiling my sad \G[]fancy into smiling,}
\li{by the \F[]grave and stern decorum of the \G[]countenance it wore.}
\li{\dq Though thy \Am[]crest be shorn and shaven, thou,\dq{} I \C[]said, \dq art sure no craven,}
\li{ghastly \F[]grim and ancient raven wandering \G[]on the nightly shore –}
\li{tell me \Em[]what thy lordly name is on the \F[]night's Plutonian shore!\dq }
\li{Quoth the \G[]Raven, \dq Never\Am[]more.\dq}
}

\verse{
\li{Now the raven, sitting lonely on that \G[]placid bust, spoke only}
\li{that one \F[]word, as if his soul in that one \G[]word he did outpour.}
\li{Nothing \Am[]further then he uttered – not a \C[]feather then he fluttered –}
\li{'till I \F[]scarcely more than muttered, \dq Other \G[]friends have gone before –}
\li{on the \Em[]morrow he will leave me, as my \F[]hopes have flown before.\dq}
\li{Quoth the \G[]Raven, \dq Never\Am[]more.\dq}
}

\verse{
\li{Then, methought, the air grew denser, perfumed \G[]by an unseen censer}
\li{swung by \F[]seraphim whose foot-falls tinkled \G[]on the tufted floor. }
\li{Once more \Am[]on the velvet sinking, I be\C[]took myself to linking}
\li{fancy \F[]unto fancy, thinking what this \G[]ominous bird of yore –}
\li{what this \Em[]grim, ungainly, ghastly, gaunt and \F[]ominous bird of yore}
\li{meant in \G[]croaking \dq Never\Am[]more.\dq}
}

\bridge{
\li{\G* \F* \G* \Am* \C* \F* \G*}
}

\verse{
\li{\Am* \dq Prophet!\dq{} said I, \dq thing of evil! - prophet \G[]still, if bird or devil! –}
\li{Whether \F[]Tempter sent, or whether tempests \G[]tossed thee here ashore,}
\li{deso\Am[]late yet all undaunted, on this \C[]desert isle enchanted –}
\li{on this \F[]home by horror haunted – tell me \G[]truly, I implore –}
\li{is there - \Em[]is there balm in Gilead? - tell me - \F[]tell me, I implore!\dq}
\li{Quoth the \G[]Raven, \dq Never\Am[]more.\dq}
}

\verse{
\li{\dq Prophet!\dq{} said I, \dq thing of evil! - prophet \G[]still, if bird or devil! –}
\li{by that \F[]Heaven stretched above us - by that \G[]God we both adore –}
\li{tell this \Am[]soul with sorrow laden if, with\C[]in the distant Aidenn,}
\li{it shall \F[]clasp a sainted maiden whom the \G[]angels name Lenore –}
\li{clasp a \Em[]rare and radiant maiden whom the \F[]angels name Lenore.\dq}
\li{Quoth the \G[]Raven, \dq Never\Am[]more.\dq}
}

\verse{
\li{\dq Be that word our sign in parting, bird or \G[]fiend,\dq{} I shrieked, upstarting –}
\li{\dq get thee \F[]back into the tempest and the \G[]night's Plutonian shore!}
\li{Leave no \Am[]black plume as a token of that \C[]lie thy soul hath spoken!}
\li{Leave my \F[]loneliness unbroken! quit the \G[]bust above my door!}
\li{Take thy \Em[]beak from out my heart, and take thy \F[]form from off my door!\dq}
\li{Quoth the \G[]Raven, \dq Never\Am[]more.\dq}
}

\verse{
\li{Now the \Am[]Raven, never flitting, still is \G[]sitting, still is sitting}
\li{on the \F[]pallid bust of Ares just a\G[]bove my chamber door;}
\li{and his \Am[]eyes have all the seeming of a \C[]demon's that is dreaming,}
\li{and the \F[]lamplight o'er him streaming throws his \G[]shadow on the floor;}
\li{and my \Em[]soul from out that shadow that lies \F[]floating on the floor}
\li{shall be \G[]lifted - never\Am[]more!}
}

\bridge{
\li{\Am* \G* \F* \G* \Am* \C* \F* \G* \G* \F* \G* \Am*}
}


}
\end{document}