\documentclass[../Liederbuch/LiederbuchGitarristen.tex]{subfiles} 
\begin{document}
\song{The longest time}{Billy Joel}{}{Englisch}{Rock}{
\chorus{
\li{\C[]Oh, \G[]oh, \C[]oh, \F[]oh, \G[7]for the longest \C[]time. \G[]Oh, \C[]oh, \F[]oh, \G[7]for the longest}
}

\verse{
\li{\C[]If you said good\F[]bye to me to\C[]night, there would still be \D[7]music left to \G[]write.}
\li{\E[7]What else could \Am[]I do? \G[7]I'm so in\C[]spired by \C[7]you.}
\li{\F[]That hasn't \Dm[]happened for the \G[]longest \C[]time.}
}

\verse{
\li{\C[]Once I thought my \F[]innocence was \C[]gone. Now I know that \D[7]happiness goes \G[]on.}
\li{\E[7]That's where you \Am[]found me, \G[7]when you put your \C[]arms around \C[7]me.}
\li{\F[]I haven't \Dm[]been there for the \G[]longest \C[]time.}
}

\refrain

\verse{
\li{\C[]I'm that voice you're \F[]hearing in the \C[]hall. And the greatest \D[7]miracle of \G[]all}
\li{\E[7]is how I \Am[]need you - \G[7]and how you \C[]needed me \C[7]too.}
\li{\F[]That hasn't \Dm[]happened for the \G[]longest \C[]time.}
}

\bridge{
\li{\G[]Maybe this won't \Am[]last very long, but \B[7]you feel so right and \C[]I could be wrong.}
\li{\Em[]Maybe I've been \Am[]hoping too hard, but \D[]I've gone this \D[7]far and it's \G[]more than I \G[7]hoped for}
}

\verse{
\li{\C[]Who knows how much \F[]further we'll go \C[]on. Maybe I'll be \D[7]sorry when you're \G[]gone.}
\li{\E[7]I'll take my \Am[]chances, \G[7]I forgot how \C[]nice romance \C[7]is,}
\li{\F[]I haven't \Dm[]been there for the \G[]longest \C[]time.}
}

\bridge{
\li{\G[]I had second \Am[]thoughts at the start. I \B[7]said to myself: Hold \C[]on to your heart.}
\li{\Em[]Now I know the \Am[]woman that you are you're \D[]wonderful so \D[7]far and it's \G[]more than I \G[7]hoped for}
}

\verse{
\li{\C[]I don't care what \F[]consequence it \C[]brings. I have been a \D[7]fool for lesser \G[]things.}
\li{\E[7]I want you \Am[]so bad - \G[7]I think you \C[]ought to know \C[7]that}
\li{\F[]I intend to \Dm[]hold you for the \G[]longest \C[]time.}
}

\outro{
\li{\C[]Oh, \G[]oh, \C[]oh, \F[]oh, \G[7]for the longest \C[]time.}
\li{\G[]Oh, \C[]oh, \F[]oh, \G[7]for the longest \C[]time. \rep{4}}
}
}
\end{document}