\documentclass[../Liederbuch/LiederbuchGitarristen.tex]{subfiles}
\begin{document}
\song{Tribute}{Tenacious D}{}{Englisch}{Rock}{

\intro{
\chli{\Am[*]}
}

\verse{
\li{\Am[*]This is the greatest and best song in the world - \Am[*]Tribute}
\li{\Am[*]Long time ago me and my brother Kyle here, \Am[*]we was hitchhikin' down a long and lonesome road.}
\li{\Am[*]All of a sudden, there shined a shiny demon \Am[*]In the middle of the road.}
\li{\Am[*]And he said: \A[Note]\dq Play the best song in the world, or I'll eat your souls.\dq}
\li{\Am[*]Well me and Kyle, we looked at each other, \Am[*]And we each said \dq Okay\dq}
}

\chorus{
\li{\Am[]And we played the first thing that \G[]came to our heads, \F[]just so happened to be}
\li{\Am[]The Best Song in the \G[]World, it was \F[]The Best Song in the World}
\li{\D[]Look into my eyes and it's \F[]easy to see}
\li{One and \C[]one make two, two and \G[]one make three, it was \F[]destiny.}
\li{\D[]Once every hundred-thousand \F[]years or so, when the \C[]sun doth shine }
\li{And the \G[]moon doth glow and the \F[]grass don't grow}
}

\verse{
\li{\Am[*]Needless to say, the beast was stunned. \Am[*]Whip-crack went his schwumpy tail,}
\li{\Am[*]And the beast was done. \Am[*]He asked us: \dq Be you angels?\dq}
\li{\Am[*]And we said, \dq Nay. \Am[*]We are but men!\dq ~- ROCK!}
}

\bridge{
\li{\D[]Ahhh, \F[]ahhh, \C[]ahhh-ah-\G[]ah, \F[]Ohhh, whoah, ah-whoah-oh!}
\li{\Am[]This is not The \G[]Greatest Song in the \Am[]World. No, this is just a \G[]tribute. \Am}
\li{\Am[*]Couldn't remember The \G[]Greatest Song in the \Am[]World. No, this is a \G[]tribute, oh. \Am}
\li{\Am* \G[]To The Greatest \D[]Song in the \F[]World, All right!}
\li{\Am* \G[]It was The Greatest \D[]Song in the \F[]World, All right!}
\li{\Am[]It was the \G[]best muthafuckin' song \D[]the greatest song in the \F[]world.}
\chli{\brep \Am \G \D \F \erep}
}

\outro{
\li{\Am[]And the peculiar \G[]thing is this my friends: \D[]The song we sang on that \F[]fateful night,}
\li{\Am[]It didn't actually sound \G[]anything like this \D[]song. \F}
\li{This is just a \Am[]tribute! You \G[]gotta' be\D[]lieve me! \F}
\li{And I wish you were \Am[]there! \G[]Just a matter of op\D[]inion. \F}
\li{Ah, fuck! \Am[*]Good God, \G[]God lovin', \D[]So surprised to find \F[]you can't stop it.}
\li{\E* \F[]All \G[]right! \E* \F[]All right! \E* \F* \Am}
}

}
\end{document}