\documentclass[../Liederbuch/LiederbuchGitarristen.tex]{subfiles} 
\begin{document}
\song{Uptown girl}{Billy Joel}{}{Englisch}{Rock}{
\intro{
\li{\D[]Oh-oh-oh-\G[]oh-oh-oh-oh-\D[]oh-oh-oh-\G[]oh-oh-oh-oh}
}

\verse{
\li{\D[]Uptown girl, \Em[]she's been living in her \Fsm[]uptown world. \G[]I bet she \A[]never had a}
\li{\D[]back street guy, \Em[]I bet her mama never \Fsm[]told her why. \G[]I'm gonna \A[]try for an}
}

\verse{
\li{\D[]Uptown girl, \Em[]she's been living in her \Fsm[]white bread world, \G[]as long as \A[]anyone with}
\li{\D[]hot blood can \Em[]and now she's looking for a \Fsm[]downtown man. \G[]That's what I \A[]am}
}

\chorus{
\li{\Bb[]And when she \Gm[]knows what she \Cm[]wants from her \F[]time}
\li{\Bb[]and when she \Gm[]wakes up and \Cm[]makes up her \F[]mind,}
\li{\G[]she'll see I'm \Em[]not so tough, \C[]just because \A[]I'm in love with an}
}

\verse{
\li{\D[]Uptown girl, \Em[]you know I've seen her in her \Fsm[]uptown world. \G[]She's getting \A[]tired of her}
\li{\D[]high class toys \Em[]and all her presents from her \Fsm[]uptown boys. \G[]She's got a \A[]choice.}
}

\bridge{
\li{\F[]Oh-oh-oh-\G[]oh-oh-oh-oh-\G[/\Gs]oh-oh-oh-oh-\Am[]oh-oh-\G[]oh-oh}
\li{\F[]Oh-oh-oh-\G[]oh-oh-oh-oh-\G[/\Gs]oh-oh-oh-oh-\A[]oh-oh-oh}
}

\verse{
\li{\D[]Uptown girl, \Em[]you know I can't afford to \Fsm[]buy her pearls. \G[]But maybe \A[]someday when my}
\li{\D[]ship comes in, \Em[]she'll understand what kind of \Fsm[]guy I've been. \G[]And then I'll \A[]win.}
}

\chorus{
\li{\Bb[]And when she's \Gm[]walking, she's \Cm[]looking so \F[]fine}
\li{\Bb[]and when she's \Gm[]talking, she'll \Cm[]say that she's \F[]mine.}
\li{\G[]She'll say I'm \Em[]not so tough, \C[]just because \A[]I'm in love with an}
}

\verse{
\li{\D[]Uptown girl, \Em[]she's been living in her \Fsm[]white bread world, \G[]as long as \A[]anyone with}
\li{\D[]hot blood can \Em[]and now she's looking for a \Fsm[]downtown man. \G[]That's what I \A[]am}
}

\bridge{
\li{\F[]Whoo-oh-oh-\G[]oh-oh-oh-oh-\G[/\Gs]oh-oh-oh-oh-\Am[]oh-oh-\G[]oh-oh}
\li{\F[]Whoo-oh-oh-\G[]oh-oh-oh-oh-\G[/\Gs]oh-oh-oh-oh-\A[]oh-oh-oh}
}

\outro{
\li{\E[]Uptown girl, \Fsm[]she's my uptown \Gsm[]girl. You \A[]know I'm in \B[]love with an}
\li{\E[]Uptown girl, \Fsm[]my uptown \Gsm[]girl. You \A[]know I'm in \B[]love with an}
\li{\E[]Uptown girl, \Fsm[]my uptown \Gsm[]girl. You \A[]know I'm in \B[]love with an}
\li{\E[]Uptown girl, \Fsm[]my uptown \Gsm[]girl.}
}
}
\end{document}