\documentclass[../Liederbuch/LiederbuchGitarristen.tex]{subfiles}
\begin{document}
\song{Wernher von Braun}{Tom Lehrer}{}{Englisch}{Liedermacher}{

\verse{
\li{Gather \G[7]round while I sing you of \C Wernher von Braun,}
\li{a \G[7]man whose al\C[]legiance is \G[7]ruled by ex\C[]pedience.}
\li{\G[7]Call him a Nazi, he \C won't even \A[7]frown.}
\li{\dq\Dm Nazi, \C Schmazi,\dq{} says \G[7]Wernher von \C Braun.}
\li{\B[7]Don't say that he's hypo\Em[]critical,}
\li{say \B[7]rather that he's apo\Em[]litical.}
\li{\dq Once the \G[7]rockets are up, who cares \C where they come \A[7]down?}
\li{That's \Dm not my de\C[]partment,\dq{} says \G[7]Wernher von \C Braun.}
}

\verse{
\li{\G[7]Some have harsh words for this \C man of renown,}
\li{but \G[7]some think our \C attitude should \G[7] be one of \C gratitude,}
\li{Like the \G[7]widows and cripples in \C old London \A[7]town,}
\li{who \Dm owe their large \C pensions to \G[7]Wernher von \C Braun.}
\li{You \B[7]too may be a big \Em hero,}
\li{once you've \B[7]learned to count backwards to \Em zero.}
\li{\dq In \G[7]German oder Englisch I know \C how to count \A[7]down.}
\li{Und I'm \Dm learning Chi\C[]nese,\dq{} says \G[7]Wernher von \C Braun.}
}

\footer{Wernher von Braun war ein deutscher Raketeningenieur, der zuerst das Raketenprogramm der Nationalsozialisten leitete, nach Kriegsende dann für das US-Militär und die NASA Raketen entwickelte, darunter die Saturn-Raketen der Apollo Mondmissionen. Damit gilt er als Pionier sowohl militärischer Raketentechnologie als auch der zivilen Raumfahrt.}
}
\end{document}