\documentclass[../Liederbuch/LiederbuchGitarristen.tex]{subfiles} 
\begin{document}
\song{Your Love Is A Lie}{Simple Plan}{1}{Englisch}{Rock}{
\verse{
\li{\Em[]I fall asleep by the \G[]telephone.}
\li{\D[]It's two o'clock and I'm \A[]waiting up alone. \Em[]}
\li{Tell me, \G[]where have you \D[]been? (where have \A[]you been)}
\li{I \Em[]found a note with an\G[]other name.}
\li{\D[]You blow a kiss but it \A[]just don't feels the \Em[]same.}
\li{'Cuz I can \G[]feel that you're \D[]gone. (feel that you're \A[]gone)}
}

\bridge{
\li{I can \C[]bite my tonge for\G[]ever}
\li{While you \D[]try to play it \A[]cool.}
\li{You can \C[]hide behind your \G[]stories}
\li{But don't \B[]take me for a fool!}
}

\chorus{
\li{You can \Em[]tell me that there's \G[]nobody \D[]else! (but I \A[]feel it!)}
\li{You can \Em[]tell me that you're \G[]home by your\D[]self! (but I \A[]see it!)}
\li{You can \Em[]look into my \G[]eyes and pretend \D[]all you \A[]want, but I \C[]know, I \D[]know}
\li{Your love is just a \Em[]lie! (\G[]Lie! \D[]Lie!)}
\li{\A[]It's nothing but a \Em[]lie! (\G[]Lie! \D[]Lie!)}
}

\verse{
\li{\Em[]You look so \G[]innocent,}
\li{\D[]But the guilt in your \A[]voice gives you a\Em[]way.}
\li{\Em[]Yeah, you \G[]know what I \D[]mean. (know what \A[]I mean)}
\li{\Em[]How does it feel when you kiss when you \G[]know that I trust you?}
\li{\D[]And do you think about me \A[]when he fucks you?}
\li{\Em[]Could you be \G[]more ob\D[]scene? (be \A[]more obscene)}
}

\bridge{
\li{So don't \C[]try to say you're \G[]sorry,}
\li{Or \D[]try to make it \A[]right.}
\li{And don't \C[]waste your breath be\G[]cause it's too \Em[]late,}
\li{ it's too \B[]late!}
}

\repref{2}
}
\end{document}