\documentclass[../Liederbuch/LiederbuchGitarristen.tex]{subfiles} 
\begin{document}
\song{Zombie}{The Cranberries}{}{Englisch}{Rock}{
\verse{
\li{\Em[]Another \C[]head hangs lowly}
\li{\G[]child is slowly \D[]taken}
\li{\Em[]And the violence \C[]caused such silence,}
\li{\G[]who are we mis\D[]taken}
}

\bridge{
\li{But you \Em[]see it's not me, it's not \C[]my family,}
\li{In your \G[]head, in your head, they are \D[]fighting}
\li{With their \Em[]tanks and their bombs,}
\li{and their \C[]bombs and their guns.}
\li{In your \G[]head, in your head, they are \D[]crying.}
}

\chorus{
\li{In your \Em[]head, in your \C[]head, zom\G[]bie, zombie, zom\D[]bie-ie-ie}
\li{What's in your \Em[]head, in your \C[]head, zom\G[]bie, zombie, zom\D[]bie-ie-ie-ie}
\li{Oh, \Em[]dou, dou, dou, dou, \C[]dou, dou, dou, dou, \G[]dou, dou, dou, dou, \D[]dou, dou, dou, dou}
}

\verse{
\li{\Em[]Another \C[]mother's breakin',}
\li{\G[]Heart is taking \D[]over.}
\li{\Em[]When the vi'lence \C[]causes silence,}
\li{\G[]We must be mis\D[]taken.}
}

\bridge{
\li{It's the \Em[]same old theme since \C[]nineteen-sixteen.}
\li{In your \G[]head, in your head they're still \D[]fighting,}
\li{With their \Em[]tanks and their bombs,}
\li{And their \C[]bombs and their guns.}
\li{In your \G[]head, in your head, they are \D[]dying.}
}

\refrain
\footer{Zombie ist gewissermaßen ein Protestsong gegen den Nordirlandkonflikt, in dem sich Katholiken und Protestanten seit Jahrzehnten schwere Gefechte liefern. Es sind außerdem deutliche Zusammenhänge mit dem Osteraufstand von 1916 zu erkennen.}
}
\end{document}